### 2014-02-22 paper/draft.tex
the first paper draft

\documentclass[manuscript]{aastex}
%\documentclass[preprint2]{aastex}
\newcommand{\vdag}{(v)^\dagger}
\newcommand{\myemail}{skywalker@galaxy.far.far.away}

\shorttitle{A Connection Between Star Formation Rate and Dark Matter Halos at Z \~ 6}
\shortauthors{G\'omez-Cort\'es}

\begin{document}

\title{A Connection Between Star Formation Rate and Dark Matter Halos at $Z\sim6$ Using 2013 Plank Cosmology.}

\author{F.L. G\'omez-Cort\'es\altaffilmark{1} }
\affil{Departamento de Física, Universidad de los Andes, Colombia}

\begin{abstract}
This work relates baryonic matter and dark matter at high redshift using observational data
from the HST and results of the Multidark Simulation.
Luminosity Function - Dark Matter Halos, Star Formation Rate - Dark Matter Halos.
\end{abstract}

\keywords{LF, SFR, high redshift galaxies, reionization}

\section{Introduction}
\subsection{Halo Mass Function (HMF)}
The HMF is created using the DMH catalog from the Multidark Database.
\subsection{Cosmic Variance}
Is important to know and understand the existence of local fluctuations
or inhomogeneities due the observed scale.

For this part is necesary to study the HMF on smaller boxes

\section{Relationship between Galaxy Luminosity Function (GLF) and
Dark Matter Halo (DMH) mass}

In one hand we have observational results: the GLF for star-forming galaxies at high redshift (z=5.9)\citep{bouwens06,willott07}
expressed in terms of magnitude in the ultraviolet range (M1350). In the other hand we have a DMH 
catalog, result from the Multidark Simulation with Plank Cosmology. %\citep{Multidark}

A $1000 \textrm{ Mpc} ^3 \textrm{h}^{−3}$ cubic box containing near to $11\times10^6$ dark matter halos.

The idea is to connect the observed GLF with the DMH catalog. We assume that each halo contains one and just one galaxy, and its luminosity is given by:
\begin{equation}
L_\textrm{galaxy}=\alpha M_\textrm{halo}^\beta 
\end{equation}
but this function is given in magnitude units. Is necesary to convert magnitude to luminosity.

\section{Magnitude to Luminosity}
The Luminosity is an intrinsic propertie of the stars. It doesn't deppends of the distance. 
It's directly related to the energy flux emmited. The luminosity $L_\nu$ at a given frecuency 
$\nu$ is has $[\textrm{W}\textrm{Hz}^{-1}]$ or $[\textrm{erg }\textrm{s}^{-1}\textrm{Hz}^{-1}]$ units.

The magnitude is brightnes star classification inherited from ancient Greeks. It deppends of 
the stellar distance. The absolute magnitude is a modern classification independent of 
distance. Taking the Sun as reference, the absolute magnitud at a given wavelengt is given by: 
\[ M_{\lambda} = M_{\lambda \odot} - 2.5 \log_{10}\left( \frac{L_\lambda}{L_{\lambda \odot}} \right) \]
The solar absolute magnitude in the U filter is:
\[ M_{\textrm{U} \odot} = 5.61\]
and the luminosity:
\[ 1 L_{\textrm{U} \odot} = 10^{18.48} \textrm{ergs s}^{-1}\textrm{Hz}^{-1}\]
\[ 1 L_{\textrm{U} \odot} = 3.02 \times 10^{18} \textrm{ergs s}^{-1}\textrm{Hz}^{-1}\]
Replacing in the absolute magnitude equation:
\[ M_{\textrm{U}} = 5.61 - 2.5 \log_{10}(L_{\textrm{U}}) + 25\times18.48\]
gives:
\[ M_{\textrm{U}} = 51.82 - 2.5 \log_{10}(L_{\textrm{U}}) \]

\subsection{Best Fitting Parameters}

\huge
A big mistake.

\[\log \neq \log_{10}\]
\normalsize

--Here comes the fitting graph--

And the fitting parameters

$\alpha = ?$

$\beta = ?$

\section{Stelar Formation Rate}

\subsection{The UV Continuum}
The UV region is dominated by big blue young stars, is possible to make an extrapolation to small young stars.

On stellar-formation galaxies the spectrum has a UV continuum nearly flat. This is a good approximation:

$ \textrm{SFR}\left(M_\odot \textrm{yr}^{-1}\right) = 1.4 \times 10^{28} L_{\nu} \left( \textrm{erg s}^{-1}\textrm{Hz}^{-1} \right)$

With Initial Mass Function (IMF) between $0.1 M_\odot$ and $100 M_\odot$, in the range of $1250-2500 \mathring{\textrm{A}} $

\subsection{The Fitting Model}

This fitting model contains four parameters: $\left(m/M\right)_0$, $M_1$, $\beta$ and $\gamma$, 
where $m:=$ Stellar mass, and $M :=$ Dark Matter Halo mass.
\begin{equation}
\frac{m}{M} = 2 \left( \frac{m}{M} \right)_{0} 
		  \left[ \left(\frac{M}{M_1}\right)^{-\beta} + \left(\frac{M}{M_1}\right)^{\gamma} \right]^{-1} 
\end{equation}
Another model cited in the article contains five parameters: $m_0$, $M_1$, $\beta$, $\gamma_1$ and $\gamma_2$.
\[ m(M) = m_0 \frac{ (M/M_1)^{\gamma_1}}{ \left[ 1 + (M/M_1)^\beta \right]^{ (\gamma_1-\gamma_2)/\beta}} \]

\section{Observations}

Willott

Bowens

McLure

\section{Discussion}

\section{Summary}

\acknowledgments
Gracias Totales

\appendix

\section{Appendix material}

\begin{thebibliography}{}
\bibitem[Bouwens(2006)]{bouwens06} Bouwens, R. J. et al. 2006, \apj, 653, 53
\bibitem[Willot(2007)]{willott07} Willott, Chris J. et al. 2013, \aj, 145, 4
\end{thebibliography}

\end{document}

%%
%% End of file `sample.tex'.

### 2014-03-10 paper/draft.tex
Abstract updated

@@
 %\documentclass[preprint2]{aastex}
+
 \newcommand{\vdag}{(v)^\dagger}
@@
 \begin{abstract}
-This work relates baryonic matter and dark matter at high redshift using observational data
-from the HST and results of the Multidark Simulation.
-Luminosity Function - Dark Matter Halos, Star Formation Rate - Dark Matter Halos.
+This work relates baryonic matter and dark matter at redshift $z=5.9$ using observational data
+from CFHTLS\citep{willott13}, HUDF09\citep{bouwens06,bouwens12}, UKIRT and SDXS\citep{mclure09}, and results of the Multidark Simulation \citep{riebe13}
+in a cubic box of length $1000 \textrm{Mpc h}^{-1}$. Cosmic variance effects are studied on smaller boxes of length $250 \textrm{Mpc h}^{-1}$.
+The luminosity function is fitted in booth sizes. Using the relationship between the UV continuum and Star Formation Rate (SFR) by \cite{kennicutt98}
+we get the relationship between the Dark Matter Halos Mass and Star Formation Rate.
+%Luminosity Function - Dark Matter Halos, Star Formation Rate - Dark Matter Halos.
 \end{abstract}
-
-\keywords{LF, SFR, high redshift galaxies, reionization}
+\keywords{Dark Matter, LF, SFR, High Redshift Galaxies, Reionization}
 
@@
 
-In one hand we have observational results: the GLF for star-forming galaxies at high redshift (z=5.9)\citep{bouwens06,willott07}
+In one hand we have observational results: the GLF for star-forming galaxies at high redshift (z=5.9)\citep{bouwens06,willott13}
 expressed in terms of magnitude in the ultraviolet range (M1350). In the other hand we have a DMH 
@@
 
+\subsection{The Drop-out Technique - Lyman Break Technique}
+
 \section{Discussion}
@@
 \acknowledgments
-Gracias Totales
-
+%Gracias Totales
+%
 \appendix
@@
 \begin{thebibliography}{}
-\bibitem[Bouwens(2006)]{bouwens06} Bouwens, R. J. et al. 2006, \apj, 653, 53
-\bibitem[Willot(2007)]{willott07} Willott, Chris J. et al. 2013, \aj, 145, 4
+\bibitem[Bouwens(2006)]{bouwens06} Bouwens, R. J. et al. 2006, \apj, 653, 53%2006ApJ...653...53B
+\bibitem[Bouwens(2012)]{bouwens12} Bouwens, R. J. et al. 2012, \apj, 752, 5 %2012ApJ...752L...5B
+\bibitem[Kennicutt(1998)]{kennicutt98} Kennicutt, Robert C., Jr. 1998, \araa, 36, 189%1998ARA&A..36..189K
+\bibitem[McLure(2009)]{mclure09} McLure, R. J. et al. 2009, \mnras, 395, 2196%2009MNRAS.395.2196M
+\bibitem[Riebe(2013)]{riebe13} Riebe, K. et al. 2013, AN, 334, 691 %2013AN....334..691R
+\bibitem[Willott(2013)]{willott13} Willott, Chris J. et al. 2013, \aj, 145, 4%2013AJ....145....4W
+
 \end{thebibliography}

### 2014-03-10 paper/draft.tex
title: small mod. fragments from observational data references and the fitting function reference.

@@
 
-\title{A Connection Between Star Formation Rate and Dark Matter Halos at $Z\sim6$ Using 2013 Plank Cosmology.}
+\title{A Connection Between Star Formation Rate and Dark Matter Halos at $Z\sim6$ In 2013 Planck Cosmology.}
 
@@
 This work relates baryonic matter and dark matter at redshift $z=5.9$ using observational data
-from CFHTLS\citep{willott13}, HUDF09\citep{bouwens06,bouwens12}, UKIRT and SDXS\citep{mclure09}, and results of the Multidark Simulation \citep{riebe13}
-in a cubic box of length $1000 \textrm{Mpc h}^{-1}$. Cosmic variance effects are studied on smaller boxes of length $250 \textrm{Mpc h}^{-1}$.
-The luminosity function is fitted in booth sizes. Using the relationship between the UV continuum and Star Formation Rate (SFR) by \cite{kennicutt98}
-we get the relationship between the Dark Matter Halos Mass and Star Formation Rate.
+from CFHTLS \citep{willott13}, HUDF09 \citep{bouwens06,bouwens12}, UKIDSS and SDXS \citep{mclure09}, 
+and results of the Multidark Simulation \citep{riebe13} in a cubic box of $1000 \textrm{Mpc h}^{-1}$ length
+with 2013 Planck Cosmology. 
+The Luminosity Function (LF) is fitted via four parameters with the Markov Chain Monte Carlo method.
+The relationship between the Dark Matter Halos Mass and Star Formation Rate is obtained
+using the relationship between the UV continuum (from the fitted LF) and Star Formation Rate (SFR) by \cite{kennicutt98}.
+Cosmic variance effects are studied on smaller boxes of $250 \textrm{Mpc h}^{-1}$ length.
+
 %Luminosity Function - Dark Matter Halos, Star Formation Rate - Dark Matter Halos.
@@
 \section{Introduction}
+
   \subsection{Halo Mass Function (HMF)}
-The HMF is created using the DMH catalog from the Multidark Database.
+
+  The HMF is created using the DMH catalog from the Multidark Database \citep{riebe13}.
+
   \subsection{Cosmic Variance}
+
   Is important to know and understand the existence of local fluctuations
@@
   \subsection{The UV Continuum}
-The UV region is dominated by big blue young stars, is possible to make an extrapolation to small young stars.
+  The UV region is dominated by big blue young stars, 
+  is possible to make an extrapolation to small young stars\citep{kennicutt98}.
+  On stellar-formation galaxies the spectrum has a 
+  UV continuum nearly flat. This is a good approximation:
 
-On stellar-formation galaxies the spectrum has a UV continuum nearly flat. This is a good approximation:
+  $ \textrm{SFR}\left(M_\odot \textrm{yr}^{-1}\right) 
+      = 1.4 \times 10^{28} L_{\nu} \left( \textrm{erg s}^{-1}\textrm{Hz}^{-1} \right)$
 
-$ \textrm{SFR}\left(M_\odot \textrm{yr}^{-1}\right) = 1.4 \times 10^{28} L_{\nu} \left( \textrm{erg s}^{-1}\textrm{Hz}^{-1} \right)$
-
-With Initial Mass Function (IMF) between $0.1 M_\odot$ and $100 M_\odot$, in the range of $1250-2500 \mathring{\textrm{A}} $
+  With Initial Mass Function (IMF) between $0.1 M_\odot$ 
+  and $100 M_\odot$, in the range of $1250-2500 \mathring{\textrm{A}} $
 
@@
   \end{equation}
+  This is similar to the proposed by \cite{moster10}.
   Another model cited in the article contains five parameters: $m_0$, $M_1$, $\beta$, $\gamma_1$ and $\gamma_2$.
@@
 
+   ``We use a statistical approach to determine the relationship between the stellar masses of galaxies and the masses
+  of the dark matter halos in which they reside. We obtain a parameterized stellar-to-halo mass (SHM) relation by
+  populating halos and subhalos in an N-body simulation with galaxies and requiring that the observed stellar mass
+  function be reproduced.'' \citep{moster10}
+
 \section{Observations}
 
-Willott
+  \subsection{CFHTLS}
 
-Bowens
+  CFHTLS - Canada-France-Hawaii Telescope Legacy Survey - MegaCam\citep{willott13}
 
-McLure
+  ``We identify a sample of 40 Lyman break galaxies brighter than
+    magnitude z ′ = 25.3 across an area of almost 4 square degrees.
+    Sensitive spectroscopic observations of seven galaxies provide 
+    redshifts for four, of which only two have moderate to strong 
+    Lyα emission lines. All four have clear continuum breaks in 
+    their spectra.'' \cite{willott13}.
+
+  ``The imaging data used to select high-redshift galax-
+    ies come primarily from the 3.6 m Canada-France-Hawaii
+    Telescope. Optical observations with MegaCam in the
+    u ∗ g ′ r ′ i ′ z ′ filters are from CFHTLS Deep which covered
+    four ≈ 1 square degree fields with typical total integra-
+    tion time of 75 ks in u ∗ , 85 ks in g ′ , 145 ks in r ′ , 230 ks in
+    i ′ and 175 ks in z ′ . The seeing in the final stacks at i ′ and
+    z ′ range from 0.66 to 0.76 arcsec. The data used here are
+    from the 6th data release, T0006, which contains all the
+    data acquired over the five years of the project '' \cite{willott13}.
+
+  ``These optical data are complemented by near-IR data
+    from the WIRCam Deep Survey (WIRDS; Bielby et al.
+    2012). WIRDS used the WIRCam near-IR imager at
+    the CFHT'' \cite{willott13}.
+
+  \subsection{HUDF09}
+
+  ``Table 1 summarizes the search fields used for the z ∼ 5-
+    8 LF determinations and the approximate depths of the
+    available ACS+WFC3/IR observations. Our primary
+    data set consists of the full two-year WFC3/IR obser-
+    vations of the HUDF and two flanking fields obtained
+    with the 192-orbit HUDF09 program (PI Illingworth:
+    GO 11563). Our second data set is the ∼145 arcmin 2
+    ACS+WFC3/IR observations over the wide-area Early
+    Release Science (Windhorst et al. 2011) and CDF-South
+    CANDELS'' \cite{bouwens12}
+
+  ``A detailed summary of the ACS HUDF, HUDF-Ps, and GOODS
+    data we use for our dropout selections is provided in our previous
+    work ( B06). Nevertheless, a brief description of the data is in-
+    cluded here. The ACS HUDF data we use are the version 1.0 re-
+    ductions of Beckwith et al. (2006) and extend to 5  point-source
+    limits of 29Y30 in the B 435 V 606 i 775 z 850 bands. The HUDF-Ps re-
+    ductions we use are from B06 and take advantage of the deep
+    (k72 orbit) BViz ACS data fields taken in parallel with the HUDF
+    NICMOS program (Thompson et al. 2005). Together the parallel
+    data from this program sum to create two very deep ACS fields
+    that we can use for dropout searches. While of somewhat var-
+    iable depths, the central portions of these fields (12Y20 arcmin 2 )
+    reach some 0.6Y0.9 mag deeper than the data in the original ACS
+    GOODS program (Giavalisco et al. 2004a). Finally, for the ACS
+    GOODS reductions, we use an updated version of those generated
+    for our previous z 6 study (B06).'' \cite{bouwens06}
+
+  \subsection{UKIDSS \& SDXS}
+    ``The UDS is the deepest of five near-IR surveys currently underway
+      at the UK InfraRed Telescope (UKIRT) with the new WFCAM
+      imager (Casali et al. 2007) which together comprise the UKIDSS
+      (Lawrence et al. 2007). The UDS covers an area of 0.8 deg 2 cen-
+      tred on RA = 02:17:48, Dec. = −05:05:57 (J2000) and is already
+      the deepest, large area, near-IR survey ever undertaken. The data
+      utilized in this paper were taken from the first UKIDSS Data Re-
+      lease (DR1; Warren et al. 2007), which included JK imaging of the
+      entire UDS field to 5σ depths of J = 23.9, K = 23.8 (1.6 arcsec
+      diameter apertures). The UKIDSS DR1 became publicly available
+      to the world wide astronomical community in 2008 January and can
+      be downloaded from the WFCAM Science Archive. 2
+      The UDS field is covered by a wide variety of deep, multiwave-
+      length observations ranging from the X-ray through to the radio (see
+      Cirasuolo et al. 2008 for a recent summary). However, for this study
+      the most important multiwavelength observations are the deep op-
+      tical imaging of the field taken with Suprime-Cam (Miyazaki et al.
+      2002) on Subaru as part of the Subaru/XMM–Newton Deep Survey
+      (Sekiguchi et al. 2005). The optical imaging consists of five over-
+      lapping Suprime-Cam pointings, and covers an area of 1.3 deg 2 .
+      The whole field has been imaged in the BV Ri z filters, to typical
+      5σ depths of B = 27.9, V = 27.4, R = 27.2, i = 27.2 and z = 26.2
+      (1.6 arcsec diameter apertures). The reduced optical imaging of the
+      SXDS is now publicly available 3 and full details of the observations,
+      data reduction and calibration procedures are provided in Furusawa
+      et al. (2008). The high-redshift galaxies investigated in this study
+      were selected from a contiguous area of 0.63 deg 2 (excluding areas
+      contaminated by bright stars and CCD blooming) covered by both
+      the UDS near-IR and SXDS optical imaging.'' \cite{mclure09}
 
 \subsection{The Drop-out Technique - Lyman Break Technique}
+
+\cite{steidel03}
 
@@
 \begin{thebibliography}{}
-\bibitem[Bouwens(2006)]{bouwens06} Bouwens, R. J. et al. 2006, \apj, 653, 53%2006ApJ...653...53B
+\bibitem[Bouwens(2006)]{bouwens06} Bouwens, R. J. et al. 2006, \apj, 653, 53			%2006ApJ...653...53B
 \bibitem[Bouwens(2012)]{bouwens12} Bouwens, R. J. et al. 2012, \apj, 752, 5 			%2012ApJ...752L...5B
-\bibitem[Kennicutt(1998)]{kennicutt98} Kennicutt, Robert C., Jr. 1998, \araa, 36, 189%1998ARA&A..36..189K
-\bibitem[McLure(2009)]{mclure09} McLure, R. J. et al. 2009, \mnras, 395, 2196%2009MNRAS.395.2196M
+\bibitem[Kennicutt(1998)]{kennicutt98} Kennicutt, Robert C., Jr. 1998, \araa, 36, 189		%1998ARA&A..36..189K
+\bibitem[McLure(2009)]{mclure09} McLure, R. J. et al. 2009, \mnras, 395, 2196			%2009MNRAS.395.2196M
+\bibitem[Moster(2010)]{moster10} Moster, Benjamin P. et al. 2010, \apj, 710, 903 
 \bibitem[Riebe(2013)]{riebe13} Riebe, K. et al. 2013, AN, 334, 691 				%2013AN....334..691R
-\bibitem[Willott(2013)]{willott13} Willott, Chris J. et al. 2013, \aj, 145, 4%2013AJ....145....4W
+\bibitem[Steidel(2003)]{steidel03} Steidel, Charles C. et al. 2003, \apj, 592, 728 		%2003ApJ...592..728S
+\bibitem[Willott(2013)]{willott13} Willott, Chris J. et al. 2013, \aj, 145, 4			%2013AJ....145....4W
 

### 2014-06-19 paper/discussion.tex
UV luminosity - SFR

\section{Discussion}

\begin{figure}
\epsscale{1.00}
\plotone{fig/cosmic_variance.pdf}
\caption{Cosmic Variance: The Luminosity Function is made using the DMH catalog 
from the full box and the set of parameters from the small boxes.}
\label{graph_cosmic_variance}
\end{figure}

Q: Mpc/h ?

### 2014-06-19 paper/draft.tex
UV luminosity - SFR

--- 2014-02-22 paper/draft.tex
@@
 %\documentclass[preprint2]{aastex}
+%\usepackage{graphicx}
+%\usepackage{graphics}
+%\usepackage[dvips]{epsfig}
+\usepackage{epstopdf}
+
 \newcommand{\vdag}{(v)^\dagger}
@@
 
-\shorttitle{A Connection Between Star Formation Rate and Dark Matter Halos at Z \~ 6}
+\shorttitle{A Connection Between Star Formation Rate and Dark Matter Halos at Z 
+\~ 6}
 \shortauthors{G\'omez-Cort\'es}
@@
 
-\title{A Connection Between Star Formation Rate and Dark Matter Halos at $Z\sim6$ Using 2013 Plank Cosmology.}
+\title{A Connection Between Star Formation Rate and Dark Matter Halos at 
+$Z\sim6$ In 2013 Planck Cosmology.}
 
@@
 \begin{abstract}
-This work relates baryonic matter and dark matter at high redshift using observational data
-from the HST and results of the Multidark Simulation.
-Luminosity Function - Dark Matter Halos, Star Formation Rate - Dark Matter Halos.
+This work relates baryonic matter and dark matter at redshift $z=5.9$ using 
+observational data from CFHTLS \citep{willott13}, HUDF09 
+\citep{bouwens06,bouwens12}, UKIDSS and SDXS \citep{mclure09}, and results of 
+the Multidark Simulation \citep{riebe13} in a cubic box of $1000 \textrm{Mpc 
+h}^{-1}$ length with 2013 Planck Cosmology. The Luminosity Function (LF) is 
+fitted via four parameters with the Markov Chain Monte Carlo method. The 
+relationship between the Dark Matter Halos Mass and Star Formation Rate is 
+obtained using the relationship between the UV  continuum (from the fitted LF) 
+and Star Formation Rate (SFR) by \cite{kennicutt98}.Cosmic variance effects are 
+studied on smaller boxes of $250 \textrm{Mpc h}^{-1}$ length.
+
+%Luminosity Function - Dark Matter Halos, Star Formation Rate - Dark Matter 
+Halos.
 \end{abstract}
+\keywords{Dark Matter, LF, SFR, High Redshift Galaxies, Reionization}
 
-\keywords{LF, SFR, high redshift galaxies, reionization}
+\include{introduction}
 
-\section{Introduction}
-\subsection{Halo Mass Function (HMF)}
-The HMF is created using the DMH catalog from the Multidark Database.
-\subsection{Cosmic Variance}
-Is important to know and understand the existence of local fluctuations
-or inhomogeneities due the observed scale.
+\include{star_formation_rate}
 
-For this part is necesary to study the HMF on smaller boxes
+\include{fitting_model}
 
-\section{Relationship between Galaxy Luminosity Function (GLF) and
-Dark Matter Halo (DMH) mass}
+\include{observations}
 
-In one hand we have observational results: the GLF for star-forming galaxies at high redshift (z=5.9)\citep{bouwens06,willott07}
-expressed in terms of magnitude in the ultraviolet range (M1350). In the other hand we have a DMH 
-catalog, result from the Multidark Simulation with Plank Cosmology. %\citep{Multidark}
-
-A $1000 \textrm{ Mpc} ^3 \textrm{h}^{−3}$ cubic box containing near to $11\times10^6$ dark matter halos.
-
-The idea is to connect the observed GLF with the DMH catalog. We assume that each halo contains one and just one galaxy, and its luminosity is given by:
-\begin{equation}
-L_\textrm{galaxy}=\alpha M_\textrm{halo}^\beta 
-\end{equation}
-but this function is given in magnitude units. Is necesary to convert magnitude to luminosity.
-
-\section{Magnitude to Luminosity}
-The Luminosity is an intrinsic propertie of the stars. It doesn't deppends of the distance. 
-It's directly related to the energy flux emmited. The luminosity $L_\nu$ at a given frecuency 
-$\nu$ is has $[\textrm{W}\textrm{Hz}^{-1}]$ or $[\textrm{erg }\textrm{s}^{-1}\textrm{Hz}^{-1}]$ units.
-
-The magnitude is brightnes star classification inherited from ancient Greeks. It deppends of 
-the stellar distance. The absolute magnitude is a modern classification independent of 
-distance. Taking the Sun as reference, the absolute magnitud at a given wavelengt is given by: 
-\[ M_{\lambda} = M_{\lambda \odot} - 2.5 \log_{10}\left( \frac{L_\lambda}{L_{\lambda \odot}} \right) \]
-The solar absolute magnitude in the U filter is:
-\[ M_{\textrm{U} \odot} = 5.61\]
-and the luminosity:
-\[ 1 L_{\textrm{U} \odot} = 10^{18.48} \textrm{ergs s}^{-1}\textrm{Hz}^{-1}\]
-\[ 1 L_{\textrm{U} \odot} = 3.02 \times 10^{18} \textrm{ergs s}^{-1}\textrm{Hz}^{-1}\]
-Replacing in the absolute magnitude equation:
-\[ M_{\textrm{U}} = 5.61 - 2.5 \log_{10}(L_{\textrm{U}}) + 25\times18.48\]
-gives:
-\[ M_{\textrm{U}} = 51.82 - 2.5 \log_{10}(L_{\textrm{U}}) \]
-
-\subsection{Best Fitting Parameters}
-
-\huge
-A big mistake.
-
-\[\log \neq \log_{10}\]
-\normalsize
-
---Here comes the fitting graph--
-
-And the fitting parameters
-
-$\alpha = ?$
-
-$\beta = ?$
-
-\section{Stelar Formation Rate}
-
-\subsection{The UV Continuum}
-The UV region is dominated by big blue young stars, is possible to make an extrapolation to small young stars.
-
-On stellar-formation galaxies the spectrum has a UV continuum nearly flat. This is a good approximation:
-
-$ \textrm{SFR}\left(M_\odot \textrm{yr}^{-1}\right) = 1.4 \times 10^{28} L_{\nu} \left( \textrm{erg s}^{-1}\textrm{Hz}^{-1} \right)$
-
-With Initial Mass Function (IMF) between $0.1 M_\odot$ and $100 M_\odot$, in the range of $1250-2500 \mathring{\textrm{A}} $
-
-\subsection{The Fitting Model}
-
-This fitting model contains four parameters: $\left(m/M\right)_0$, $M_1$, $\beta$ and $\gamma$, 
-where $m:=$ Stellar mass, and $M :=$ Dark Matter Halo mass.
-\begin{equation}
-\frac{m}{M} = 2 \left( \frac{m}{M} \right)_{0} 
-		  \left[ \left(\frac{M}{M_1}\right)^{-\beta} + \left(\frac{M}{M_1}\right)^{\gamma} \right]^{-1} 
-\end{equation}
-Another model cited in the article contains five parameters: $m_0$, $M_1$, $\beta$, $\gamma_1$ and $\gamma_2$.
-\[ m(M) = m_0 \frac{ (M/M_1)^{\gamma_1}}{ \left[ 1 + (M/M_1)^\beta \right]^{ (\gamma_1-\gamma_2)/\beta}} \]
-
-\section{Observations}
-
-Willott
-
-Bowens
-
-McLure
-
-\section{Discussion}
+\include{discussion}
 
@@
 \section{Appendix material}
+DEXTER \url{http://dc.zah.uni-heidelberg.de/dexter/ui/ui/custom}
 
-\begin{thebibliography}{}
-\bibitem[Bouwens(2006)]{bouwens06} Bouwens, R. J. et al. 2006, \apj, 653, 53
-\bibitem[Willot(2007)]{willott07} Willott, Chris J. et al. 2013, \aj, 145, 4
-\end{thebibliography}
+\include{the_bibliography}
 

### 2014-06-19 paper/fitting_model.tex
UV luminosity - SFR

\section{The Fitting Model}

  This fitting model contains four parameters: $\left(m/M\right)_0$, $M_1$, 
$\beta$ and $\gamma$, 
  where $m:=$ Stellar mass, and $M :=$ Dark Matter Halo mass.
  \begin{equation}
  \frac{m}{M} = 2 \left( \frac{m}{M} \right)_{0} 
		    \left[ \left(\frac{M}{M_1}\right)^{-\beta} + 
\left(\frac{M}{M_1}\right)^{\gamma} \right]^{-1} 
  \end{equation}
  This is similar to the proposed by \cite{moster10}.
  Another model cited in the article contains five parameters: $m_0$, $M_1$, 
$\beta$, $\gamma_1$ and $\gamma_2$.
  \[ m(M) = m_0 \frac{ (M/M_1)^{\gamma_1}}{ \left[ 1 + (M/M_1)^\beta \right]^{ 
(\gamma_1-\gamma_2)/\beta}} \]

   ``We use a statistical approach to determine the relationship between the 
stellar masses of galaxies and the masses
  of the dark matter halos in which they reside. We obtain a parameterized 
stellar-to-halo mass (SHM) relation by
  populating halos and subhalos in an N-body simulation with galaxies and 
requiring that the observed stellar mass
  function be reproduced.'' \citep{moster10}

### 2014-06-19 paper/introduction.tex
UV luminosity - SFR

\section{Introduction}

Dark matter is a significative component of the universe.

\citep{trimble87}

Hierarchy Structure Evolution: Early formation of small structures
merging on major structures after.

From simulations, Halo Mass Function as function of redshift (or time).

Star formation rate as function of time. Peak at $z\sim 2$.

Main Objetive: Reproduce the observed luminosity function at redshift $z=5.9$
from a DMH catalog from simulations.

  \subsection{Halo Mass Function (HMF)}

  The HMF is created using the DMH catalog from the Multidark Database 
\citep{riebe13}.

  \subsection{Cosmic Variance}

  Is important to know and understand the existence of local fluctuations   or 
inhomogeneities due the observed scale.  For this part is necesary to study the 
HMF on smaller boxes

\section{Relationship between Galaxy Luminosity Function (GLF) and
  Dark Matter Halo (DMH) mass}

  In one hand we have observational results: the GLF for star-forming galaxies 
at high redshift (z=5.9)\citep{bouwens06,willott13}  expressed in terms of 
magnitude in the ultraviolet range (M1350). In the other hand we have a DMH  
catalog, result from the Multidark Simulation with Plank Cosmology. 
%\citep{Multidark}

  A $1000 \textrm{ Mpc} ^3 \textrm{h}^{−3}$ cubic box containing near to  
$11\times10^6$ dark matter halos.

  The idea is to connect the observed GLF with the DMH catalog. We assume that  
each halo contains one and just one galaxy, and its luminosity is given by:
  \begin{equation}
  L_\textrm{galaxy}=\alpha M_\textrm{halo}^\beta 
  \end{equation}
but this function is given in magnitude units. Is necesary to convert 
magnitude to luminosity.

  \subsection{Magnitude to Luminosity}
  The Luminosity is an intrinsic propertie of the stars. It doesn't deppends of 
the distance.  It's directly related to the energy flux emmited. The luminosity 
$L_\nu$ at a given frecuency $\nu$ has $[\textrm{W}\textrm{Hz}^{-1}]$ or 
$[\textrm{erg}\textrm{s}^{-1}\textrm{Hz}^{-1}]$ units.

  The magnitude is brightnes star classification inherited from ancient Greeks. 
It deppends of the stellar distance. The absolute magnitude is a modern 
classification independent of  distance. Taking the Sun as reference, the 
absolute magnitud at a given wavelengt is given by: 
 \[ M_{\lambda} = M_{\lambda \odot} - 2.5 \log_{10}\left( 
\frac{L_\lambda}{L_{\lambda \odot}} \right) \]
  The solar absolute magnitude in the U filter is $M_{U\odot} = 5.61$,
and the solar luminosity in the same filter is $L_{U\odot} = 10^{18.48} 
\textrm{ergs s}^{-1}\textrm{Hz}^{-1}$ or $ L_{U\odot} = 3.02 \times 10^{18} 
\textrm{ergs s}^{-1}\textrm{Hz}^{-1}$.

  Replacing in the absolute magnitude equation:
  \[ M_{U} = 5.61 - 2.5 \log_{10}(L_{U}) + 2.5\times18.48\]
  gives the magnitude in the U filter of an astrophysical source:
  \[ M_{U} = 51.82 - 2.5 \log_{10}(L_{U}) \]

  \subsection{Best Fitting Parameters}

### 2014-06-19 paper/observations.tex
UV luminosity - SFR

\section{Observations}

The dataset was retrieved from graphs for \cite{bouwens14} and \cite{mclure09} 
using DEXTER
\url{http://dc.zah.uni-heidelberg.de/dexter/ui/ui/custom}

\begin{figure}
\epsscale{1.00}
\plotone{fig/observational_data.pdf}
\caption{Observational data from \cite{bouwens14,mclure09}and \cite{willott13}.}
\label{graph_observational_data}
\end{figure}

  \subsection{CFHTLS}

  CFHTLS - Canada-France-Hawaii Telescope Legacy Survey - 
MegaCam\citep{willott13}

  ``We identify a sample of 40 Lyman break galaxies brighter than
    magnitude z ′ = 25.3 across an area of almost 4 square degrees.
    Sensitive spectroscopic observations of seven galaxies provide 
    redshifts for four, of which only two have moderate to strong 
    Lyα emission lines. All four have clear continuum breaks in 
    their spectra.'' \cite{willott13}.

  ``The imaging data used to select high-redshift galax-
    ies come primarily from the 3.6 m Canada-France-Hawaii
    Telescope. Optical observations with MegaCam in the
    u ∗ g ′ r ′ i ′ z ′ filters are from CFHTLS Deep which covered
    four ≈ 1 square degree fields with typical total integra-
    tion time of 75 ks in u ∗ , 85 ks in g ′ , 145 ks in r ′ , 230 ks in
    i ′ and 175 ks in z ′ . The seeing in the final stacks at i ′ and
    z ′ range from 0.66 to 0.76 arcsec. The data used here are
    from the 6th data release, T0006, which contains all the
    data acquired over the five years of the project '' \cite{willott13}.

  ``These optical data are complemented by near-IR data
    from the WIRCam Deep Survey (WIRDS; Bielby et al.
    2012). WIRDS used the WIRCam near-IR imager at
    the CFHT'' \cite{willott13}.

   About the Luminosity function: sect 6.3
   ``Because our LBG sample covers only a limited range of
    apparent and absolute magnitudes, we cannot use it to determine
    the full galaxy luminosity function at z = 6. The luminosity
    function at the break and at fainter magnitudes has already
    been well studied from deep HST surveys over small sky areas
    (Bouwens et al. 2007). The main contribution of our study is
    to determine the space density of very rare, highly luminous
    LBGs.''\cite{willott13}.

  \subsection{HUDF09}

  ``Table 1 summarizes the search fields used for the z ∼ 5-
    8 LF determinations and the approximate depths of the
    available ACS+WFC3/IR observations. Our primary
    data set consists of the full two-year WFC3/IR obser-
    vations of the HUDF and two flanking fields obtained
    with the 192-orbit HUDF09 program (PI Illingworth:
    GO 11563). Our second data set is the ∼145 arcmin 2
    ACS+WFC3/IR observations over the wide-area Early
    Release Science (Windhorst et al. 2011) and CDF-South
    CANDELS'' \cite{bouwens12}

  ``A detailed summary of the ACS HUDF, HUDF-Ps, and GOODS
    data we use for our dropout selections is provided in our previous
    work ( B06). Nevertheless, a brief description of the data is in-
    cluded here. The ACS HUDF data we use are the version 1.0 re-
    ductions of Beckwith et al. (2006) and extend to 5  point-source
    limits of 29Y30 in the B 435 V 606 i 775 z 850 bands. The HUDF-Ps re-
    ductions we use are from B06 and take advantage of the deep
    (k72 orbit) BViz ACS data fields taken in parallel with the HUDF
    NICMOS program (Thompson et al. 2005). Together the parallel
    data from this program sum to create two very deep ACS fields
    that we can use for dropout searches. While of somewhat var-
    iable depths, the central portions of these fields (12Y20 arcmin 2 )
    reach some 0.6Y0.9 mag deeper than the data in the original ACS
    GOODS program (Giavalisco et al. 2004a). Finally, for the ACS
    GOODS reductions, we use an updated version of those generated
    for our previous z 6 study (B06).'' \cite{bouwens06}

  \subsection{UKIDSS \& SDXS}
    ``The UDS is the deepest of five near-IR surveys currently underway
      at the UK InfraRed Telescope (UKIRT) with the new WFCAM
      imager (Casali et al. 2007) which together comprise the UKIDSS
      (Lawrence et al. 2007). The UDS covers an area of 0.8 deg 2 cen-
      tred on RA = 02:17:48, Dec. = −05:05:57 (J2000) and is already
      the deepest, large area, near-IR survey ever undertaken. The data
      utilized in this paper were taken from the first UKIDSS Data Re-
      lease (DR1; Warren et al. 2007), which included JK imaging of the
      entire UDS field to 5σ depths of J = 23.9, K = 23.8 (1.6 arcsec
      diameter apertures). The UKIDSS DR1 became publicly available
      to the world wide astronomical community in 2008 January and can
      be downloaded from the WFCAM Science Archive. 2
      The UDS field is covered by a wide variety of deep, multiwave-
      length observations ranging from the X-ray through to the radio (see
      Cirasuolo et al. 2008 for a recent summary). However, for this study
      the most important multiwavelength observations are the deep op-
      tical imaging of the field taken with Suprime-Cam (Miyazaki et al.
      2002) on Subaru as part of the Subaru/XMM–Newton Deep Survey
      (Sekiguchi et al. 2005). The optical imaging consists of five over-
      lapping Suprime-Cam pointings, and covers an area of 1.3 deg 2 .
      The whole field has been imaged in the BV Ri z filters, to typical
      5σ depths of B = 27.9, V = 27.4, R = 27.2, i = 27.2 and z = 26.2
      (1.6 arcsec diameter apertures). The reduced optical imaging of the
      SXDS is now publicly available 3 and full details of the observations,
      data reduction and calibration procedures are provided in Furusawa
      et al. (2008). The high-redshift galaxies investigated in this study
      were selected from a contiguous area of 0.63 deg 2 (excluding areas
      contaminated by bright stars and CCD blooming) covered by both
      the UDS near-IR and SXDS optical imaging.'' \cite{mclure09}

\subsection{The Drop-out Technique - Lyman Break Technique}

\cite{steidel03}

### 2014-06-19 paper/star_formation_rate.tex
UV luminosity - SFR

\section{Star Formation Rate}

On the study of far galaxies individual stellar spectrum is unresolved, is not 
possible to make a detailed census of the galaxy popullation. Only is possible 
to get information from the whole stellar population, an integrated spectrum.

Kennicutt pruposed a method in wich a linear relation between luminosity and 
SFR can be assumed. This model allows to estimate the young stars fraction and 
the mean SFR over periods of $10^8 - 10^9 \textrm{yr}$. The luminosity in the 
modfel, comes from the UV and the FIR broadband, also from speciffic 
recombination lines.

In a typical galaxy spectrum the visible wavelengths are dominated by the main 
sequence stars (A to early F) and G-K giants. In few wavelength ranges we have 
a significative contribution from the young stars rather than the old stars. 
The infrared and far infrared wavelengths emission is dominated by dust, this 
dust is  heated by the whole stellar popullation, in particular by young, 
UV-bright stars \citep{law11}.The UV broadband emission is dominated by blue 
stars with temperature near to 40.000K. These hot and massive stars has a 
lifetime of $10^8\textrm{Gyr}$, they spend their nuclear fuel faster than smaller 
and cooler sunlike stars.

The relation between UV luminosity and Star Formation Rate \citep{kennicutt98} 
is given by:
  $ \textrm{SFR}\left(M_\odot \textrm{yr}^{-1}\right) 
      = 1.4 \times 10^{28} L_{\nu} \left( \textrm{erg s}^{-1}\textrm{Hz}^{-1} 
\right)$
  With Initial Mass Function (IMF) between $0.1 M_\odot$ 
  and $100 M_\odot$, in the range of $1250-2500 \mathring{\textrm{A}} $

The UV dust absorption \citep{kennicutt09} is not taken account in this work.

%Synthesis Models:
%1) Study individual star spectra, star atmospheres. Creation of spectral 
%libraries.
%2) ``Individual stellar templates are summed together weigthed by an initial 
%mass function (IMF)... These isochrones can the be added in linear combination 
%to syntesize the spectrum or colors of a galaxy with any arbitrary star 
%formation history, usually parametrized as an expinential function of time.
%*** A single model contains at least 4 parameters (SF history, galaxy age, 
%metal abundance, and IMF). The colors of normal galaxies are well represented 
%by a one-parameter sequence with fixed age, composition and IMF, varying in the 
%time dependence of the SFR****

### 2014-06-19 paper/the_bibliography.tex
UV luminosity - SFR

\begin{thebibliography}{}
\bibitem[Bouwens(2006)]{bouwens06} Bouwens, R. J. et al. 2006, \apj, 653, 53	
		%2006ApJ...653...53B
\bibitem[Bouwens(2012)]{bouwens12} Bouwens, R. J. et al. 2012, \apj, 752, 5 	
		%2012ApJ...752L...5B
\bibitem[Bouwens(2014)]{bouwens14} Bouwens, R. J. et al. 2012, arXiv:1403.4295
\bibitem[Kennicutt(1998)]{kennicutt98} Kennicutt, Robert C., Jr. 1998, \araa, 
36, 189		%1998ARA&A..36..189K
\bibitem[Kennicutt(2009)]{kennicutt09} Kennicutt, Robert C., Jr et al. 2009, \apj, 
703, 4672	%2009ApJ...703.1672K
\bibitem[Law(2011)]{law11} Law, K. et al. 2011, \apj, 738, 124
		%2011ApJ...738..124L
\bibitem[McLure(2009)]{mclure09} McLure, R. J. et al. 2009, \mnras, 395, 2196	
		%2009MNRAS.395.2196M
\bibitem[Moster(2010)]{moster10} Moster, Benjamin P. et al. 2010, \apj, 710, 
903 
\bibitem[Riebe(2013)]{riebe13} Riebe, K. et al. 2013, AN, 334, 691 		
		%2013AN....334..691R
\bibitem[Steidel(2003)]{steidel03} Steidel, Charles C. et al. 2003, \apj, 592, 
728 		%2003ApJ...592..728S
\bibitem[Trimble(1987)]{trimble87} Trible, Virginia. 1987, \araa, 25, 425
\bibitem[Willott(2013)]{willott13} Willott, Chris J. et al. 2013, \aj, 145, 4	
		%2013AJ....145....4W

\end{thebibliography}

### 2014-06-20 paper/fitting_model.tex
SFR, Fitting Model, The_Bibliography

@@
 \section{The Fitting Model}
+The model links dark matter and U-luminosity by a four parameter function.
+For each galaxy we have the luminosity:
+  \begin{equation}
+  L = L_{0} M \left[ \left( \frac{M}{M_0}\right)^{-\beta} 
+		   + \left( \frac{M}{M_0}\right)^{\gamma} 
+               \right]^{-1}
+  \end{equation}
+where $M$ is the hosting DMH mass, $L_{0}$ is a normalization constant, $M_0$
+is the critical mass where the luminosity function has a slope change, 
+$\beta$ and $\gamma$ are the slopes.
+This relation can reproduce the luminosity function with best agreement than the classical Schechter function wich works good for low redshift galaxies.
 
-  This fitting model contains four parameters: $\left(m/M\right)_0$, $M_1$, 
-$\beta$ and $\gamma$, 
-  where $m:=$ Stellar mass, and $M :=$ Dark Matter Halo mass.
-  \begin{equation}
-  \frac{m}{M} = 2 \left( \frac{m}{M} \right)_{0} 
-		    \left[ \left(\frac{M}{M_1}\right)^{-\beta} + 
-\left(\frac{M}{M_1}\right)^{\gamma} \right]^{-1} 
-  \end{equation}
-  This is similar to the proposed by \cite{moster10}.
-  Another model cited in the article contains five parameters: $m_0$, $M_1$, 
-$\beta$, $\gamma_1$ and $\gamma_2$.
-  \[ m(M) = m_0 \frac{ (M/M_1)^{\gamma_1}}{ \left[ 1 + (M/M_1)^\beta \right]^{ 
-(\gamma_1-\gamma_2)/\beta}} \]
-
-   ``We use a statistical approach to determine the relationship between the 
-stellar masses of galaxies and the masses
-  of the dark matter halos in which they reside. We obtain a parameterized 
-stellar-to-halo mass (SHM) relation by
-  populating halos and subhalos in an N-body simulation with galaxies and 
-requiring that the observed stellar mass
-  function be reproduced.'' \citep{moster10}
+This equation has a similar fashion to the mass to light relation \citep{vandenbosch03} and the mean relation between stellar mas of a galaxy and the mas of its halo used by \cite{moster10}.

### 2014-06-20 paper/introduction.tex
SFR, Fitting Model, The_Bibliography

@@
 
-  The HMF is created using the DMH catalog from the Multidark Database 
-\citep{riebe13}.
+%  The HMF is created using the DMH catalog from the Multidark Database 
+%\citep{riebe13}.
 
@@
 
-  Is important to know and understand the existence of local fluctuations   or 
-inhomogeneities due the observed scale.  For this part is necesary to study the 
-HMF on smaller boxes
+%  Is important to know and understand the existence of local fluctuations   or 
+%inhomogeneities due the observed scale.  For this part is necesary to study the 
+%HMF on smaller boxes
 
-\section{Relationship between Galaxy Luminosity Function (GLF) and
+\section{Linking Galaxy Luminosity Function (GLF) and
   Dark Matter Halo (DMH) mass}
 
-  In one hand we have observational results: the GLF for star-forming galaxies 
-at high redshift (z=5.9)\citep{bouwens06,willott13}  expressed in terms of 
-magnitude in the ultraviolet range (M1350). In the other hand we have a DMH  
-catalog, result from the Multidark Simulation with Plank Cosmology. 
+%  In one hand we have observational results: the GLF for star-forming galaxies 
+%at high redshift (z=5.9)\citep{bouwens06,willott13}  expressed in terms of 
+%magnitude in the ultraviolet range (M1350). In the other hand we have a DMH  
+%atalog, result from the Multidark Simulation with Plank Cosmology. 
 %\citep{Multidark}
 
-  A $1000 \textrm{ Mpc} ^3 \textrm{h}^{−3}$ cubic box containing near to  
-$11\times10^6$ dark matter halos.
+ % A $1000 \textrm{ Mpc} ^3 \textrm{h}^{−3}$ cubic box containing near to  
+%$11\times10^6$ dark matter halos.
 
-  The idea is to connect the observed GLF with the DMH catalog. We assume that  
-each halo contains one and just one galaxy, and its luminosity is given by:
-  \begin{equation}
-  L_\textrm{galaxy}=\alpha M_\textrm{halo}^\beta 
-  \end{equation}
-but this function is given in magnitude units. Is necesary to convert 
-magnitude to luminosity.
+%  The idea is to connect the observed GLF with the DMH catalog. We assume that  
+%each halo contains one and just one galaxy, and its luminosity is given by:
+%  \begin{equation}
+%  L_\textrm{galaxy}=\alpha M_\textrm{halo}^\beta 
+%  \end{equation}
+%but this function is given in magnitude units. Is necesary to convert 
+%magnitude to luminosity.
 
 \subsection{Magnitude to Luminosity}
-  The Luminosity is an intrinsic propertie of the stars. It doesn't deppends of 
-the distance.  It's directly related to the energy flux emmited. The luminosity 
-$L_\nu$ at a given frecuency $\nu$ has $[\textrm{W}\textrm{Hz}^{-1}]$ or 
-$[\textrm{erg}\textrm{s}^{-1}\textrm{Hz}^{-1}]$ units.
 
-  The magnitude is brightnes star classification inherited from ancient Greeks. 
-It deppends of the stellar distance. The absolute magnitude is a modern 
-classification independent of  distance. Taking the Sun as reference, the 
-absolute magnitud at a given wavelengt is given by: 
+Luminosity Functions (LF) are usually expressed in terms of magnitude instead 
+luminosity. Luminosity is the energy emmited by a source in a given wavelengt range, 
+is a physical quantity. 
+%The luminosity 
+%$L_\nu$ at a given frecuency $\nu$ has $[\textrm{W}\textrm{Hz}^{-1}]$ or 
+%$[\textrm{erg}\textrm{s}^{-1}\textrm{Hz}^{-1}]$ units.
+Magnitude is a classification inherited from ancient Greeks, this
+quantifies the response of the first astrometric device: the human eye, this
+perception grows loarithmically with the retrieved radiation.
+
+Taking the Sun as reference, the absolute magnitud at a given wavelengt is given by: 
  \[ M_{\lambda} = M_{\lambda \odot} - 2.5 \log_{10}\left( 
@@
 \textrm{ergs s}^{-1}\textrm{Hz}^{-1}$ or $ L_{U\odot} = 3.02 \times 10^{18} 
-\textrm{ergs s}^{-1}\textrm{Hz}^{-1}$.
+\textrm{ergs s}^{-1}\textrm{Hz}^{-1}$. The solar luminosity can be used as
+refference unit, in this fashion, the typical luminosity of a galaxy can be expresed in
+terms of $10^{8}-10^{11}$ times the sun luminosity.
 
-  Replacing in the absolute magnitude equation:
-  \[ M_{U} = 5.61 - 2.5 \log_{10}(L_{U}) + 2.5\times18.48\]
-  gives the magnitude in the U filter of an astrophysical source:
+  The absolute magnitude of a galaxy equation in the U filter:
+  %\[ M_{U} = 5.61 - 2.5 \log_{10}(L_{U}) + 2.5\times18.48\]
+  %gives the magnitude in the U filter of an astrophysical source:
   \[ M_{U} = 51.82 - 2.5 \log_{10}(L_{U}) \]
 
-  \subsection{Best Fitting Parameters}
+ %\subsection{Best Fitting Parameters}

### 2014-06-30 paper/fitting_model.tex
adding references
LF model

@@
-\section{The Fitting Model}
-The model links dark matter and U-luminosity by a four parameter function.
-For each galaxy we have the luminosity:
+\subsection{The Luminosity Model}
+
+In this model we have made two assumptions:
+\begin{enumerate}
+ \item Each halo in the catalog hosts one galaxy. There are not empty
+halos, also none of halos has two or more galaxies.
+ \item The UV luminosity of each galaxy is function of one variable: the mass of
+the DMH in wich is located.
+\end{enumerate}
+
+The simplest relation we can have is a powerlaw:
+ \begin{equation}
+  L = L_0 M^\alpha
+ \end{equation}
+but has not well agreement with observed luminosity functions.
+
+A better model is a four parameter function. Each galaxy has a luminosity given
+by:
   \begin{equation}
@@
 is the critical mass where the luminosity function has a slope change, 
-$\beta$ and $\gamma$ are the slopes.
-This relation can reproduce the luminosity function with best agreement than the classical Schechter function wich works good for low redshift galaxies.
+$\beta$ and $\gamma$ are the slopes. This equation has a similar fashion to the
+mass to light relation \citep{vandenbosch03} and the mean relation between
+stellar mas of a galaxy and the mas of its halo used by \cite{moster10}.
 
-This equation has a similar fashion to the mass to light relation \citep{vandenbosch03} and the mean relation between stellar mas of a galaxy and the mas of its halo used by \cite{moster10}.
+There are more complex models\citep{lee09} that includes a random behavior:
+galaxies has not synchronization on the beginning of star forming stage, also
+this stage may be time limited. This is called duty cycle. It is probable to
+have in the observations some invisible galaxies in the UV continuum due their
+duty cycle may has not started as well it may ended. Also may be present a
+normal distribution of the luminosity around the expected values.

### 2014-06-30 paper/star_formation_rate.tex
SFR, Fitting Model, The_Bibliography
LF model

@@
-\section{Star Formation Rate}
+\subsection{Star Formation Rate}
 
-On the study of far galaxies individual stellar spectrum is unresolved, is not 
+The age of a star can be estimated by analyzing its spectrum. But when far
+galaxies are studied, individual stars can not be resolved. Is not 
 possible to make a detailed census of the galaxy popullation. Only is possible 
@@
 
-Kennicutt pruposed a method in wich a linear relation between luminosity and 
-SFR can be assumed. This model allows to estimate the young stars fraction and 
-the mean SFR over periods of $10^8 - 10^9 \textrm{yr}$. The luminosity in the 
-modfel, comes from the UV and the FIR broadband, also from speciffic 
-recombination lines.
+Kennicutt pruposed a method in wich a linear relation between SFR and
+luminosity in specific wavelength ranges can be assumed. This model allows to
+estimate the young stars fraction and the mean SFR over periods of $10^8 - 10^9
+\textrm{yr}$. The luminosity in the model, comes from the UV and the FIR
+broadband, also from speciffic recombination lines.
 
@@
 
+The star forming rate will be:
+  \begin{equation}
+  SFR = k \times L_{0} M \left[ \left( \frac{M}{M_0}\right)^{-\beta} 
+		   + \left( \frac{M}{M_0}\right)^{\gamma} 
+               \right]^{-1}
+  \end{equation}
+
 The UV dust absorption \citep{kennicutt09} is not taken account in this work.
+
+DUST EXTINTION ALSO STUDIED by 002-TACCHELLA-A Physical Model for ---
 

### 2014-07-01 paper/introduction.tex
paper: intro, observations, bibliography

@@
 \section{Introduction}
+Cosmological simulations still playing an important role on astrophysics and
+cosmology. They have become the bridge between observations and theory, a
+laboratory where is possible to create universes with different parameters and
+new physics.
 
+This is an important tool in the study of dark matter. Since its existence was
+purposed, DM has been not observed directly neither on telescopes or high energy
+particle colliders, there exists many other theories explaining the observed
+universe behavior modifying the gravity itself.
+
+The most successful and accepted cosmological model is the Lambda-CDM. 
 Dark matter is a significative component of the universe.
-
 \citep{trimble87}
@@
 From simulations, Halo Mass Function as function of redshift (or time).
+
+In this paper is established a relation between dark matter and galaxy
+luminosity functions at high redshifrt. This relation is a direct
+connection between the Lambda-CDM model and the farthest galaxy observations
+made with space and grounded telescopes.
 
@@
 
-Taking the Sun as reference, the absolute magnitud at a given wavelengt is given by: 
+Luminosity of any object can be compared with Sun Luminosity $(L_{\lambda
+\odot})$ at any wavelengt. With the Sun Magnitude as reference
+$(M_{\lambda \odot})$, the absolute magnitud of the objet  at an specific
+wavelengt is given by: 
  \[ M_{\lambda} = M_{\lambda \odot} - 2.5 \log_{10}\left( 

### 2014-07-01 paper/observations.tex
paper: intro, observations, bibliography

@@
 
+This paper is based on three main observation sets. The most recent is from the
+Hubble Space Telescope, this observations where performed by \cite{bouwens14}.
+The second set is from the Canada-France Hawaii Telescope, \cite{willott13} and
+the last one by the UK Infrared Telescope and the Subaru Telescope
+\cite{mclure09}. Those observations where made using the Frop-out technique.
+
+The data from the HST is a compilation of previous works since
+2006 \citep{bouwens06}, wich includes also observations after the 2009
+upgrade mission\citep{bouwens12}.
+
 The dataset was retrieved from graphs for \cite{bouwens14} and \cite{mclure09} 
-using DEXTER
-\url{http://dc.zah.uni-heidelberg.de/dexter/ui/ui/custom}
+using
+GAVO-DEXTER\footnote{\url{http://dc.zah.uni-heidelberg.de/dexter/ui/ui/custom}}.
 
@@
 
-  \subsection{CFHTLS}
-
-  CFHTLS - Canada-France-Hawaii Telescope Legacy Survey - 
-MegaCam\citep{willott13}
-
-  ``We identify a sample of 40 Lyman break galaxies brighter than
-    magnitude z ′ = 25.3 across an area of almost 4 square degrees.
-    Sensitive spectroscopic observations of seven galaxies provide 
-    redshifts for four, of which only two have moderate to strong 
-    Lyα emission lines. All four have clear continuum breaks in 
-    their spectra.'' \cite{willott13}.
-
-  ``The imaging data used to select high-redshift galax-
-    ies come primarily from the 3.6 m Canada-France-Hawaii
-    Telescope. Optical observations with MegaCam in the
-    u ∗ g ′ r ′ i ′ z ′ filters are from CFHTLS Deep which covered
-    four ≈ 1 square degree fields with typical total integra-
-    tion time of 75 ks in u ∗ , 85 ks in g ′ , 145 ks in r ′ , 230 ks in
-    i ′ and 175 ks in z ′ . The seeing in the final stacks at i ′ and
-    z ′ range from 0.66 to 0.76 arcsec. The data used here are
-    from the 6th data release, T0006, which contains all the
-    data acquired over the five years of the project '' \cite{willott13}.
-
-  ``These optical data are complemented by near-IR data
-    from the WIRCam Deep Survey (WIRDS; Bielby et al.
-    2012). WIRDS used the WIRCam near-IR imager at
-    the CFHT'' \cite{willott13}.
-
-   About the Luminosity function: sect 6.3
-   ``Because our LBG sample covers only a limited range of
-    apparent and absolute magnitudes, we cannot use it to determine
-    the full galaxy luminosity function at z = 6. The luminosity
-    function at the break and at fainter magnitudes has already
-    been well studied from deep HST surveys over small sky areas
-    (Bouwens et al. 2007). The main contribution of our study is
-    to determine the space density of very rare, highly luminous
-    LBGs.''\cite{willott13}.
-
-  \subsection{HUDF09}
-
-  ``Table 1 summarizes the search fields used for the z ∼ 5-
-    8 LF determinations and the approximate depths of the
-    available ACS+WFC3/IR observations. Our primary
-    data set consists of the full two-year WFC3/IR obser-
-    vations of the HUDF and two flanking fields obtained
-    with the 192-orbit HUDF09 program (PI Illingworth:
-    GO 11563). Our second data set is the ∼145 arcmin 2
-    ACS+WFC3/IR observations over the wide-area Early
-    Release Science (Windhorst et al. 2011) and CDF-South
-    CANDELS'' \cite{bouwens12}
-
-  ``A detailed summary of the ACS HUDF, HUDF-Ps, and GOODS
-    data we use for our dropout selections is provided in our previous
-    work ( B06). Nevertheless, a brief description of the data is in-
-    cluded here. The ACS HUDF data we use are the version 1.0 re-
-    ductions of Beckwith et al. (2006) and extend to 5  point-source
-    limits of 29Y30 in the B 435 V 606 i 775 z 850 bands. The HUDF-Ps re-
-    ductions we use are from B06 and take advantage of the deep
-    (k72 orbit) BViz ACS data fields taken in parallel with the HUDF
-    NICMOS program (Thompson et al. 2005). Together the parallel
-    data from this program sum to create two very deep ACS fields
-    that we can use for dropout searches. While of somewhat var-
-    iable depths, the central portions of these fields (12Y20 arcmin 2 )
-    reach some 0.6Y0.9 mag deeper than the data in the original ACS
-    GOODS program (Giavalisco et al. 2004a). Finally, for the ACS
-    GOODS reductions, we use an updated version of those generated
-    for our previous z 6 study (B06).'' \cite{bouwens06}
-
-  \subsection{UKIDSS \& SDXS}
-    ``The UDS is the deepest of five near-IR surveys currently underway
-      at the UK InfraRed Telescope (UKIRT) with the new WFCAM
-      imager (Casali et al. 2007) which together comprise the UKIDSS
-      (Lawrence et al. 2007). The UDS covers an area of 0.8 deg 2 cen-
-      tred on RA = 02:17:48, Dec. = −05:05:57 (J2000) and is already
-      the deepest, large area, near-IR survey ever undertaken. The data
-      utilized in this paper were taken from the first UKIDSS Data Re-
-      lease (DR1; Warren et al. 2007), which included JK imaging of the
-      entire UDS field to 5σ depths of J = 23.9, K = 23.8 (1.6 arcsec
-      diameter apertures). The UKIDSS DR1 became publicly available
-      to the world wide astronomical community in 2008 January and can
-      be downloaded from the WFCAM Science Archive. 2
-      The UDS field is covered by a wide variety of deep, multiwave-
-      length observations ranging from the X-ray through to the radio (see
-      Cirasuolo et al. 2008 for a recent summary). However, for this study
-      the most important multiwavelength observations are the deep op-
-      tical imaging of the field taken with Suprime-Cam (Miyazaki et al.
-      2002) on Subaru as part of the Subaru/XMM–Newton Deep Survey
-      (Sekiguchi et al. 2005). The optical imaging consists of five over-
-      lapping Suprime-Cam pointings, and covers an area of 1.3 deg 2 .
-      The whole field has been imaged in the BV Ri z filters, to typical
-      5σ depths of B = 27.9, V = 27.4, R = 27.2, i = 27.2 and z = 26.2
-      (1.6 arcsec diameter apertures). The reduced optical imaging of the
-      SXDS is now publicly available 3 and full details of the observations,
-      data reduction and calibration procedures are provided in Furusawa
-      et al. (2008). The high-redshift galaxies investigated in this study
-      were selected from a contiguous area of 0.63 deg 2 (excluding areas
-      contaminated by bright stars and CCD blooming) covered by both
-      the UDS near-IR and SXDS optical imaging.'' \cite{mclure09}
-
 \subsection{The Drop-out Technique - Lyman Break Technique}

### 2014-07-04 fullprogram/observational_data.py
Cumulative LF added

@@ -1,0 +1,145 @@
+# Last version: 2014-jul-03
+# Cumulative Luminosity Function added
+
+from numpy import *
+
+####################################
+#                                  #
+#     Willott observations         #
+#                                  #
+####################################
+
+HIST1_bins=[-22.75,-22.25,-21.75,-21.25,-20.75,-20.25]
+
+Willott = array( 
+[# Mag,LumFunct, low_err, upp_err #
+[-22.5, 2.66E-8, 9.08E-9, 7.78E-8],
+[-22.0, 2.18E-6, 8.70E-7, 9.70E-6],
+[-21.5, 1.45E-5, 2.88E-6, 2.92E-5],
+[-21.0, 1.29E-4, 7.06E-5, 2.19E-4],
+[-20.5, 2.30E-4, 9.34E-5,5.77E-4]
+])  
+
+Obs_data1 = zeros([5,4])
+Obs_data1_log10 = zeros([5,4])
+Obs_data1yerror = [array(Willott[:,1]-Willott[:,2]),array(Willott[:,3]-Willott[:,1])]
+
+for i in range(5):
+    Obs_data1[i,0]=Willott[i,0]
+    Obs_data1[i,1]=Willott[i,1]
+    Obs_data1[i,2]=0
+    Obs_data1[i,3]=0.25
+    Obs_data1_log10[i,0]=Willott[i,0]
+    Obs_data1_log10[i,1]=log10(Willott[i,1])
+    Obs_data1_log10[i,2]=0
+    Obs_data1_log10[i,3]=0.25
+    
+Obs_data1_log10yerror = [array(log10(Willott[:,1]/Willott[:,2])),array(log10(Willott[:,3]/Willott[:,1]))]
+sigma1 = (Obs_data1_log10yerror[:][0] +  Obs_data1_log10yerror[:][0])/2
+
+Obs_data1_cum = array([
+[-22.75 , 2.660000E-8],
+[-22.25 , 2.206600E-6],
+[-21.75 , 1.670766E-5],
+[-21.25 , 1.457066E-4],
+[-20.75 , 3.757066E-4]
+])
+
+####################################
+#                                  #
+#     Bouwens observations         #
+#                                  #
+####################################
+
[…]

### 2014-07-21 paper/discussion.tex
SFR, Fitting Model, The_Bibliography
Intro, Obs. data, SFR

@@
 
-Q: Mpc/h ?
+\citep{lundgren14} SFR evolution from $z=1$ to $6$
+
+\citep{bouwens14} HST Legacy
+
+\citep{jiang11} Keck pectroscopy
+
+``Fig. 16.— Updated Determinations of the derived SFR (left axis) and U V
+luminosity (right axis) densities versus redshift (5.4). The
+left axis gives the SFR densities we would infer from the measured luminosity
+densities, assuming the Madau et al. (1998) conversion
+factor relevant for star-forming galaxies with ages of 108 yr (see also
+Kennicutt 1998). The right axis gives the U V luminosities we infer
+integrating the present and published LFs to a faint-end limit of −17 mag (0.03
+L∗ )''BOUWENS 2014 UV LF

### 2014-07-21 paper/introduction.tex
Intro, Obs. data, SFR

@@
 
+``An important frontier in the study of very high redshift
+galaxies remains the study of their stellar populations.
+Galaxies within a few hundred million years of the Big
+Bang are expected to be quite different from galaxies at
+lower redshift, with significantly younger ages and lower
+metallicities. For very young and chemically immature
+systems, changes in the stellar population could include a
+transition to a more top-heavy IMF (e.g., Bromm \& Lar-
+son 2004), evolution in the dust composition (e.g., due to
+changes in the dust production mechanism: Maiolino et
+al. 2004), as well as a much lower dust extinction overall
+(e.g., Bouwens et al. 2009; Finlator et al. 2011; Dayal \&
+Ferrara 2012).'' BOWENS 2014 BETA SLOPE
+
 Main Objetive: Reproduce the observed luminosity function at redshift $z=5.9$
 from a DMH catalog from simulations.
+
+This paper is organized as follows: In section 2... in section 3...
 
@@
 
+``One of the most fundamental properties of galaxy sub-
+populations at any epoch is their number density. However,
+observational estimates of galaxy number densities in finite
+volumes are subject to uncertainty due to cosmic variance,
+arising from underlying large-scale density fluctuations and
+leading to uncertainties in excess of naïve Poisson errors.
+Note that this source of uncertainty is referred to as ‘sample
+variance’ in other branches of cosmology. For sampling vol-
+umes much larger than the typical clustering scale of the ob-
+served objects, cosmic variance is not significant.''A COSMIC VARIANCE COOKBOOK
+
+``However many important existing surveys have a sampling volume that
+is small enough that cosmic variance may dominate the un-
+certainties. This may be particularly true at high redshift,
+where galaxies are expected to be much more strongly clus-
+tered than dark matter (Kauffmann et al. 1999; Baugh et al.
+1999; Coil et al. 2004; Moster et al. 2009). Still, many pub-
+lished quantities which are based on number density (e.g. lu-
+minosity functions, stellar mass functions, etc.) are quoted
+with error budgets that do not properly account for cosmic
+variance. As shown by Trenti \& Stiavelli (2008), the normal-
+ization and the slope of high-redshift luminosity functions can
+be affected by cosmic variance errors.''A COSMIC VARIANCE COOKBOOK
+
+``Somerville et al. (2004) provided predictions that could be
+used to estimate cosmic variance as a function of mean red-
+shift and survey volume, using the number density of the pop-
+ulation to estimate the bias, assuming one galaxy per halo.'' A COSMIC VARIANCE
+COOKBOOK
+
+===========>>>>>>>>> COSMIC VARIANCE CALCULATOR <<<<<<<<<===============
+Results obtained using CosmicVarianceCalculator v1.02 
+Developed by Michele Trenti \& Massimo Stiavelli 
+If you use these results in scientific papers, please refer to:  
+Trenti \& Stiavelli (2008), ApJ, 676, 767
+
 \section{Linking Galaxy Luminosity Function (GLF) and
   Dark Matter Halo (DMH) mass}
+
+READ THIS PAPER
+Vale - Ostriker
+arXiv:astro-ph/0402500v2 6 Jul 2004
+Mon. Not. R. Astron. Soc.
+Linking halo mass to galaxy luminosity
+
+``In recent years, N-body numerical simulations have given us
+a good understanding of dark matter structure for standard
+cosmological scenarios, while large scale observational
+surveys have done the same for the distribution of galaxies'' arXiv:0402500v2
+
+``More indirect approaches have also been studied.
+The halo occupation distribution (HOD) model (Seljak
+2000; Benson 2001; Bullock, Wechsler, \& Somerville 2002;
+Zheng et al. 2002; Berlind \& Weinberg 2002; Berlind et al.
+2003; Magliocchetti \& Porciani 2003) is based on the prob-
+ability P(N|M) that a halo of mass M is host to N galax-
+ies. By specifying the P(N|M) function, along with some
+form for the distribution of dark matter and galaxies within
+each halo, it is then possible to relate different statistical
+indicators of the dark matter and galaxy distributions, such
+as correlation functions, to each other. This fully specifies
+the bias between the galaxy and the underlying matter dis-
+tributions. '' arXiv:0402500v2
+
+``Other authors have used a slightly different method.
+Instead of trying to specify the number of galaxies in each
+halo, they treat the halo as a whole and identify it with
+a galaxy group. Then, by comparing the group luminosity
+function with the halo mass function, they obtain the lu-
+minosity associated with each halo (Peacock \& Smith 2000;
+Marinoni \& Hudson 2002), '' arXiv:0402500v2
+
+============>>>>>>>>> Check Peacock \& Smith 2000; Marioni \& Hudson 202
 

### 2014-07-21 paper/star_formation_rate.tex
Intro, Obs. data, SFR

@@
 
-Kennicutt pruposed a method in wich a linear relation between SFR and
-luminosity in specific wavelength ranges can be assumed. This model allows to
-estimate the young stars fraction and the mean SFR over periods of $10^8 - 10^9
-\textrm{yr}$. The luminosity in the model, comes from the UV and the FIR
-broadband, also from speciffic recombination lines.
+There is a  method\citep{madau98} in wich a linear relation between SFR
+and luminosity in specific wavelength ranges can be assumed. This model allows
+to estimate the young stars fraction and the mean SFR over periods of $10^8 -
+10^9 \textrm{yr}$\citep{kennicutt98}. The luminosity in the model, comes from
+the UV and the FIR broadband, also from speciffic recombination lines.
+
+%``The UV continuum emission from a galaxy with significant ongoing star
+%formation is entirely dominated by late-O/early-B stars on the main sequence.
+%As these have masses $>10 M_\odot$ and lifetimes $t_{ms} 2\times 10^7 yr$, the
+%measured luminosity becomes proportional to the stellar birthrate and
+%independent of the galaxy history for $t\gg t_{ms}$ .'' MADAU 1998
+%\citep{madau98}
 
@@
 dust is  heated by the whole stellar popullation, in particular by young, 
-UV-bright stars \citep{law11}.The UV broadband emission is dominated by blue 
-stars with temperature near to 40.000K. These hot and massive stars has a 
-lifetime of $10^8\textrm{Gyr}$, they spend their nuclear fuel faster than smaller 
-and cooler sunlike stars.
+UV-bright stars \citep{law11}.
 
-The relation between UV luminosity and Star Formation Rate \citep{kennicutt98} 
+On active galaxies the UV broadband emission is dominated by late-O
+and early-B type stars, with temperature near to 40.000K. These hot and massive
+stars has a lifetime below $10^7\textrm{Gyr}$, they spend their nuclear fuel
+faster than smaller and cooler sunlike stars.
+
+The relation between UV luminosity and Star Formation Rate
+\citep{madau98,kennicutt98} 
 is given by:
-  $ \textrm{SFR}\left(M_\odot \textrm{yr}^{-1}\right) 
-      = 1.4 \times 10^{28} L_{\nu} \left( \textrm{erg s}^{-1}\textrm{Hz}^{-1} 
-\right)$
+\begin{equation}
+ \textrm{SFR}\left(M_\odot \textrm{yr}^{-1}\right) 
+      = 1.4 \times 10^{-28} L_{\nu} \left( \textrm{erg s}^{-1}\textrm{Hz}^{-1} 
+	\right)
+\end{equation}
+
   With Initial Mass Function (IMF) between $0.1 M_\odot$ 
@@
 The UV dust absorption \citep{kennicutt09} is not taken account in this work.
-
-DUST EXTINTION ALSO STUDIED by 002-TACCHELLA-A Physical Model for ---
+%DUST EXTINTION ALSO STUDIED by 002-TACCHELLA-A Physical Model for ---
 

### 2015-02-17 paper/discussion.tex
Willott observations paragraph added, also SFR vs. DM (w/wo dust)figures

@@
 L∗ )''BOUWENS 2014 UV LF
+
+\begin{figure}
+\epsscale{1.00}
+\plotone{fig/scattering_plots.png}
+\caption{Covariance of parameters for one small box}
+\label{graph_scattering_plots}
+\end{figure}
+
+\begin{figure}
+\epsscale{1.00}
+\plotone{fig/SFR_DMHM_wo.pdf}
+\caption{Star formation rate as function of the dark matter halo mass without dust attenuation. 
+Solid lines represents the mean SFR value over the small boxes within $50\%$  shaded region. }
+\label{graph_SFR_DMHM_wo}
+\end{figure}
+
+\begin{figure}
+\epsscale{1.00}
+\plotone{fig/SFR_DMHM_w.pdf}
+\caption{Star formation rate as function of the dark matter halo mass with dust attenuation. 
+Solid lines represents the mean SFR value over the small boxes within $50\%$  shaded region. }
+\label{graph_SFR_DMHM_w}
+\end{figure}

### 2015-02-17 paper/observations.tex
Willott observations paragraph added, also SFR vs. DM (w/wo dust)figures

@@
 
-This paper is based on three main observation sets. The most recent is from the
-Hubble Space Telescope, this observations where performed by \cite{bouwens14}.
-The second set is from the Canada-France Hawaii Telescope, \cite{willott13} and
+This paper is based on four main observational data sets. The most recent is
+from the Hubble Space Telescope Legacy plus ground telescopes \citep{bouwens14}.
+The second set is from the Canada-France Hawaii Telescope\citep{willott13} and
 the last one by the UK Infrared Telescope and the Subaru Telescope
-\cite{mclure09}. Those observations where made using the Frop-out technique.
+\cite{mclure09}. Those observations where made using the Drop-out technique.
 
-The data from the HST is a compilation of previous works since
+The data from the HSTL is a compilation of previous works since
 2006 \citep{bouwens06}, wich includes also observations after the 2009
-upgrade mission\citep{bouwens12}.
+upgrade mission\citep{bouwens12}. They estimate the uncertainty in their LF due
+to cosmic variance. Taking account they used five independent surveys, they get
+jus $\sigma\sim 10\%$\citep{bouwens14} using the Cosmic Variance Calculator
+developed by Trenti \& Stiavelli (2008).
 
@@
 GAVO-DEXTER\footnote{\url{http://dc.zah.uni-heidelberg.de/dexter/ui/ui/custom}}.
+
+Willott et al.
+\cite{willott13} presented the sixth release of the Canada-France-Hawaii Telescope Legacy Survey CFHTLS.
+The observations where performed over four separated fields covering a total area $\sim 4 \deg^2$ (a large area), it gives this survey great robustness.
+Optical observations used MegaCam with $u^* g' r' i' z'$ filters.
+The main selection criteria: all the objects must be brighter than magnitude $z' = 25.3$.
+The final number of LBGs founded was 40.
+Moreover, they get spectroscopic confirmation for 7 candidates using GMOS spectrograph on the Gemini Telescopes, which has a field of view $\ll 1 \deg^2$.
+They show incompleteness in the sample due to foreground contamination and the detection algorithm; there is no warranty to have every object brighter than the limit magnitude on the faint limit.
+The full galaxy LF at $z=6$ cannot be obtained as in other studies.
+Nevertheless, this survey was focussed on the highly luminous LBGs.
+LF is calculated using the stepwise maximum likelihood method of Efstathiu et al.
+[Cite required!!!], within magnitudes from $M_{1350} = -22.5$ up to $-20.5$.
+The luminosity function of $z=5.9$ shows an exponential decline at the bright end, where feedback processes and inefficient last cooling limites star forming in bright galaxies hosted in the most massive halos.
 

### 2015-02-17 paper/latexdraft.sh

@@ -1,0 +1,6 @@
+pdflatex draft.tex
+pdflatex draft.tex
+rm *.tex~
+rm *.log
+rm *.aux
+#open -a Preview draft.pdf

### 2015-02-18 paper/latexdraft.sh
Script that removes auxiliar files after two compilations

@@ -1,5 +1,6 @@
 pdflatex draft.tex
 pdflatex draft.tex
+rm *.backup
 rm *.tex~
 rm *.log
 rm *.aux

### 2015-02-20 paper/observations.tex
Paragraphs added to Observations: Mclure, Bouwens and Willott. Pending: Finkelstein

@@
 
-This paper is based on four main observational data sets. The most recent is
-from the Hubble Space Telescope Legacy plus ground telescopes \citep{bouwens14}.
-The second set is from the Canada-France Hawaii Telescope\citep{willott13} and
-the last one by the UK Infrared Telescope and the Subaru Telescope
-\cite{mclure09}. Those observations where made using the Drop-out technique.
+This paper is based on four main observational data sets from the Hubble Space Telescope 
+and three ground-based telescopes. All $z\sim 6$ LBG candidates where discovered using using 
+the drop-out technique\citep{steidel03}. All magnitudes are in AB system.
 
-The data from the HSTL is a compilation of previous works since
-2006 \citep{bouwens06}, wich includes also observations after the 2009
-upgrade mission\citep{bouwens12}. They estimate the uncertainty in their LF due
-to cosmic variance. Taking account they used five independent surveys, they get
-jus $\sigma\sim 10\%$\citep{bouwens14} using the Cosmic Variance Calculator
-developed by Trenti \& Stiavelli (2008).
+The data from the Hubble Space Telescope Legacy (HSTL) \citep{bouwens14} is a compilation 
+of observations since the installation of the Advanced Camera for Surveys (ACS) in 2002, 
+through the near-infrared Wide Field Camera 3 (WFC3/IR) installed in 2009, up to 2012. 
+The HST fields of view are: XDF, HUDF09-1, HUDF09-2, CANDELS-S/Deep, 
+CANDELS-S/Wide, ERS, CANDELS-N/Deep, CANDELS-N/Wide, CANDELS-UDS, 
+CANDELS-COSMOS and CANDELS-EGS, with areas of 4.7, 4.7, 4.7, 64.5, 34.2, 
+40.5, 62.9, 60.9, 151.2, 151.9 and 150.7 arcmin$^2$ respectively. The total area corresponds 
+to $\sim 0.7 \deg^2$ over five different lines of sight, reducing cosmic variance effects. 
+Two cameras performed the observations: ACS and WFC3/IR, using 
+$B_{435} V_{606} i_{814} z_{850} I_{814} Y_{098} Y_{105} J{125} JH_{140}$ and $H_{160}$ filters.
+The limit magnitude is between $\sim27.5$mag in CANDELS-EGS and$\sim30 $mag in the 
+deepest field (XDF). Total number of z=6 LBG candidates is 940, most of them in the faint 
+end of the LF, magnitudes in the rest frame are in the range $-22.52\leq M_{1600} \leq -16.77$
+The Schechter parameters derived are: $\phi^* / \textrm{Mpc}^{-3} =(0.33_{-0.10}^{+0.15}) \times 10 ^{-3}$, $M^*_{1600} = -21.16\pm 0.20$ and $\alpha = -1.91 \pm 0.09$.
+\citet{bouwens14} reported that using just few fields of view, UVLF has a slightly non-Schechter-like form.
 
-The dataset was retrieved from graphs for \cite{bouwens14} and \cite{mclure09} 
-using
+\citet{willott13} presented the sixth release of the Canada-France-Hawaii 
+Telescope Legacy Survey CFHTLS. The observations where performed over four 
+separated fields covering a total area $\sim 4 \deg^2$ (a large area), it gives this 
+survey great robustness. Optical observations used MegaCam 
+[CITE REQUIRED] with $u^* g' r' i' z'$ filters. The main selection criteria: all the 
+objects must be brighter than magnitude $z' = 25.3$. The final 
+number of LBGs founded was 40. Moreover, they get spectroscopic confirmation 
+for 7 candidates using GMOS spectrograph on the Gemini Telescopes, which 
+has a $\ll 5.5$-square arcmin field of view . They show incompleteness in the sample due to 
+foreground contamination and the detection algorithm; there is no warranty to 
+have every object brighter than the limit magnitude on the faint limit. The full 
+galaxy LF at $z=6$ cannot be obtained as in other studies. Nevertheless, this survey 
+was focussed on the highly luminous LBGs. LF is calculated using the stepwise 
+maximum likelihood method of Efstathiu et al. [MNRAS 1998 Cite required!!!], within 
+magnitudes 
+from $M_{1350} = -22.5$ up to $-20.5$. The luminosity function of $z=5.9$ shows 
+an exponential decline at the bright end, where feedback processes and inefficient 
+last cooling limites star forming in bright galaxies hosted in the most massive halos.
+
+\citet{mclure09} build the luminosity function for $z=5$ and $z=6$ using data from two ground-based
+ telescopes: the United Kingdom Infrared Telescope in the near-IR imaging and Subaru 
+ Telescope for the optical imaging. They use the first data release of the UKIRT Infrared 
+ DeepSky Survey Ultra Deep Survey (UDS), together with the Subaru XMM-Newton 
+ Survey (SXDS). Total observed area is $0.63 \deg^2$ uniformly covered by booth catalogues.
+The UKIRT was equipped with the WFCAM using $J K$ filters. The Subaru was equipped 
+with the Suprime-Cam with the $B V R i' z'$ filters. All candidates where brighter than 
+$z'=26$. The UV rest frame magnitude range is $-22.4\leq M_{1500} \leq-20.6$. The LF 
+was calculated using the maximum likelihood estimator of Schmidt (1968). [Cite Required!!!!]. 
+Their analysis gave a total number of 104 LBG candidates in the redshift range 
+$5.7\leq z \leq 6.3$. LF was parameterized according to the Schechter function with 
+$\phi^* / \textrm{Mpc}^{-3} =(1.8 \pm 0.5) \times 10 ^{-3}$, $M^*_{1500} = -20.04\pm 0.12$ 
+and $\alpha = -1.71 \pm 0.11$.
+
+The dataset was retrieved from \cite{mclure09} graph using
 GAVO-DEXTER\footnote{\url{http://dc.zah.uni-heidelberg.de/dexter/ui/ui/custom}}.
 
-Willott et al.
-\cite{willott13} presented the sixth release of the Canada-France-Hawaii Telescope Legacy Survey CFHTLS.
-The observations where performed over four separated fields covering a total area $\sim 4 \deg^2$ (a large area), it gives this survey great robustness.
-Optical observations used MegaCam with $u^* g' r' i' z'$ filters.
-The main selection criteria: all the objects must be brighter than magnitude $z' = 25.3$.
-The final number of LBGs founded was 40.
-Moreover, they get spectroscopic confirmation for 7 candidates using GMOS spectrograph on the Gemini Telescopes, which has a field of view $\ll 1 \deg^2$.
-They show incompleteness in the sample due to foreground contamination and the detection algorithm; there is no warranty to have every object brighter than the limit magnitude on the faint limit.
-The full galaxy LF at $z=6$ cannot be obtained as in other studies.
-Nevertheless, this survey was focussed on the highly luminous LBGs.
-LF is calculated using the stepwise maximum likelihood method of Efstathiu et al.
-[Cite required!!!], within magnitudes from $M_{1350} = -22.5$ up to $-20.5$.
-The luminosity function of $z=5.9$ shows an exponential decline at the bright end, where feedback processes and inefficient last cooling limites star forming in bright galaxies hosted in the most massive halos.
+Finkelstein
+HST using CANDELS/GOODS fields, HUDF and Hubble Frontier Field deep parallel observations near the Abell 2744 and MACS J0416.1-2403 clusters. (Unlensend fields)
 
@@
 
-\subsection{The Drop-out Technique - Lyman Break Technique}
-
-\cite{steidel03}
+%They estimate the uncertainty in their LF due
+%to cosmic variance. Taking account they used five independent surveys, they get
+%#jus $\sigma\sim 10\%$\citep{bouwens14} using the Cosmic Variance Calculator
+%developed by Trenti \& Stiavelli (2008).

### 2015-02-20 paper/the_bibliography.tex
SFR, Fitting Model, The_Bibliography
adding references
Intro, Obs. data, SFR
Paragraphs added to Observations: Mclure, Bouwens and Willott. Pending: Finkelstein

@@
 \begin{thebibliography}{}
+
 \bibitem[Bouwens(2006)]{bouwens06} Bouwens, R. J. et al. 2006, \apj, 653, 53	
@@
 		%2012ApJ...752L...5B
-\bibitem[Bouwens(2014)]{bouwens14} Bouwens, R. J. et al. 2012, arXiv:1403.4295
+\bibitem[Bouwens et al.(2014)]{bouwens14} Bouwens, R. J., G. D. Illingworth, P. A. Oesch, M. Trenti, I. Labbe', L. Bradley, M. Carollo, et al.2014, arXiv:1403.4295
+
 \bibitem[Kennicutt(1998)]{kennicutt98} Kennicutt, Robert C., Jr. 1998, \araa, 
@@
 		%2011ApJ...738..124L
-\bibitem[McLure(2009)]{mclure09} McLure, R. J. et al. 2009, \mnras, 395, 2196	
+\bibitem[Jiang(2011)]{jiang11} Jiang, Linhua et al. 2011, \apj, 743, 65
+		%2011ApJ...743...65J
+\bibitem[Lee(2009)]{lee09} Lee, Kyoung-Soo et al. 2009, \apj, 695, 368
+		%2009ApJ...695..368L
+\bibitem[Lundgren(2014]{lundgren14} Lundgren, Britt F. et al, 2014, \apj, 780,
+34		%2014ApJ...780...34L
+\bibitem[Madau(1998)]{madau98} Madau, Piero. et al, 1998, \apj, 498, 106M
+		%1998ApJ...498..106M
+\bibitem[McLure et al.(2009)]{mclure09} McLure, R. J., M. Cirasuolo, J. S. Dunlop, S. Foucaud, \and O. Almaini. 2009, \mnras, 395, 2196	
 		%2009MNRAS.395.2196M
@@
 \bibitem[Trimble(1987)]{trimble87} Trible, Virginia. 1987, \araa, 25, 425
-\bibitem[Willott(2013)]{willott13} Willott, Chris J. et al. 2013, \aj, 145, 4	
+
+\bibitem[van den Bosch(203)]{vandenbosch03} van den Bosh, Frank C. et al. 2003, \mnras,
+40, 771		%2003MNRAS.340..771V
+\bibitem[Willott et al.(2013)]{willott13} Willott, Chris J., Ross J.
+McLure, Pascale Hibon, Richard Bielby, Henry J.
+McCracken, Jean-Paul Kneib, Olivier Ilbert, David G.
+Bonfield, Victoria A.
+Bruce, \and Matt J.
+Jarvis.
+2013, \aj, 145, 4
 		%2013AJ....145....4W
-
 \end{thebibliography}

### 2015-02-23 paper/draft.tex
LF model
Intro, Obs. data, SFR
Willott observations paragraph added, also SFR vs. DM (w/wo dust)figures
Refs. in observations. Removing intro. Methodology main ideas.

@@
 \usepackage{epstopdf}
+\usepackage{color}
 
@@
 This work relates baryonic matter and dark matter at redshift $z=5.9$ using 
-observational data from CFHTLS \citep{willott13}, HUDF09 
-\citep{bouwens06,bouwens12}, UKIDSS and SDXS \citep{mclure09}, and results of 
+observational data from CFHTLS \citep{willott13}, HST Legacy Survey
+\citep{bouwens14,finkelstein14}, UKIDSS and SDXS \citep{mclure09}, and results of 
 the Multidark Simulation \citep{riebe13} in a cubic box of $1000 \textrm{Mpc 
@@
 
-\include{introduction}
+%\include{introduction}
+
+\include{fitting_model}
 
@@
 
-\include{fitting_model}
+\include{observations}
 
-\include{observations}
+\include{methodology}
 
@@
 
-\section{Appendix material}
-DEXTER \url{http://dc.zah.uni-heidelberg.de/dexter/ui/ui/custom}
+%\section{Appendix material}
+%DEXTER \url{http://dc.zah.uni-heidelberg.de/dexter/ui/ui/custom}
 

### 2015-02-23 paper/methodology.tex
Refs. in observations. Removing intro. Methodology main ideas.

\section{Methodology}

The first goal in this paper is reproduce the observed UVLF from DMH, from
 simulations at redshift $z=6$. The observational datasets where aforementioned.

Bolshoi Simulation \citep{riebe13} was performed by the MuldiDark consortium
MultiDark Database is

UV Luminosity as function of DMH mass. 
Parameters.
Dust Extinction

MCMC, maximum likelihood.

UV luminosity to SFR

### 2015-02-23 paper/observations.tex
Refs. in observations. Removing intro. Methodology main ideas.

@@
 Two cameras performed the observations: ACS and WFC3/IR, using 
-$B_{435} V_{606} i_{814} z_{850} I_{814} Y_{098} Y_{105} J{125} JH_{140}$ and $H_{160}$ filters.
+$B_{435}$, $V_{606}$, $ i_{814}$, $ z_{850}$, $ I_{814}$, $Y_{098}$, $Y_{105}$, $J{125}$, 
+$JH_{140}$ and $H_{160}$ filters.
 The limit magnitude is between $\sim27.5$mag in CANDELS-EGS and$\sim30 $mag in the 
@@
 end of the LF, magnitudes in the rest frame are in the range $-22.52\leq M_{1600} \leq -16.77$
-The Schechter parameters derived are: $\phi^* / \textrm{Mpc}^{-3} =(0.33_{-0.10}^{+0.15}) \times 10 ^{-3}$, $M^*_{1600} = -21.16\pm 0.20$ and $\alpha = -1.91 \pm 0.09$.
+\citet{bowens14} calculated LF using a stepwise maximum-likelihood (SWML) based on \citet{efstathiou88}. 
+The Schechter parameters derived are: 
+$\phi^* / \textrm{Mpc}^{-3} =(0.33_{-0.10}^{+0.15}) \times 10 ^{-3}$, 
+$M^*_{1600} = -21.16\pm 0.20$ and $\alpha = -1.91 \pm 0.09$. 
 \citet{bouwens14} reported that using just few fields of view, UVLF has a slightly non-Schechter-like form.
+
+\citet{finkelstein14} worked also with HST, using the HUDF, CANDELS and GOODS fields, along with two of the Hubble Frontier Fields (HFF): deep parallel observations (unlensed fields) near the Abell 2744 and MACS J0416.1-2403 clusters.
+The HFF uses the ACS and the WFC3/IR with the same filters aforementioned but $z_{850}$.
 
@@
 separated fields covering a total area $\sim 4 \deg^2$ (a large area), it gives this 
-survey great robustness. Optical observations used MegaCam 
-[CITE REQUIRED] with $u^* g' r' i' z'$ filters. The main selection criteria: all the 
+survey great robustness. Optical observations used MegaCam  %%%%%%[CITE REQUIRED] 
+with $u^* g' r' i' z'$ filters. The main selection criteria: all the 
 objects must be brighter than magnitude $z' = 25.3$. The final 
@@
 was focussed on the highly luminous LBGs. LF is calculated using the stepwise 
-maximum likelihood method of Efstathiu et al. [MNRAS 1998 Cite required!!!], within 
+maximum likelihood method of \citet{efstathiou88}, within 
 magnitudes 
@@
 $z'=26$. The UV rest frame magnitude range is $-22.4\leq M_{1500} \leq-20.6$. The LF 
-was calculated using the maximum likelihood estimator of Schmidt (1968). [Cite Required!!!!]. 
+was calculated using the maximum likelihood estimator of \citet{schmidt68}. 
 Their analysis gave a total number of 104 LBG candidates in the redshift range 
@@
 GAVO-DEXTER\footnote{\url{http://dc.zah.uni-heidelberg.de/dexter/ui/ui/custom}}.
-
-Finkelstein
-HST using CANDELS/GOODS fields, HUDF and Hubble Frontier Field deep parallel observations near the Abell 2744 and MACS J0416.1-2403 clusters. (Unlensend fields)
 

### 2015-02-24 paper/discussion.tex
2 paragraphs in methodology

@@
 
-``Fig. 16.— Updated Determinations of the derived SFR (left axis) and U V
-luminosity (right axis) densities versus redshift (5.4). The
-left axis gives the SFR densities we would infer from the measured luminosity
-densities, assuming the Madau et al. (1998) conversion
-factor relevant for star-forming galaxies with ages of 108 yr (see also
-Kennicutt 1998). The right axis gives the U V luminosities we infer
-integrating the present and published LFs to a faint-end limit of −17 mag (0.03
-L∗ )''BOUWENS 2014 UV LF
+%``Fig. 16.— Updated Determinations of the derived SFR (left axis) and U V
+%luminosity (right axis) densities versus redshift (5.4). The
+%left axis gives the SFR densities we would infer from the measured luminosity
+%densities, assuming the Madau et al. (1998) conversion
+%factor relevant for star-forming galaxies with ages of 108 yr (see also
+%Kennicutt 1998). The right axis gives the U V luminosities we infer
+%integrating the present and published LFs to a faint-end limit of −17 mag (0.03
+%L∗ )''BOUWENS 2014 UV LF
 

### 2015-02-24 paper/draft.tex
2 paragraphs in methodology

@@
 
-\author{F.L. G\'omez-Cort\'es\altaffilmark{1} }
-\affil{Departamento de Física, Universidad de los Andes, Colombia}
+\author{Felipe L. G\'omez-Cort\'es\altaffilmark{1} }
+\affil{Departamento de F\'isica, Universidad de los Andes, Colombia}
 
@@
 \citep{bouwens14,finkelstein14}, UKIDSS and SDXS \citep{mclure09}, and results of 
-the Multidark Simulation \citep{riebe13} in a cubic box of $1000 \textrm{Mpc 
-h}^{-1}$ length with 2013 Planck Cosmology. The Luminosity Function (LF) is 
+the Multidark Simulation \citep{klypin14} in a cubic box of $1000 \textrm{Mpc 
+h}^{-1}$ length with 2013 Planck Cosmology \citep{planck1}. The Luminosity Function (LF) is 
 fitted via four parameters with the Markov Chain Monte Carlo method. The 
@@
 
-\include{fitting_model}
-
-\include{star_formation_rate}
-
 \include{observations}
-
 \include{methodology}
@@
 
-\section{Summary}
-
+%\section{Summary}
 \acknowledgments
 %Gracias Totales
-%
 \appendix
-
 %\section{Appendix material}
-%DEXTER \url{http://dc.zah.uni-heidelberg.de/dexter/ui/ui/custom}
-
 \include{the_bibliography}
-
 \end{document}
-
-%%
-%% End of file `sample.tex'.

### 2015-02-24 paper/methodology.tex
2 paragraphs in methodology

@@
 
-The first goal in this paper is reproduce the observed UVLF from DMH, from
- simulations at redshift $z=6$. The observational datasets where aforementioned.
+The key element to connect SFR with halo mass from simulations is the observed UVLF. 
+If there exist a function whom gives to each halo a UV luminosity then is posible to 
+reproduce UVLF from DMH catalogs. The fitting parameters can be explored using a 
+Markov Chain Monte-Carlo (MCMC) implementation. Once the parameters are found, 
+the SFR-Halo Mass relation have been found.
 
-Bolshoi Simulation \citep{riebe13} was performed by the MuldiDark consortium
-MultiDark Database is
+We use the dark matter halo catalog from the Big MultiDark Plank 1 (MDPL) Simulation 
+\citep{klypin14} with 2013 Planck cosmology \citep{planck1}. MDPL is quite similar to the 
+Big Bolshoi ($1 \textrm{Gpc h}^{-1}$) \citep{prada12} and 
+its predecesor Bolshoi \citep{klypin11} ($250 \textrm{Mpc h}^{-1}$), booth of them with 
+WMAP5 cosmology, but MDPL has bigger mass resolution.  Those halo catalogs are 
+available at the MultiDark Database\footnote{\url{http://www.multidark.org}} 
+\citep{riebe13}.
 
-UV Luminosity as function of DMH mass. 
-Parameters.
-Dust Extinction
+The MDPL run is a N-body dark matter only simulation based on the L-Gadget2 
+code. The simulated volume is a cubic box of $1 \textrm{Gpc h}^{-1}$ side length. 
+It has $3840^3$ dark matter particles of 
+$1.51\times 9 \textrm{M}_{\odot} \textrm{h}^{-1}$ mass each one.
+The 2013 Planck cosmology is defined by the following parameters: $\Sigma_M = 0.307$, 
+$\Sigma_B = 0.048$, $\Sigma_\Lambda = 0.730$, $\sigma_8 = 0.829$, $n_s = 0.96$ and 
+$H_0 = 67.8$. The DMH Catalog at $z=6$ contains $\sim 10.9 \times 10^7$ 
+halos, to avoid incompleteness in the low mass end, halos with mass below 
+$10^{10.3} \textrm{M}_{\odot} \textrm{h}^{-1}$ are rejected. In order to study how 
+cosmic variance can affect measurements, the original catalog is divided into 64 small 
+cubic boxes, with a similar volume to the observations.
+
+The following treatment is applied to every one small box.
+
+The halo abundance matching technique has been widely used \citep{colin99, kravtsov04}
+resulting in good reproduction of the observed galaxy clustering. \citep{conroy06, lee09}. 
+Here we use the simplest case with few premises: 
+\begin{enumerate}
+ \item Each halo in the catalog hosts one galaxy. There are not empty
+halos, also none of halos has two or more galaxies.
+ \item The UV luminosity of each galaxy is function of one variable; the mass of
+the DMH in which is located. This function must be monotone, this guarantees that most massive halos will host the most luminous galaxies in the same volume.
+\end{enumerate}
+
+The simplest relation we can have is a power law, two parametric function:
+ \begin{equation}
+    L_{\textrm{UV}} (M) = L_0 M^k
+ \end{equation}
+but it does not reproduce the two slopes in the UVLF.
+
+A better model is a four parameter function. Each galaxy has a luminosity given
+by:
+  \begin{equation}
+  L_{\textrm{UV}} (M) = L_{0} M \left[ \left( \frac{M}{M_0}\right)^{-\beta} 
+		   + \left( \frac{M}{M_0}\right)^{\gamma} 
+               \right]^{-1}
+  \end{equation}
+where $M$ is the hosting DMH mass, $L_{0}$ is a normalization constant, $M_0$
+is the critical mass where the luminosity function has a slope change, 
+$\beta$ and $\gamma$ are the slopes. This equation has a similar fashion to the
+mass to light relation \citep{vandenbosch03} and the mean relation between
+stellar mas of a galaxy and the mass of its halo used by \citet{moster10}.
+
+Dust Extinction.
 
@@
 
-UV luminosity to SFR
+Python, Ipython Notebook, Scipy, Matplotlib, Numpy.
+
+The galaxy UV luminosity can be directly related with SFR according to \citet{madau98}
+This model is accurate within the range of $10^8 - 10^9 \textrm{yr}$\citep{kennicutt98}.
+The relation between UV luminosity and Star Formation Rate \citep{madau98,kennicutt98} 
+is given by:
+\begin{equation}
+ \textrm{SFR}\left(M_\odot \textrm{yr}^{-1}\right) 
+      = 1.4 \times 10^{-28} L_{\nu} \left( \textrm{erg s}^{-1}\textrm{Hz}^{-1} 
+	\right)
+\end{equation}

### 2015-02-24 paper/the_bibliography.tex
Refs. in observations. Removing intro. Methodology main ideas.
2 paragraphs in methodology

@@
 
-\bibitem[Bouwens(2006)]{bouwens06} Bouwens, R. J. et al. 2006, \apj, 653, 53	
+\bibitem[Behroozi et al.(2013)]{behroozi13} Behroozi, Peter S., Risa H. Wechsler, 
+\and Charlie Conroy. 2013, \apj,  770, 57
+% Semi-Analytical Model for SFR-DMHM
+
+\bibitem[Bouwens et al.(2006)]{bouwens06} Bouwens, R. J. et al. 2006, \apj, 653, 53	
 		%2006ApJ...653...53B
-\bibitem[Bouwens(2012)]{bouwens12} Bouwens, R. J. et al. 2012, \apj, 752, 5 	
+% Observational luminosity function
+
+\bibitem[Bouwens et al.(2012)]{bouwens12} Bouwens, R. J. et al. 2012, \apj, 752, 5 	
 		%2012ApJ...752L...5B
-\bibitem[Bouwens et al.(2014)]{bouwens14} Bouwens, R. J., G. D. Illingworth, P. A. Oesch, M. Trenti, I. Labbe', L. Bradley, M. Carollo, et al.2014, arXiv:1403.4295
+% Observational luminosity function
+
+\bibitem[Bouwens et al.(2014)]{bouwens14} Bouwens, R. J., G. D. Illingworth, P. A. 
+Oesch, M. Trenti, I. Labbe', L. Bradley, M. Carollo, et al. 2014, arXiv:1403.4295
+% Observational luminosity function
+
+\bibitem[Col\'in et al.(1999)]{colin99}
+Col\'n, Pedro, Anatoly A. Klypin, Andrey V. Kravtsov, and Alexei M. Khokhlov. 
+1999, \apj , 523,32
+% Halo Abundance Matching
+\bibitem[Conroy et al.(2006)]{conroy06}
+Conroy, Charlie, Risa H. Wechsler, \and Andrey V. Kravtsov. 2006, \apj,647,201
+% Halo Abundance Matching
+
+\bibitem[Efstathiou et al.(1988)]{efstathiou88} Efstathiou, G., Richard S. Ellis, 
+\and Bruce A. Peterson. 1988, \mnras, 232,431.
+% StepWise Maximun Likelihood LF
+
+\bibitem[Finkelstein et al.(2014)]{finkelstein14} Finkelstein, Steven L., Russell E. 
+Ryan Jr., Casey Papovich, Mark Dickinson, Mimi Song, Rachel Somerville, 
+Henry C. Ferguson, et al. 2014, arXiv:1410.5439
+% Observational luminosity function
 
@@
 36, 189		%1998ARA&A..36..189K
-\bibitem[Kennicutt(2009)]{kennicutt09} Kennicutt, Robert C., Jr et al. 2009, \apj, 
+\bibitem[Kennicutt et al.(2009)]{kennicutt09} Kennicutt, Robert C., Jr et al. 2009, \apj, 
 703, 4672	%2009ApJ...703.1672K
-\bibitem[Law(2011)]{law11} Law, K. et al. 2011, \apj, 738, 124
+
+\bibitem[Kravtsov et al.(2004)]{kravtsov04}
+Kravtsov, Andrey V., Andreas A. Berlind, Risa H. Wechsler, Anatoly A. Klypin, 
+Stefan Gottlöber, Brandon Allgood, \and Joel R. Primack. 2004, \apj, 609, 35
+%Halo Abundance Matching
+
+\bibitem[Klypin et al.(2011)]{klypin11} Klypin, Anatoly A., Sebastian Trujillo-Gomez, \
+and Joel Primack. 2009, \apj, 740, 102
+% Bolshoi 2011
+
+\bibitem[Klypin et al.(2014)]{klypin14} Anatoly Klypin, Gustavo Yepes, Stefan Gottlober, 
+Francisco Prada \and Steffen Hess. 2014, arXiv:`1411.4001
+% Big Bolshoi Planck 1 - MDPL
+
+\bibitem[Law et al.(2011)]{law11} Law, K. et al. 2011, \apj, 738, 124
 		%2011ApJ...738..124L
-\bibitem[Jiang(2011)]{jiang11} Jiang, Linhua et al. 2011, \apj, 743, 65
+\bibitem[Jiang et al.(2011)]{jiang11} Jiang, Linhua et al. 2011, \apj, 743, 65
 		%2011ApJ...743...65J
-\bibitem[Lee(2009)]{lee09} Lee, Kyoung-Soo et al. 2009, \apj, 695, 368
+\bibitem[Lee et al.(2009)]{lee09} Lee, Kyoung-Soo et al. 2009, \apj, 695, 368
 		%2009ApJ...695..368L
-\bibitem[Lundgren(2014]{lundgren14} Lundgren, Britt F. et al, 2014, \apj, 780,
+\bibitem[Lundgren et al.(2014]{lundgren14} Lundgren, Britt F. et al, 2014, \apj, 780,
 34		%2014ApJ...780...34L
-\bibitem[Madau(1998)]{madau98} Madau, Piero. et al, 1998, \apj, 498, 106M
+\bibitem[Madau et al.(1998)]{madau98} Madau, Piero. et al, 1998, \apj, 498, 106M
 		%1998ApJ...498..106M
@@
 		%2009MNRAS.395.2196M
-\bibitem[Moster(2010)]{moster10} Moster, Benjamin P. et al. 2010, \apj, 710, 
+\bibitem[Moster et al.(2010)]{moster10} Moster, Benjamin P. et al. 2010, \apj, 710, 
 903
-\bibitem[Riebe(2013)]{riebe13} Riebe, K. et al. 2013, AN, 334, 691 		
-		%2013AN....334..691R
-\bibitem[Steidel(2003)]{steidel03} Steidel, Charles C. et al. 2003, \apj, 592, 
+
+\bibitem[Planck Collaboration et al(2014)]{planck1}
+Planck Collaboration, P. A. R. Ade, N. Aghanim, C. Armitage-Caplan, M. Arnaud, 
+M. Ashdown, F. Atrio-Barandela, et al. \aap, 571, A16
+%Planck 2013 cosmology release.
+
+\bibitem[Prada et al.(2012)]{prada12} Prada, Francisco, Anatoly A. Klypin, 
+Antonio J. Cuesta, Juan E. Betancort-Rijo, and Joel Primack. 2012. \mnras, 423, 3018
+% Big Bolshoi
+
+\bibitem[Riebe et al.(2013)]{riebe13} Riebe, K. et al. 2013, AN, 334, 691 		
+% Multiyear Database Release		%2013AN....334..691R
+
+\bibitem[Schmidt(1968)]{schmidt68} Schmidt, Maarten. 1968, \apj 151, 393.
+% StepWise Maximun Likelihood LF
+
+\bibitem[Steidel et al.(2003)]{steidel03} Steidel, Charles C. et al. 2003, \apj, 592, 
 728 		%2003ApJ...592..728S
@@
 
-\bibitem[van den Bosch(203)]{vandenbosch03} van den Bosh, Frank C. et al. 2003, \mnras,
+\bibitem[van den Bosch et al.(203)]{vandenbosch03} van den Bosh, Frank C. et al. 2003, \mnras,
 40, 771		%2003MNRAS.340..771V
-\bibitem[Willott et al.(2013)]{willott13} Willott, Chris J., Ross J.
-McLure, Pascale Hibon, Richard Bielby, Henry J.
-McCracken, Jean-Paul Kneib, Olivier Ilbert, David G.
-Bonfield, Victoria A.
-Bruce, \and Matt J.
-Jarvis.
-2013, \aj, 145, 4
+
+\bibitem[Willott et al.(2013)]{willott13} Willott, Chris J., Ross J. McLure, Pascale Hibon,
+ Richard Bielby, Henry J. McCracken, Jean-Paul Kneib, Olivier Ilbert, David G. Bonfield,
+  Victoria A. Bruce, \and Matt J. Jarvis. 2013, \aj, 145, 4	
 		%2013AJ....145....4W

### 2015-03-03 paper/methodology.tex
MCMC sketch

@@
 $1.51\times 9 \textrm{M}_{\odot} \textrm{h}^{-1}$ mass each one.
-The 2013 Planck cosmology is defined by the following parameters: $\Sigma_M = 0.307$, 
-$\Sigma_B = 0.048$, $\Sigma_\Lambda = 0.730$, $\sigma_8 = 0.829$, $n_s = 0.96$ and 
+The 2013 Planck cosmology is defined by the following parameters: $\Omega_M = 0.307$, 
+$\Omega_B = 0.048$, $\Omega_\Lambda = 0.730$, $\sigma_8 = 0.829$, $n_s = 0.96$ and 
 $H_0 = 67.8$. The DMH Catalog at $z=6$ contains $\sim 10.9 \times 10^7$ 
@@
  \item The UV luminosity of each galaxy is function of one variable; the mass of
-the DMH in which is located. This function must be monotone, this guarantees that most massive halos will host the most luminous galaxies in the same volume.
+the DMH in which is located. This function must be monotone, this guarantees that most 
+massive halos will host the most luminous galaxies in the same volume.
 \end{enumerate}
 
-The simplest relation we can have is a power law, two parametric function:
- \begin{equation}
-    L_{\textrm{UV}} (M) = L_0 M^k
- \end{equation}
-but it does not reproduce the two slopes in the UVLF.
+\subsection{Fitting Model}
 
-A better model is a four parameter function. Each galaxy has a luminosity given
-by:
-  \begin{equation}
-  L_{\textrm{UV}} (M) = L_{0} M \left[ \left( \frac{M}{M_0}\right)^{-\beta} 
+The observed UV Luminosity Function has two slopes. To reproduce it we decide to use the four parameter model:
+  \begin{equation}\label{eqn:luminosity}
+  L_{\textrm{\small{UV}}} (M) = L_{0} M \left[ \left( \frac{M}{M_0}\right)^{-\beta} 
 		   + \left( \frac{M}{M_0}\right)^{\gamma} 
@@
 
-Dust Extinction.
+%Dust Extinction
+\subsection{MCMC}
+We used a Markov Chain Monte Carlo method to find the best parameters and its 
+uncertainties over each one of the boxes and each observational dataset.
 
-MCMC, maximum likelihood.
+Observational data set to fit is selected.
+A halo catalog of a cubic box of length 250 Mpc h-1 is selected.
+Initial parameters are introduced.
 
-Python, Ipython Notebook, Scipy, Matplotlib, Numpy.
+An UV luminosity is given to each halo as function of his mass according to equation
+ \ref{eqn:luminosity}.
+Luminosity is converted to magnitude using:
+  \[ M_{U} = 51.82 - 2.5 \log_{10}(L_{U}). \]
 
-The galaxy UV luminosity can be directly related with SFR according to \citet{madau98}
+The luminosity function is constructed as an histogram of the magnitudes normalized by 
+the volume of the catalog. Each observed luminosity function has a different bin range.
+
+Once having the LF, we compare our LF against observed LF. Our likelihood estimator is 
+the sum of the square difference over each bin, divided by the number of degrees of 
+freedom. We worked on the logarithmic space of luminosities to have a good fitting on
+six decades.
+
+\[ \chi^2  = \sum_{i=o}^{n}\left( x_{i,obs} - x_{i,fit} \right)^2 \]
+
+\[ \mathcal{L} \propto \exp \left( \frac{\chi ^2}{n} \right) \]
+
+Then we have a small variation on the parameters, it gives us a new LF and a new 
+likelihood estimator $\chi^2$.
+
+We compare the new fitting versus the old fitting.
+
+Some restrictions where imposed over two parameters to guarantee convergence in the 
+MCMC method: $0 \leq \alpha \leq 1.8 $  and $\gamma \geq 0$.
+
+%MCMC, maximum likelihood.
+
+%Python, Ipython Notebook, Scipy, Matplotlib, Numpy. Astropy
+Finally, the UV luminosity for each galaxy can be directly related with SFR according 
+to \citet{madau98}.
 This model is accurate within the range of $10^8 - 10^9 \textrm{yr}$\citep{kennicutt98}.

### 2015-03-03 paper/observations.tex
MCMC sketch

@@
 The Schechter parameters derived are: 
-$\phi^* / \textrm{Mpc}^{-3} =(0.33_{-0.10}^{+0.15}) \times 10 ^{-3}$, 
+$\phi^* =(0.33_{-0.10}^{+0.15}) \times 10 ^{-3} / \textrm{Mpc}^{-3} $, 
 $M^*_{1600} = -21.16\pm 0.20$ and $\alpha = -1.91 \pm 0.09$. 

### 2015-03-10 paper/methodology.tex
Methodology: Dust attenuation

@@
 
-%Dust Extinction
+\subsection{Dust Attenuation}
+
+Dust in galaxies absorbs part of the UV radiation and reemits on IR. The more massive is the galaxy
+then more dust contains and dust attenuation will be bigger.
+
+The UV Spectral Slope $\beta$ was introduced by \citet{meurer99} as a color index to 
+study dust attenuation in high redshift galaxies calibrating with local galaxies. 
+This index is becomes from a power law
+fitting, with the flux $f$ as function of the wavelength $\lambda$,
+\[ f \propto \lambda^\beta\],
+The relation they found is:
+\begin{equation}
+A = 4.43 + 1.99 \beta
+\end{equation}.
+
+\citet{bouwens12b} found a linear relation between $\beta$ and the UV magnitude.
+\begin{equation}
+\langle \beta \rangle = \frac{d \beta}{d M_{UV}} \left( M_{UV,AB}+19.5 \right) + \beta_{M_{UV}=-19.5}
+\end{equation}
+
+We use a similar dust attenuation model as the used by \cite{smit12} with 
+$ \beta_{M_{UV}=-19.5} = -2.20$ and $d \beta/d M_{UV} = -0.21$ at $z=5.9$ 
+according \citep(bouwens12b), imposing also the condition:
+\[ A \geq 0 \]
+
 \subsection{MCMC}

### 2015-03-11 paper/methodology.tex
Methodology Dust Attenuation

--- 2015-03-03 paper/methodology.tex
@@
 
-The observed UV Luminosity Function has two slopes. To reproduce it we decide to use the four parameter model:
+The observed UV Luminosity Function has two slopes. To reproduce it we decide to use the
+ four parameter model:
   \begin{equation}\label{eqn:luminosity}
@@
 
-%Dust Extinction
+\subsection{Dust Attenuation}
+
+Dust in star forming galaxies absorbs part of the UV radiation and reemits on IR. The more 
+massive is the galaxy then more dust contains and dust attenuation will be greater. The 
+relation between dust attenuation and magnitude have been already studied, with this relation 
+we can infer the dust-free UV luminosity of a galaxy from observations, resulting in  a more 
+accurate inferred SFR.
+
+The UV Spectral Slope $\beta$ was introduced by \citet{meurer99} as a UV color to 
+study dust attenuation in local starburst galaxies and extrapolating to high redshift galaxies. 
+This index appears when a power law fitting is performed over the spectral flux $f$ 
+as function of the wavelength $\lambda$;
+\[ f \propto \lambda^\beta.\]
+The relation for ultra-violet attenuation at $1600 \textrm{\AA}$ they found is:
+\begin{equation}
+A_{1600} = 4.43 + 1.99 \beta,
+\end{equation}
+with $A_{1600}$ in magnitude units.
+
+Due LBGs have more similar spectra properties to local starburst galaxies rather than AGNs 
+for example, we can assume that local calibration of $\beta-A_{1600}$ can be applied also 
+for LBGs,
+%%% From Meurer99
+``The main requirement is that the data include fluxes in two broad bands or coarse spectra 
+covering the rest-frame UV.''
+
+\citet{bouwens12b} uses the fluxes on different bands to estimate $\beta$ on each LBG 
+candidate found with $z \sim 4-7$. After in redshift groups they found a linear relation 
+between $\beta$ and the UV magnitude:
+\begin{equation}
+\langle \beta \rangle = \frac{d \beta}{d M_{UV}} \left( M_{UV,AB}+19.5 \right) 
+                                   + \beta_{M_{UV}=-19.5}
+\end{equation}
+with $ \beta_{M_{UV}=-19.5} = -2.20$ and $d \beta/d M_{UV} = -0.21$ at $z=5.9$.
+
+\citet{smit12} used the aforementioned relations to infer the corrected luminosity functions,
+i.e. dust-free luminosity functions, and the corrected SFR at $z=4$.
+
+Here we use the inverse relation, starting from the intrinsic or dust-free galaxy magnitude, 
+obtaining the observed magnitude:
+\begin{equation}\label{eqn. dust attenuation}
+  M_{obs} = \begin{cases} 
+                         \frac{M_{int}-4.616}{1.259}, &\mbox{if } A>0 \\
+                         M_{int}, &\mbox{else}
+                   \end{cases}.
+\end{equation}
+
 \subsection{MCMC}
@@
 Luminosity is converted to magnitude using:
-  \[ M_{U} = 51.82 - 2.5 \log_{10}(L_{U}). \]
+  \[ M_{UV} = 51.82 - 2.5 \log_{10}(L_{UV}). \]
+If we consider the dust attenuation im the equation \ref{eqn. dust attenuation} we have
+a dust-corrected UV Luminosity Function.
 

### 2015-03-17 paper/observations.tex
Methodology: Dust attenuation
Methodology Dust Attenuation
Revision of volumes

--- 2015-02-23 paper/observations.tex
@@
 the drop-out technique\citep{steidel03}. All magnitudes are in AB system.
+%%%%%%%%%%%%%%Steidel 1996, Bunker 2003
 
@@
 CANDELS-COSMOS and CANDELS-EGS, with areas of 4.7, 4.7, 4.7, 64.5, 34.2, 
-40.5, 62.9, 60.9, 151.2, 151.9 and 150.7 arcmin$^2$ respectively. The total area corresponds 
-to $\sim 0.7 \deg^2$ over five different lines of sight, reducing cosmic variance effects. 
+40.5, 62.9, 60.9, 151.2, 151.9 and 150.7 arcmin$^2$ respectively. The total area 
+at redshift 6 corresponds 
+to 740.8 arcmin$^2$ over five different lines of sight, wit a total volume of 
+$1.8 \times 10^6 \textrm{Mpc}^3$.
 Two cameras performed the observations: ACS and WFC3/IR, using 
@@
 end of the LF, magnitudes in the rest frame are in the range $-22.52\leq M_{1600} \leq -16.77$
-\citet{bowens14} calculated LF using a stepwise maximum-likelihood (SWML) based on \citet{efstathiou88}. 
+\citet{bouwens14} calculated LF using a stepwise maximum-likelihood (SWML) based on \citet{efstathiou88}. 
 The Schechter parameters derived are: 
-$\phi^* / \textrm{Mpc}^{-3} =(0.33_{-0.10}^{+0.15}) \times 10 ^{-3}$, 
+$\phi^* =(0.33_{-0.10}^{+0.15}) \times 10 ^{-3}  \textrm{Mpc}^{-3} $, 
 $M^*_{1600} = -21.16\pm 0.20$ and $\alpha = -1.91 \pm 0.09$. 
@@
 
-\citet{finkelstein14} worked also with HST, using the HUDF, CANDELS and GOODS fields, along with two of the Hubble Frontier Fields (HFF): deep parallel observations (unlensed fields) near the Abell 2744 and MACS J0416.1-2403 clusters.
-The HFF uses the ACS and the WFC3/IR with the same filters aforementioned but $z_{850}$.
+\citet{finkelstein14} worked also with HST, using the HUDF, CANDELS and GOODS fields, 
+along with two of the Hubble Frontier Fields (HFF): deep parallel observations (unlensed 
+fields) near the Abell 2744 and MACS J0416.1-2403 clusters. The HFF uses the ACS and 
+the WFC3/IR with the same filters aforementioned but $z_{850}$. Total survey area is around 
+$\sim300\textrm{arcmin}^2$, with 706 photometric candidates at redshift 6 defined as the interval $5.5<z<6.5$. 
+Total volume of this study is around $ 8 \times 10^5 \textrm{Mpc}^3$. The Schechter function parameters they found are $\phi^* =(1.86_{-0.80}^{+0.94}) \times 10 ^{-4}  \textrm{Mpc}^{-3} $, 
+$M^*_{1600} = -21.1_{-0.31}^{+0.25}$ and $\alpha = -2.02_{-0.10}^{+0.10}$.
 
@@
 for 7 candidates using GMOS spectrograph on the Gemini Telescopes, which 
-has a $\ll 5.5$-square arcmin field of view . They show incompleteness in the sample due to 
+has a $\ll 5.5$-square arcmin field of view, giving a volume $\sim 1.09 \times 10^7 \textrm{Mpc}^3$. 
+They show incompleteness in the sample due to 
 foreground contamination and the detection algorithm; there is no warranty to 
@@
  Survey (SXDS). Total observed area is $0.63 \deg^2$ uniformly covered by booth catalogues.
+The volume in this survey is $\sim 3 \times 10^6 \textrm{Mpc}^3$.
 The UKIRT was equipped with the WFCAM using $J K$ filters. The Subaru was equipped 
@@
 $5.7\leq z \leq 6.3$. LF was parameterized according to the Schechter function with 
-$\phi^* / \textrm{Mpc}^{-3} =(1.8 \pm 0.5) \times 10 ^{-3}$, $M^*_{1500} = -20.04\pm 0.12$ 
+$\phi^*  =(1.8 \pm 0.5) \times 10 ^{-3}  \textrm{Mpc}^{-3}$, $M^*_{1500} = -20.04\pm 0.12$ 
 and $\alpha = -1.71 \pm 0.11$.

### 2015-03-17 paper/methodology.tex
MCMC and Dust attenuation

@@
 We used a Markov Chain Monte Carlo method to find the best parameters and its 
-uncertainties over each one of the boxes and each observational dataset.
+uncertainties over each one of the boxes and each observational dataset. The code was written
+on Python using the Scipy, Numpy and Matplotlib libraries.
 
-Observational data set to fit is selected.
-A halo catalog of a cubic box of length 250 Mpc h-1 is selected.
-Initial parameters are introduced.
+First of all, one of the four observational data sets (Bouwens, Finkelstein, Willow and McLure) 
+is selected to be the model to fit.
+From the whole simulated halo catalog, a subsample with cubic box shape of 
+ $250\textrm{Mpc h}^{-1}$ length is selected.
 
-An UV luminosity is given to each halo as function of his mass according to equation
- \ref{eqn:luminosity}.
-Luminosity is converted to magnitude using:
+With an initial set of parameters $(\alpha, \gamma, M_0,$ and $ L_0)$ the UV luminosity
+for the halo is calculated as function of his mass according to equation
+ \ref{eqn:luminosity}. Then Luminosity is converted to magnitude units using:
   \[ M_{UV} = 51.82 - 2.5 \log_{10}(L_{UV}). \]
@@
 
-Once having the LF, we compare our LF against observed LF. Our likelihood estimator is 
-the sum of the square difference over each bin, divided by the number of degrees of 
-freedom. We worked on the logarithmic space of luminosities to have a good fitting on
+Once having the LF, we compare our LF against observed LF. The error function we consider
+is the sum of the square difference over each bin, divided by the observational data uncertain.
+\[ \chi^2  = \sum_{i=o}^{n} \frac {\left( x_{i,obs} - x_{i,fit} \right)^2 }{2\sigma_i^2}\]
+We worked on the logarithmic space of luminosities to have a good fitting on
 six decades.
 
-\[ \chi^2  = \sum_{i=o}^{n}\left( x_{i,obs} - x_{i,fit} \right)^2 \]
+The likelihood will have this property:
+\[ \mathcal{L} \propto \exp \left(  -\frac{\chi ^2}{n} \right) \], where $n$ is the number of degrees
+of freedom. We have the maximum likelihood when the error is the minimum.
 
-\[ \mathcal{L} \propto \exp \left( \frac{\chi ^2}{n} \right) \]
+Each MCMC step will have have a small variation of the parameters, the UV luminosity and magnitude are 
+calculated again for each halo, we have a new error $\chi_{new}^2$ and a new likelihood 
+$ \mathcal{L}_{new} $.
 
-Then we have a small variation on the parameters, it gives us a new LF and a new 
-likelihood estimator $\chi^2$.
+Following the Metropolis method, we compare the new and the old likelihood:
+\[ R =\frac{ \mathcal{L}_{new}  }{ \mathcal{L}_{old} }  = 
+exp( \chi_{new}^2 - \chi_{old}^2 )
+\]
 
-We compare the new fitting versus the old fitting.
+If $  R \geq 1$, then we immediate accept the new set of parameters and start the next MCMC step.
 
-Some restrictions where imposed over two parameters to guarantee convergence in the 
-MCMC method: $0 \leq \alpha \leq 1.8 $  and $\gamma \geq 0$.
+Else, we have a chance to keep the new set. When $ R < 1$, we compare with a uniformly 
+random number $p$ in the range $[0,1]$. if $ R>p$ we accept the new set of parameters and start
+the next MCMC step. 
+Else we reject the new set and start again with the old set.
 
-%MCMC, maximum likelihood.
+We performed 10.000 effective MCMC steps, plus 1.000 thermalization steps over each box.
+We repeated for the same box without consider dust attenuation.
 
-%Python, Ipython Notebook, Scipy, Matplotlib, Numpy. Astropy
+Then we perform the same method over the 64 boxes and the resting three data sets.
+
+The restrictions imposed over the parameters where $0 \leq \alpha \leq 2.0 $  and 
+$\gamma \geq 0$.
+
 Finally, the UV luminosity for each galaxy can be directly related with SFR according 

### 2015-03-17 program/observational_data.py
addition of commented lines

@@ -1,5 +1,11 @@
-# Last modification: 2014-nov-26 - Bogota
-# New lists created
+# Last modification: 2015-mar-17 - West Lafayette
+# commented lines added with "OD# Name"
+
+# OD1 Willott
+# OD2 Bouwens
+# OD3 McLure
+# OD4 Finkelstein
+
 
 from numpy import *
 

### 2015-03-18 paper/discussion.tex
Paper: initial results

@@
 
-\begin{figure}
-\epsscale{1.00}
-\plotone{fig/cosmic_variance.pdf}
-\caption{Cosmic Variance: The Luminosity Function is made using the DMH catalog 
-from the full box and the set of parameters from the small boxes.}
-\label{graph_cosmic_variance}
-\end{figure}
+%\citep{lundgren14} SFR evolution from $z=1$ to $6$
 
-\citep{lundgren14} SFR evolution from $z=1$ to $6$
+%\citep{bouwens14} HST Legacy
 
-\citep{bouwens14} HST Legacy
-
-\citep{jiang11} Keck pectroscopy
+%\citep{jiang11} Keck pectroscopy
 
@@
 %L∗ )''BOUWENS 2014 UV LF
-
-\begin{figure}
-\epsscale{1.00}
-\plotone{fig/scattering_plots.png}
-\caption{Covariance of parameters for one small box}
-\label{graph_scattering_plots}
-\end{figure}
-
-\begin{figure}
-\epsscale{1.00}
-\plotone{fig/SFR_DMHM_wo.pdf}
-\caption{Star formation rate as function of the dark matter halo mass without dust attenuation. 
-Solid lines represents the mean SFR value over the small boxes within $50\%$  shaded region. }
-\label{graph_SFR_DMHM_wo}
-\end{figure}
-
-\begin{figure}
-\epsscale{1.00}
-\plotone{fig/SFR_DMHM_w.pdf}
-\caption{Star formation rate as function of the dark matter halo mass with dust attenuation. 
-Solid lines represents the mean SFR value over the small boxes within $50\%$  shaded region. }
-\label{graph_SFR_DMHM_w}
-\end{figure}

### 2015-03-18 paper/results.tex
Paper: initial results

\section{Results}

\begin{figure}
\epsscale{1.00}
\plotone{fig/OD3_w_15.pdf}
\caption{Parameter dispersion: The 10.000 MCMC step parameters histogram for OD3 over the small boxe 15
with dust attenuation.}
\label{fig:ParamDispWithDust}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/OD3_wo_15.pdf}
\caption{Parameter dispersion: The 10.000 MCMC step parameters histogram for OD3 over the small boxe 15
with dust attenuation.}
\label{fig:ParamDispWithoutDust}
\end{figure}

$\gamma$ always has the best coincidence for the minimum at the 10\%.

%\begin{figure}
%\epsscale{1.00}
%\plotone{fig/cosmic_variance.pdf}
%\caption{Cosmic Variance: The Luminosity Function is made using the DMH catalog 
%from the full box and the set of parameters from the small boxes.}
%\label{graph_cosmic_variance}
%\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/bestpar_disp_w_OD3.pdf}
\caption{Cosmic Variance: The best fit parameters histogram for OD3 over the 64 small boxes 
with dust attenuation.}
\label{fig:ParamScatteringWithDust}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/bestpar_disp_w_OD3.pdf}
\caption{Cosmic Variance: The best fit parameters histogram for OD3 over the 64 small boxes 
without dust attenuation.}
\label{fig:ParamScatteringWithoutDust}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/scattering_plots.png}
\caption{Covariance of parameters for one small box}
\label{graph_scattering_plots}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/SFR_DMHM_wo.pdf}
\caption{Star formation rate as function of the dark matter halo mass without dust attenuation. 
Solid lines represents the mean SFR value over the small boxes within $50\%$  shaded region. 
Comparison with the GALFORM semi-analitical model \citep{gonzalez14} and a implementation
of abundance matching model \citep{behroozi13}. }
\label{graph_SFR_DMHM_wo}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/SFR_DMHM_w.pdf}
\caption{Star formation rate as function of the dark matter halo mass with dust attenuation. 
Solid lines represents the mean SFR value over the small boxes within $50\%$  shaded region.
Comparison with the GALFORM semi-analitical model \citep{gonzalez14} and a implementation
of abundance matching model \citep{behroozi13}. }
\label{graph_SFR_DMHM_w}
\end{figure}

### 2015-03-18 paper/the_bibliography.tex
Methodology: Dust attenuation
Paper: initial results

@@
 
-\bibitem[Bouwens et al.(2012)]{bouwens12} Bouwens, R. J. et al. 2012, \apj, 752, 5 	
+\bibitem[Bouwens et al.(2012a)]{bouwens12} Bouwens, R. J. et al. 2012a, \apj, 752, 5 	
 		%2012ApJ...752L...5B
 % Observational luminosity function
+
+\bibitem[Bouwens et al.(2012b)]{bouwens12b} Bouwens, R. J., G. D. Illingworth, 
+P. A. Oesch, M. Franx, I. Labbé, M. Trenti, P. van Dokkum, et al. 2012b. \apj, 754,83
+% Dust Attenuation
 
@@
 \bibitem[Col\'in et al.(1999)]{colin99}
-Col\'n, Pedro, Anatoly A. Klypin, Andrey V. Kravtsov, and Alexei M. Khokhlov. 
+Col\'in, Pedro, Anatoly A. Klypin, Andrey V. Kravtsov, and Alexei M. Khokhlov. 
 1999, \apj , 523,32
@@
 % Observational luminosity function
+
+\bibitem[Gonzalez-Perez et al(2014)]{gonzalez14}
+Gonzalez-Perez, V., C. G. Lacey, C. M. Baugh, C. D. P. Lagos, J. Helly, D. J. R. Campbell, and P. D. Mitchell. 2014.\mnras, 439, 264
+% GALFORM semi-analytical model
 
@@
 		%1998ApJ...498..106M
-\bibitem[McLure et al.(2009)]{mclure09} McLure, R. J., M. Cirasuolo, J. S. Dunlop, S. Foucaud, \and O. Almaini. 2009, \mnras, 395, 2196	
+\bibitem[McLure et al.(2009)]{mclure09} McLure, R. J., M. Cirasuolo, J. S. Dunlop, S. Foucaud, 
+\and O. Almaini. 2009, \mnras, 395, 2196	
 		%2009MNRAS.395.2196M
+
+\bibitem[Meurer et al.(1999)]{meurer99} Meurer, Gerhardt R., Timothy M. Heckman, 
+\and Daniela Calzetti. 1999, \apj, 521, 64
+% Dust Attenuation
+
 \bibitem[Moster et al.(2010)]{moster10} Moster, Benjamin P. et al. 2010, \apj, 710, 
@@
 
+\bibitem[Smit et al.(2012)]{smit12} Smit, Renske, Rychard J. Bouwens, Marijn Franx, Garth D. 
+Illingworth, Ivo Labbé, Pascal A. Oesch, \and Pieter G. van Dokkum. 2012, \apj 756,14
+% Dust Attenuation
+
 \bibitem[Steidel et al.(2003)]{steidel03} Steidel, Charles C. et al. 2003, \apj, 592, 

### 2015-04-17 paper/ms.tex
unifyied manuscript

\documentclass{emulateapj}
\submitted{{\it Submitted for publication in ApJ}}
\usepackage{multirow,color,wrapfig,ulem}
\usepackage {graphicx}
\usepackage{graphics}
\usepackage{amsmath}
\usepackage[dvips]{epsfig}
\bibliographystyle{apj}
\newcommand{\avg}[1]{\langle{#1}\rangle}  
\newcommand{\nscatt}{\langle N_{\rm  scatt}\rangle}
\newcommand{\ly}{{\ifmmode{{\rm Ly}\alpha~}\else{Ly$\alpha$~}\fi}}
\newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}   
\newcommand{\hGpc}{{\ifmmode{h^{-1}{\rm Gpc}}\else{$h^{-1}$Gpc }\fi}}   
\newcommand{\hmpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}  
\newcommand{\hkpc}{{\ifmmode{h^{-1}{\rm kpc}}\else{$h^{-1}$kpc }\fi}}  
\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm
        {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}   
\newcommand{\hmsun}{{\ifmmode{h^{-1}{\rm
        {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}   
\newcommand{\Msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
\newcommand{\msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
\newcommand{\lya}{{Lyman $\alpha$~}}
\newcommand{\clara}{{\texttt{CLARA}}~}
\newcommand{\rand}{{\ifmmode{{\mathcal{R}}}\else{${\mathcal{R}}$ }\fi}}  
\newcommand{\hs}{{\hspace{1mm}}}  
\newcommand{\kms}{{\ifmmode{{\mathrm{\,km\ s}^{-1}}}\else{\,km~s$^{-1}$}\fi}}
% definition to produce a "less than or similar to" symbol
\def\lsim{~\rlap{$<$}{\lower 1.0ex\hbox{$\sim$}}}
% definition to produce a "greater than or similar to" symbol
\def\gsim{~\rlap{$>$}{\lower 1.0ex\hbox{$\sim$}}}
%@arxiver{fig3.pdf,fig11a.pdf, fig11b.pdf} 
\begin{document}

\title{The connection between star formation rate and dark matter halo
  mass in the epoch of reionization}  
\shorttitle{SFR and DM halo mass during reionization}

\shortauthors{Gomez, Forero-Romero}

\author{Felipe Gomez, Jaime E. Forero-Romero}  
\affil{Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
No. 18A-10, Edificio Ip, Bogot\'a, Colombia}
\email{fl.gomez10@uniandes.edu.co}
\email{je.forero@uniandes.edu.co}

\keywords{galaxies: high-redshift --- methods: numerical} 
\begin{abstract}
We procent updated constraints between the star formation rate and
dark matter halo mass at redshift $z\sim 6$.
The observational basis for our work is the luminosity function data
obtained with  from CFHTLS, HST Legacy Survey and UKIDSS.
The constrains are based on an abundance matching method using data
from cosmological N-body simulations in order to take into account the impact
of cosmic variance in our estimates.

\end{abstract}

\section{Introduction}
\label{sec:intro}
Cosmological simulations still playing an important role on astrophysics and
cosmology. They have become the bridge between observations and theory, a
laboratory where is possible to create universes with different parameters and
new physics.

This is an important tool in the study of dark matter. Since its existence was
purposed, DM has been not observed directly neither on telescopes or high energy
particle colliders, there exists many other theories explaining the observed
universe behavior modifying the gravity itself.

The most successful and accepted cosmological model is the Lambda-CDM. 
Dark matter is a significative component of the universe.
\citep{trimble87}

Hierarchy Structure Evolution: Early formation of small structures
merging on major structures after.

From simulations, Halo Mass Function as function of redshift (or time).

In this paper is established a relation between dark matter and galaxy
luminosity functions at high redshifrt. This relation is a direct
connection between the Lambda-CDM model and the farthest galaxy observations
made with space and grounded telescopes.

Star formation rate as function of time. Peak at $z\sim 2$.

Main Objetive: Reproduce the observed luminosity function at redshift $z=5.9$
from a DMH catalog from simulations.

This paper is organized as follows: In section 2... in section 3...

  \subsection{Halo Mass Function (HMF)}

%  The HMF is created using the DMH catalog from the Multidark Database 
%\citep{riebe13}.

  \subsection{Cosmic Variance}

\section{Linking Galaxy Luminosity Function (GLF) and
  Dark Matter Halo (DMH) mass}

\subsection{Magnitude to Luminosity}

Luminosity Functions (LF) are usually expressed in terms of magnitude instead 
luminosity. Luminosity is the energy emmited by a source in a given wavelengt range, 
is a physical quantity.

Magnitude is a classification inherited from ancient Greeks, this
quantifies the response of the first astrometric device: the human eye, this
perception grows loarithmically with the retrieved radiation.

Luminosity of any object can be compared with Sun Luminosity $(L_{\lambda
\odot})$ at any wavelengt. With the Sun Magnitude as reference
$(M_{\lambda \odot})$, the absolute magnitud of the objet  at an specific
wavelengt is given by: 
 \[ M_{\lambda} = M_{\lambda \odot} - 2.5 \log_{10}\left( 
\frac{L_\lambda}{L_{\lambda \odot}} \right) \]
  The solar absolute magnitude in the U filter is $M_{U\odot} = 5.61$,
and the solar luminosity in the same filter is $L_{U\odot} = 10^{18.48} 
\textrm{ergs s}^{-1}\textrm{Hz}^{-1}$ or $ L_{U\odot} = 3.02 \times 10^{18} 
\textrm{ergs s}^{-1}\textrm{Hz}^{-1}$. The solar luminosity can be used as
refference unit, in this fashion, the typical luminosity of a galaxy can be expresed in
terms of $10^{8}-10^{11}$ times the sun luminosity.

  The absolute magnitude of a galaxy equation in the U filter:
  %\[ M_{U} = 5.61 - 2.5 \log_{10}(L_{U}) + 2.5\times18.48\]
  %gives the magnitude in the U filter of an astrophysical source:
  \[ M_{U} = 51.82 - 2.5 \log_{10}(L_{U}) \]

 %\subsection{Best Fitting Parameters}

\section{Observational Background}
\label{sec:theo}

This paper is based on four main observational data sets from the Hubble Space Telescope 
and three ground-based telescopes. All $z\sim 6$ LBG candidates where discovered using using 
the drop-out technique\citep{steidel03}. All magnitudes are in AB system.
%%%%%%%%%%%%%%Steidel 1996, Bunker 2003

The data from the Hubble Space Telescope Legacy (HSTL) \citep{bouwens14} is a compilation 
of observations since the installation of the Advanced Camera for Surveys (ACS) in 2002, 
through the near-infrared Wide Field Camera 3 (WFC3/IR) installed in 2009, up to 2012. 
The HST fields of view are: XDF, HUDF09-1, HUDF09-2, CANDELS-S/Deep, 
CANDELS-S/Wide, ERS, CANDELS-N/Deep, CANDELS-N/Wide, CANDELS-UDS, 
CANDELS-COSMOS and CANDELS-EGS, with areas of 4.7, 4.7, 4.7, 64.5, 34.2, 
40.5, 62.9, 60.9, 151.2, 151.9 and 150.7 arcmin$^2$ respectively. The total area 
at redshift 6 corresponds 
to 740.8 arcmin$^2$ over five different lines of sight, wit a total volume of 
$1.8 \times 10^6 \textrm{Mpc}^3$.
Two cameras performed the observations: ACS and WFC3/IR, using 
$B_{435}$, $V_{606}$, $ i_{814}$, $ z_{850}$, $ I_{814}$, $Y_{098}$, $Y_{105}$, $J{125}$, 
$JH_{140}$ and $H_{160}$ filters.
The limit magnitude is between $\sim27.5$mag in CANDELS-EGS and$\sim30 $mag in the 
deepest field (XDF). Total number of z=6 LBG candidates is 940, most of them in the faint 
end of the LF, magnitudes in the rest frame are in the range $-22.52\leq M_{1600} \leq -16.77$
\citet{bouwens14} calculated LF using a stepwise maximum-likelihood (SWML) based on \citet{efstathiou88}. 
The Schechter parameters derived are: 
$\phi^* =(0.33_{-0.10}^{+0.15}) \times 10 ^{-3}  \textrm{Mpc}^{-3} $, 
$M^*_{1600} = -21.16\pm 0.20$ and $\alpha = -1.91 \pm 0.09$. 
\citet{bouwens14} reported that using just few fields of view, UVLF has a slightly non-Schechter-like form.

\citet{finkelstein14} worked also with HST, using the HUDF, CANDELS and GOODS fields, 
along with two of the Hubble Frontier Fields (HFF): deep parallel observations (unlensed 
fields) near the Abell 2744 and MACS J0416.1-2403 clusters. The HFF uses the ACS and 
the WFC3/IR with the same filters aforementioned but $z_{850}$. Total survey area is around 
$\sim300\textrm{arcmin}^2$, with 706 photometric candidates at redshift 6 defined as the interval $5.5<z<6.5$. 
Total volume of this study is around $ 8 \times 10^5 \textrm{Mpc}^3$. The Schechter function parameters they found are $\phi^* =(1.86_{-0.80}^{+0.94}) \times 10 ^{-4}  \textrm{Mpc}^{-3} $, 
$M^*_{1600} = -21.1_{-0.31}^{+0.25}$ and $\alpha = -2.02_{-0.10}^{+0.10}$.

\citet{willott13} presented the sixth release of the Canada-France-Hawaii 
Telescope Legacy Survey CFHTLS. The observations where performed over four 
separated fields covering a total area $\sim 4 \deg^2$ (a large area), it gives this 
survey great robustness. Optical observations used MegaCam  %%%%%%[CITE REQUIRED] 
with $u^* g' r' i' z'$ filters. The main selection criteria: all the 
objects must be brighter than magnitude $z' = 25.3$. The final 
number of LBGs founded was 40. Moreover, they get spectroscopic confirmation 
for 7 candidates using GMOS spectrograph on the Gemini Telescopes, which 
has a $\ll 5.5$-square arcmin field of view, giving a volume $\sim 1.09 \times 10^7 \textrm{Mpc}^3$. 
They show incompleteness in the sample due to 
foreground contamination and the detection algorithm; there is no warranty to 
have every object brighter than the limit magnitude on the faint limit. The full 
galaxy LF at $z=6$ cannot be obtained as in other studies. Nevertheless, this survey 
was focussed on the highly luminous LBGs. LF is calculated using the stepwise 
maximum likelihood method of \citet{efstathiou88}, within 
magnitudes 
from $M_{1350} = -22.5$ up to $-20.5$. The luminosity function of $z=5.9$ shows 
an exponential decline at the bright end, where feedback processes and inefficient 
last cooling limites star forming in bright galaxies hosted in the most massive halos.

\citet{mclure09} build the luminosity function for $z=5$ and $z=6$ using data from two ground-based
 telescopes: the United Kingdom Infrared Telescope in the near-IR imaging and Subaru 
 Telescope for the optical imaging. They use the first data release of the UKIRT Infrared 
 DeepSky Survey Ultra Deep Survey (UDS), together with the Subaru XMM-Newton 
 Survey (SXDS). Total observed area is $0.63 \deg^2$ uniformly covered by booth catalogues.
The volume in this survey is $\sim 3 \times 10^6 \textrm{Mpc}^3$.
The UKIRT was equipped with the WFCAM using $J K$ filters. The Subaru was equipped 
with the Suprime-Cam with the $B V R i' z'$ filters. All candidates where brighter than 
$z'=26$. The UV rest frame magnitude range is $-22.4\leq M_{1500} \leq-20.6$. The LF 
was calculated using the maximum likelihood estimator of \citet{schmidt68}. 
Their analysis gave a total number of 104 LBG candidates in the redshift range 
$5.7\leq z \leq 6.3$. LF was parameterized according to the Schechter function with 
$\phi^*  =(1.8 \pm 0.5) \times 10 ^{-3}  \textrm{Mpc}^{-3}$, $M^*_{1500} = -20.04\pm 0.12$ 
and $\alpha = -1.71 \pm 0.11$.

The dataset was retrieved from \cite{mclure09} graph using
GAVO-DEXTER\footnote{\url{http://dc.zah.uni-heidelberg.de/dexter/ui/ui/custom}}.

\begin{figure}
\epsscale{1.00} 
\plotone{fig/observational_data.pdf}
\caption{Observational data from \cite{bouwens14,mclure09}and \cite{willott13}.}
\label{graph_observational_data}
\end{figure}

\section{Abundance Matching Methodology}
\label{sec:methodology}

The key element to connect SFR with halo mass from simulations is the observed UVLF. 
If there exist a function whom gives to each halo a UV luminosity then is posible to 
reproduce UVLF from DMH catalogs. The fitting parameters can be explored using a 
Markov Chain Monte-Carlo (MCMC) implementation. Once the parameters are found, 
the SFR-Halo Mass relation have been found.

We use the dark matter halo catalog from the Big MultiDark Plank 1 (MDPL) Simulation 
\citep{klypin14} with 2013 Planck cosmology \citep{planck1}. MDPL is quite similar to the 
Big Bolshoi ($1 \textrm{Gpc h}^{-1}$) \citep{prada12} and 
its predecesor Bolshoi \citep{klypin11} ($250 \textrm{Mpc h}^{-1}$), booth of them with 
WMAP5 cosmology, but MDPL has bigger mass resolution.  Those halo catalogs are 
available at the MultiDark Database\footnote{\url{http://www.multidark.org}} 
\citep{riebe13}.

The MDPL run is a N-body dark matter only simulation based on the L-Gadget2 
code. The simulated volume is a cubic box of $1 \textrm{Gpc h}^{-1}$ side length. 
It has $3840^3$ dark matter particles of 
$1.51\times 9 \textrm{M}_{\odot} \textrm{h}^{-1}$ mass each one.
The 2013 Planck cosmology is defined by the following parameters: $\Omega_M = 0.307$, 
$\Omega_B = 0.048$, $\Omega_\Lambda = 0.730$, $\sigma_8 = 0.829$, $n_s = 0.96$ and 
$H_0 = 67.8$. The DMH Catalog at $z=6$ contains $\sim 10.9 \times 10^7$ 
halos, to avoid incompleteness in the low mass end, halos with mass below 
$10^{10.3} \textrm{M}_{\odot} \textrm{h}^{-1}$ are rejected. In order to study how 
cosmic variance can affect measurements, the original catalog is divided into 64 small 
cubic boxes, with a similar volume to the observations.

The following treatment is applied to every one small box.

The halo abundance matching technique has been widely used \citep{colin99, kravtsov04}
resulting in good reproduction of the observed galaxy clustering. \citep{conroy06, lee09}. 
Here we use the simplest case with few premises: 
\begin{enumerate}
 \item Each halo in the catalog hosts one galaxy. There are not empty
halos, also none of halos has two or more galaxies.
 \item The UV luminosity of each galaxy is function of one variable; the mass of
the DMH in which is located. This function must be monotone, this guarantees that most 
massive halos will host the most luminous galaxies in the same volume.
\end{enumerate}

\subsection{Fitting Model}

The observed UV Luminosity Function has two slopes. To reproduce it we decide to use the
 four parameter model:
  \begin{equation}\label{eqn:luminosity}
  L_{\textrm{\small{UV}}} (M) = L_{0} M \left[ \left( \frac{M}{M_0}\right)^{-\beta} 
		   + \left( \frac{M}{M_0}\right)^{\gamma} 
               \right]^{-1}
  \end{equation}
where $M$ is the hosting DMH mass, $L_{0}$ is a normalization constant, $M_0$
is the critical mass where the luminosity function has a slope change, 
$\beta$ and $\gamma$ are the slopes. This equation has a similar fashion to the
mass to light relation \citep{vandenbosch03} and the mean relation between
stellar mas of a galaxy and the mass of its halo used by \citet{moster10}.

\subsection{Dust Attenuation}

Dust in star forming galaxies absorbs part of the UV radiation and reemits on IR. The more 
massive is the galaxy then more dust contains and dust attenuation will be greater. The 
relation between dust attenuation and magnitude have been already studied, with this relation 
we can infer the dust-free UV luminosity of a galaxy from observations, resulting in  a more 
accurate inferred SFR.

The UV Spectral Slope $\beta$ was introduced by \citet{meurer99} as a UV color to 
study dust attenuation in local starburst galaxies and extrapolating to high redshift galaxies. 
This index appears when a power law fitting is performed over the spectral flux $f$ 
as function of the wavelength $\lambda$;
\[ f \propto \lambda^\beta.\]
The relation for ultra-violet attenuation at $1600 \textrm{\AA}$ they found is:
\begin{equation}
A_{1600} = 4.43 + 1.99 \beta,
\end{equation}
with $A_{1600}$ in magnitude units.

Due LBGs have more similar spectra properties to local starburst galaxies rather than AGNs 
for example, we can assume that local calibration of $\beta-A_{1600}$ can be applied also 
for LBGs,
%%% From Meurer99
``The main requirement is that the data include fluxes in two broad bands or coarse spectra 
covering the rest-frame UV.''

\citet{bouwens12b} uses the fluxes on different bands to estimate $\beta$ on each LBG 
candidate found with $z \sim 4-7$. After in redshift groups they found a linear relation 
between $\beta$ and the UV magnitude:
\begin{equation}
\langle \beta \rangle = \frac{d \beta}{d M_{UV}} \left( M_{UV,AB}+19.5 \right) 
                                   + \beta_{M_{UV}=-19.5}
\end{equation}
with $ \beta_{M_{UV}=-19.5} = -2.20$ and $d \beta/d M_{UV} = -0.21$ at $z=5.9$.

\citet{smit12} used the aforementioned relations to infer the corrected luminosity functions,
i.e. dust-free luminosity functions, and the corrected SFR at $z=4$.

Here we use the inverse relation, starting from the intrinsic or dust-free galaxy magnitude, 
obtaining the observed magnitude:
\begin{equation}
  M_{obs} = \begin{cases} 
                         \frac{M_{int}-4.616}{1.259}, &\mbox{if } A>0 \\
                         M_{int}, &\mbox{else}
                   \end{cases}.
\label{eqn. dust attenuation}
\end{equation}

\subsection{MCMC}
We used a Markov Chain Monte Carlo method to find the best parameters and its 
uncertainties over each one of the boxes and each observational dataset. The code was written
on Python using the Scipy, Numpy and Matplotlib libraries.

First of all, one of the four observational data sets (Bouwens, Finkelstein, Willow and McLure) 
is selected to be the model to fit.
From the whole simulated halo catalog, a subsample with cubic box shape of 
 $250\textrm{Mpc h}^{-1}$ length is selected.

With an initial set of parameters $(\alpha, \gamma, M_0,$ and $ L_0)$ the UV luminosity
for the halo is calculated as function of his mass according to equation
 \ref{eqn:luminosity}. Then Luminosity is converted to magnitude units using:
  \[ M_{UV} = 51.82 - 2.5 \log_{10}(L_{UV}). \]
If we consider the dust attenuation im the equation \ref{eqn. dust attenuation} we have
a dust-corrected UV Luminosity Function.

The luminosity function is constructed as an histogram of the magnitudes normalized by 
the volume of the catalog. Each observed luminosity function has a different bin range.

Once having the LF, we compare our LF against observed LF. The error function we consider
is the sum of the square difference over each bin, divided by the observational data uncertain.
\[ \chi^2  = \sum_{i=o}^{n} \frac {\left( x_{i,obs} - x_{i,fit} \right)^2 }{2\sigma_i^2}\]
We worked on the logarithmic space of luminosities to have a good fitting on
six decades.

The likelihood will have this property:
\[ \mathcal{L} \propto \exp \left(  -\frac{\chi ^2}{n} \right) \], where $n$ is the number of degrees
of freedom. We have the maximum likelihood when the error is the minimum.

Each MCMC step will have have a small variation of the parameters, the UV luminosity and magnitude are 
calculated again for each halo, we have a new error $\chi_{new}^2$ and a new likelihood 
$ \mathcal{L}_{new} $.

Following the Metropolis method, we compare the new and the old likelihood:
\[ R =\frac{ \mathcal{L}_{new}  }{ \mathcal{L}_{old} }  = 
exp( \chi_{new}^2 - \chi_{old}^2 )
\]

If $  R \geq 1$, then we immediate accept the new set of parameters and start the next MCMC step.

Else, we have a chance to keep the new set. When $ R < 1$, we compare with a uniformly 
random number $p$ in the range $[0,1]$. if $ R>p$ we accept the new set of parameters and start
the next MCMC step. 
Else we reject the new set and start again with the old set.

We performed 10.000 effective MCMC steps, plus 1.000 thermalization steps over each box.
We repeated for the same box without consider dust attenuation.

Then we perform the same method over the 64 boxes and the resting three data sets.

The restrictions imposed over the parameters where $0 \leq \alpha \leq 2.0 $  and 
$\gamma \geq 0$.

Finally, the UV luminosity for each galaxy can be directly related with SFR according 
to \citet{madau98}.
This model is accurate within the range of $10^8 - 10^9 \textrm{yr}$\citep{kennicutt98}.
The relation between UV luminosity and Star Formation Rate \citep{madau98,kennicutt98} 
is given by:
\begin{equation}
 \textrm{SFR}\left(M_\odot \textrm{yr}^{-1}\right) 
      = 1.4 \times 10^{-28} L_{\nu} \left( \textrm{erg s}^{-1}\textrm{Hz}^{-1} 
	\right)
\end{equation}

\section{Results}
\label{sec:results}

\begin{figure}
\epsscale{1.00}
\plotone{fig/OD3_w_15.pdf}
\caption{Parameter dispersion: The 10.000 MCMC step parameters histogram for OD3 over the small boxe 15
with dust attenuation.}
\label{fig:ParamDispWithDust}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/OD3_wo_15.pdf}
\caption{Parameter dispersion: The 10.000 MCMC step parameters histogram for OD3 over the small boxe 15
with dust attenuation.}
\label{fig:ParamDispWithoutDust}
\end{figure}

$\gamma$ always has the best coincidence for the minimum at the 10\%.

\begin{figure}
\epsscale{1.00}
\plotone{fig/bestpar_disp_w_OD3.pdf}
\caption{Cosmic Variance: The best fit parameters histogram for OD3 over the 64 small boxes 
with dust attenuation.}
\label{fig:ParamScatteringWithDust}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/bestpar_disp_w_OD3.pdf}
\caption{Cosmic Variance: The best fit parameters histogram for OD3 over the 64 small boxes 
without dust attenuation.}
\label{fig:ParamScatteringWithoutDust}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/scattering_plots.png}
\caption{Covariance of parameters for one small box}
\label{graph_scattering_plots}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/SFR_DMHM_wo.pdf}
\caption{Star formation rate as function of the dark matter halo mass without dust attenuation. 
Solid lines represents the mean SFR value over the small boxes within $50\%$  shaded region. 
Comparison with the GALFORM semi-analitical model \citep{gonzalez14} and a implementation
of abundance matching model \citep{behroozi13}. }
\label{graph_SFR_DMHM_wo}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/SFR_DMHM_w.pdf}
\caption{Star formation rate as function of the dark matter halo mass with dust attenuation. 
Solid lines represents the mean SFR value over the small boxes within $50\%$  shaded region.
Comparison with the GALFORM semi-analitical model \citep{gonzalez14} and a implementation
of abundance matching model \citep{behroozi13}. }
\label{graph_SFR_DMHM_w}
\end{figure}

\section{Discussion}
\label{sec:discussion}

\section{Conclusions}
\label{sec:conclusions}

\section*{Acknowledgments}
Acknowledgments...\\

\bibliography{the_bibliography}

\end{document}

### 2015-04-17 paper/ms.tex
first dump in ms*

@@
 
+\subsection{Star Formation Rate}
+
+The age of a star can be estimated by analyzing its spectrum. But when far
+galaxies are studied, individual stars can not be resolved. Is not 
+possible to make a detailed census of the galaxy popullation. Only is possible 
+to get information from the whole stellar population, an integrated spectrum.
+
+There is a  method\citep{madau98} in wich a linear relation between SFR
+and luminosity in specific wavelength ranges can be assumed. This model allows
+to estimate the young stars fraction and the mean SFR over periods of $10^8 -
+10^9 \textrm{yr}$\citep{kennicutt98}. The luminosity in the model, comes from
+the UV and the FIR broadband, also from speciffic recombination lines.
+
+In a typical galaxy spectrum the visible wavelengths are dominated by the main 
+sequence stars (A to early F) and G-K giants. In few wavelength ranges we have 
+a significative contribution from the young stars rather than the old stars. 
+The infrared and far infrared wavelengths emission is dominated by dust, this 
+dust is  heated by the whole stellar popullation, in particular by young, 
+UV-bright stars \citep{law11}.
+
+On active galaxies the UV broadband emission is dominated by late-O
+and early-B type stars, with temperature near to 40.000K. These hot and massive
+stars has a lifetime below $10^7\textrm{Gyr}$, they spend their nuclear fuel
+faster than smaller and cooler sunlike stars.
+
+The relation between UV luminosity and Star Formation Rate
+\citep{madau98,kennicutt98} 
+is given by:
+\begin{equation}
+ \textrm{SFR}\left(M_\odot \textrm{yr}^{-1}\right) 
+      = 1.4 \times 10^{-28} L_{\nu} \left( \textrm{erg s}^{-1}\textrm{Hz}^{-1} 
+	\right)
+\end{equation}
+
+  With Initial Mass Function (IMF) between $0.1 M_\odot$ 
+ and $100 M_\odot$, in the range of $1250-2500 \mathring{\textrm{A}} $
+
+The star forming rate will be:
+  \begin{equation}
+  SFR = k \times L_{0} M \left[ \left( \frac{M}{M_0}\right)^{-\beta} 
+		   + \left( \frac{M}{M_0}\right)^{\gamma} 
+               \right]^{-1}
+  \end{equation}
+
+\subsection{Dust Absorption}
+
 This paper is based on four main observational data sets from the Hubble Space Telescope 
@@
 the drop-out technique\citep{steidel03}. All magnitudes are in AB system.
-%%%%%%%%%%%%%%Steidel 1996, Bunker 2003
 
@@
 
+\subsection{The Luminosity Model}
+
+In this model we have made two assumptions:
+\begin{enumerate}
+ \item Each halo in the catalog hosts one galaxy. There are not empty
+halos, also none of halos has two or more galaxies.
+ \item The UV luminosity of each galaxy is function of one variable: the mass of
+the DMH in wich is located.
+\end{enumerate}
+
+The simplest relation we can have is a powerlaw:
+ \begin{equation}
+  L = L_0 M^\alpha
+ \end{equation}
+but has not well agreement with observed luminosity functions.
+
+A better model is a four parameter function. Each galaxy has a luminosity given
+by:
+  \begin{equation}
+  L = L_{0} M \left[ \left( \frac{M}{M_0}\right)^{-\beta} 
+		   + \left( \frac{M}{M_0}\right)^{\gamma} 
+               \right]^{-1}
+  \end{equation}
+where $M$ is the hosting DMH mass, $L_{0}$ is a normalization constant, $M_0$
+is the critical mass where the luminosity function has a slope change, 
+$\beta$ and $\gamma$ are the slopes. This equation has a similar fashion to the
+mass to light relation \citep{vandenbosch03} and the mean relation between
+stellar mas of a galaxy and the mas of its halo used by \cite{moster10}.
+
+There are more complex models\citep{lee09} that includes a random behavior:
+galaxies has not synchronization on the beginning of star forming stage, also
+this stage may be time limited. This is called duty cycle. It is probable to
+have in the observations some invisible galaxies in the UV continuum due their
+duty cycle may has not started as well it may ended. Also may be present a
+normal distribution of the luminosity around the expected values.
+
 \section{Results}
@@
 Comparison with the GALFORM semi-analitical model \citep{gonzalez14} and a implementation
-of abundance matching model \citep{behroozi13}. }
+of abundance matching model \citep{Behroozi13}. }
 \label{graph_SFR_DMHM_wo}
@@
 Comparison with the GALFORM semi-analitical model \citep{gonzalez14} and a implementation
-of abundance matching model \citep{behroozi13}. }
+of abundance matching model \citep{Behroozi13}. }
 \label{graph_SFR_DMHM_w}
@@
 
-\bibliography{the_bibliography}
+\bibliography{references}
 

### 2015-04-21 paper/ms.tex

@@
 \begin{abstract}
-We procent updated constraints between the star formation rate and
+We present updated constraints between the star formation rate and
 dark matter halo mass at redshift $z\sim 6$.
@@
 obtained with from CFHTLS, HST Legacy Survey and UKIDSS.
-The constrains are based on an abundance matching method using data
+The constrains are based on an abundance matching methodology using data
 from cosmological N-body simulations in order to take into account the impact
 of cosmic variance in our estimates.
-
 \end{abstract}
@@
 code. The simulated volume is a cubic box of $1 \textrm{Gpc h}^{-1}$ side length. 
-It has $3840^3$ dark matter particles of 
-$1.51\times 9 \textrm{M}_{\odot} \textrm{h}^{-1}$ mass each one.
-The 2013 Planck cosmology is defined by the following parameters: $\Omega_M = 0.307$, 
-$\Omega_B = 0.048$, $\Omega_\Lambda = 0.730$, $\sigma_8 = 0.829$, $n_s = 0.96$ and 
-$H_0 = 67.8$. The DMH Catalog at $z=6$ contains $\sim 10.9 \times 10^7$ 
-halos, to avoid incompleteness in the low mass end, halos with mass below 
-$10^{10.3} \textrm{M}_{\odot} \textrm{h}^{-1}$ are rejected. In order to study how 
-cosmic variance can affect measurements, the original catalog is divided into 64 small 
-cubic boxes, with a similar volume to the observations.
+It has $3840^3$ dark matter particles of  $1.51\times 9
+\textrm{M}_{\odot} \textrm{h}^{-1}$ mass each one. The 2013 Planck
+cosmology is defined by the following parameters: $\Omega_M = 0.307$,
+$\Omega_B = 0.048$, $\Omega_\Lambda = 0.730$, $\sigma_8 = 0.829$, $n_s
+= 0.96$ and  $H_0 = 67.8$. The DMH Catalog at $z=6$ contains $\sim
+10.9 \times 10^7$   halos, to avoid incompleteness in the low mass
+end, halos with mass below   $10^{10.3} \textrm{M}_{\odot}
+\textrm{h}^{-1}$ are rejected. In order to study how  
+cosmic variance can affect measurements, the original catalog is
+divided into 64 small   cubic boxes, with a similar volume to the
+observations.
 

### 2015-04-23 paper/ms.tex
figures updated. fontsize corrected.

@@
 
-\shortauthors{Gomez, Forero-Romero}
+\shortauthors{Gomez-Cortes, Forero-Romero}
 
-\author{Felipe Gomez, Jaime E. Forero-Romero}  
+\author{Felipe L. Gomez-Cortes, Jaime E. Forero-Romero}  
 \affil{Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
@@
 
-First of all, one of the four observational data sets (Bouwens, Finkelstein, Willow and McLure) 
+First of all, one of the four observational data sets (Bouwens, Finkelstein, Willott and McLure) 
 is selected to be the model to fit.
@@
 
+Best fit parameters:
+
+Cosmic Variance Dust Attenuation model:
+
+$\log_{10}(L_0)$, mean value = 18.0668181805, 
+cosmic std dev=0.0288558407431, 
+mean sigma per box =0.115498563539
+
+$\log_{10}(M_0)$, mean value = 11.1894829902, 
+cosmic std dev=0.0718242117247, mean 
+sigma per box =0.72909362196
+
+$\beta$, mean value = 1.48014744519, 
+cosmic std dev=0.175026973523, 
+mean sigma per box =1.2988714515
+
+$\gamma$, mean value = 0.402845130968, 
+cosmic std dev=0.0575764062455, 
+mean sigma per box =0.314709555486
+
+\medskip
+
+Cosmic Variance No-Dust Attenuation model:
+
+$\log_{10}(L_0)$, mean value = 17.8076246968, 
+cosmic std dev=0.0198125186745, 
+mean sigma per box =0.150082796188
+
+$\log_{10}(M_0)$, mean value = 11.119460579, 
+smic std dev=0.0601358065131, 
+mean sigma per box =0.642532804052
+
+$\beta$, mean value = 1.43705896343, 
+cosmic std dev=0.178253100134, 
+mean sigma per box =1.37416358513
+
+$\gamma$, mean value = 0.518242492031, 
+cosmic std dev=0.0461244563387, 
+mean sigma per box =0.245817572122
+
 \begin{figure}
 \epsscale{1.00}
-\plotone{fig/OD3_w_15.pdf}
-\caption{Parameter dispersion: The 10.000 MCMC step parameters histogram for OD3 over the small boxe 15
-with dust attenuation.}
-\label{fig:ParamDispWithDust}
+\plotone{fig/OD1_chi2_comparison.pdf}
+\caption{Best fit to Willott comparison between the two models. Each point represent $\chi^2$ 
+calculated over each small-box. The solid line represents the ratio 1:1 }
+\label{fig:OD1_chi2_comparison}
+\end{figure}
+
+\begin{figure*}
+\epsscale{1.00}
+\plotone{fig/OD1_w_dust_box_0.png} % pdf available
+\caption{Parameter dispersion fitting the Willott with the Dust Attenuation model. 
+$1\sigma$ is defined by the likelihood ratio between 0.0 (red) and 0.5 (green)}
+\label{}
+\end{figure*}
+
+\begin{figure*}
+\epsscale{1.00}
+\plotone{fig/OD1_wo_dust_box_0.png} % pdf available
+\caption{Parameter dispersion fitting the Willott with the No-Dust Attenuation model. 
+$1\sigma$ is defined by the likelihood ratio between 0.0 (red) and 0.5 (green)}
+\label{}
+\end{figure*}
+
+\begin{figure}
+\epsscale{1.00}
+\plotone{fig/OD1_CosmicVar1_w_dust.pdf}
+\caption{Individual small-box parameter estimation with dust attenuation: Best fit values 
+to the Willott data set
+(solid line) and $1\sigma$ confidence interval using likelihood ratio $\mathcal{LR}= 0.5$. 
+The $x$ axis corresponds to the box number.}
+\label{}
 \end{figure}
@@
 \epsscale{1.00}
-\plotone{fig/OD3_wo_15.pdf}
-\caption{Parameter dispersion: The 10.000 MCMC step parameters histogram for OD3 over the small boxe 15
-with dust attenuation.}
-\label{fig:ParamDispWithoutDust}
-\end{figure}
-
-$\gamma$ always has the best coincidence for the minimum at the 10\%.
-
-\begin{figure}
-\epsscale{1.00}
-\plotone{fig/bestpar_disp_w_OD3.pdf}
-\caption{Cosmic Variance: The best fit parameters histogram for OD3 over the 64 small boxes 
-with dust attenuation.}
-\label{fig:ParamScatteringWithDust}
+\plotone{fig/OD1_CosmicVar1_wo_dust.pdf}
+\caption{Individual small-box parameter estimation with no-dust attenuation: Best fit values 
+to the Willott data set
+(solid line) and $1\sigma$ confidence interval using likelihood ratio $\mathcal{LR}= 0.5$. 
+The $x$ axis corresponds to the box number.}
+\label{}
 \end{figure}
@@
 \epsscale{1.00}
-\plotone{fig/bestpar_disp_w_OD3.pdf}
-\caption{Cosmic Variance: The best fit parameters histogram for OD3 over the 64 small boxes 
-without dust attenuation.}
-\label{fig:ParamScatteringWithoutDust}
+\plotone{fig/OD1_CosmicVar2_w_dust.pdf}
+\caption{Best fit parameter distribution due cosmic variance with Willott data in the dust
+ attenuation model.}
+\label{}
 \end{figure}
@@
 \epsscale{1.00}
-\plotone{fig/scattering_plots.png}
-\caption{Covariance of parameters for one small box}
-\label{graph_scattering_plots}
+\plotone{fig/OD1_CosmicVar2_wo_dust.pdf}
+\caption{Best fit parameter distribution due cosmic variance with Willott data in the no-dust
+ attenuation model.}
+\label{}
 \end{figure}

### 2015-04-24 paper/ms.tex
Two tables added: best fit parameters for Willott data (with/without dust attenuation)

@@
 
-Best fit parameters:
+\begin{table}
+\begin{center}
+\begin{tabular}{ccccc}\hline\hline
+Parameter  & Mean value & Cosmic Variance & MCMC error\\\hline
+$\log_{10}(L_0)$   & 18.067   & 0.029   & 0.116 \\
+$\log_{10}(M_0)$  & 11.190   & 0.072   & 0.729 \\
+$\beta$                  & 1.4801  & 0.175   & 1.299 \\
+$\gamma$             & 0.40284 & 0.058  & 0.3147\\
+\hline\hline
+\end{tabular}
+\caption{  Average Best fit parameters to the Willott data in the Dust Attenuation Model.} 
+\label{table:Willott_best_fit_parameters}
+\end{center}
+\end{table}
 
-Cosmic Variance Dust Attenuation model:
-
-$\log_{10}(L_0)$, mean value = 18.0668181805, 
-cosmic std dev=0.0288558407431, 
-mean sigma per box =0.115498563539
-
-$\log_{10}(M_0)$, mean value = 11.1894829902, 
-cosmic std dev=0.0718242117247, mean 
-sigma per box =0.72909362196
-
-$\beta$, mean value = 1.48014744519, 
-cosmic std dev=0.175026973523, 
-mean sigma per box =1.2988714515
-
-$\gamma$, mean value = 0.402845130968, 
-cosmic std dev=0.0575764062455, 
-mean sigma per box =0.314709555486
-
-\medskip
-
-Cosmic Variance No-Dust Attenuation model:
-
-$\log_{10}(L_0)$, mean value = 17.8076246968, 
-cosmic std dev=0.0198125186745, 
-mean sigma per box =0.150082796188
-
-$\log_{10}(M_0)$, mean value = 11.119460579, 
-smic std dev=0.0601358065131, 
-mean sigma per box =0.642532804052
-
-$\beta$, mean value = 1.43705896343, 
-cosmic std dev=0.178253100134, 
-mean sigma per box =1.37416358513
-
-$\gamma$, mean value = 0.518242492031, 
-cosmic std dev=0.0461244563387, 
-mean sigma per box =0.245817572122
+\begin{table}
+\begin{center}
+\begin{tabular}{ccccc}\hline\hline
+Parameter  & Mean value & Cosmic Variance & MCMC error\\\hline
+$\log_{10}(L_0)$   & 17.807   & 0.020   & 0.150 \\
+$\log_{10}(M_0)$  & 11.119    & 0.060   & 0.642 \\
+$\beta$                  &  1.437    & 0.178   & 1.374 \\
+$\gamma$             &   0.518   & 0.046  & 0.246\\
+\hline\hline
+\end{tabular}
+\caption{  Average Best fit parameters to the Willott data in the No-Dust Attenuation Model.} 
+\label{table:Willott_best_fit_parameters_no_dust}
+\end{center}
+\end{table}
 

### 2015-04-24 paper/ms.tex
cleanig the intro

@@
 \begin{abstract}
-We present updated constraints between the star formation rate and
-dark matter halo mass at redshift $z\sim 6$.
+We present updated constraints on the relationship between the star
+formation rate and dark matter halo mass at redshift $z\sim 6$.
 The observational basis for our work is the luminosity function data
@@
 of cosmic variance in our estimates.
+We also measure the influence on the results of the dust extinction
+scaling derived from observations by Bouwens.
+We compare our results against the results of abundance matching
+methods, a semi-analytic model of galaxy formation (GALFORM) and a
+hydrodynamical simulation (Illustris).
 \end{abstract}
@@
 \label{sec:intro}
-Cosmological simulations still playing an important role on astrophysics and
-cosmology. They have become the bridge between observations and theory, a
-laboratory where is possible to create universes with different parameters and
-new physics.
-
-This is an important tool in the study of dark matter. Since its existence was
-purposed, DM has been not observed directly neither on telescopes or high energy
-particle colliders, there exists many other theories explaining the observed
-universe behavior modifying the gravity itself.
-
-The most successful and accepted cosmological model is the Lambda-CDM. 
-Dark matter is a significative component of the universe.
-\citep{trimble87}
-
-Hierarchy Structure Evolution: Early formation of small structures
-merging on major structures after.
-
-From simulations, Halo Mass Function as function of redshift (or time).
-
-In this paper is established a relation between dark matter and galaxy
-luminosity functions at high redshifrt. This relation is a direct
-connection between the Lambda-CDM model and the farthest galaxy observations
-made with space and grounded telescopes.
-
-Star formation rate as function of time. Peak at $z\sim 2$.
-
-Main Objetive: Reproduce the observed luminosity function at redshift $z=5.9$
-from a DMH catalog from simulations.
-
-This paper is organized as follows: In section 2... in section 3...
 
   \subsection{Halo Mass Function (HMF)}
-
-%  The HMF is created using the DMH catalog from the Multidark Database 
-%\citep{riebe13}.
 
@@
 
-Luminosity Functions (LF) are usually expressed in terms of magnitude instead 
-luminosity. Luminosity is the energy emmited by a source in a given wavelengt range, 
-is a physical quantity.
-
-Magnitude is a classification inherited from ancient Greeks, this
-quantifies the response of the first astrometric device: the human eye, this
-perception grows loarithmically with the retrieved radiation.
-
+L
 Luminosity of any object can be compared with Sun Luminosity $(L_{\lambda

### 2015-04-24 paper/ms.tex
removing section 2

@@
 \label{sec:intro}
-
-  \subsection{Halo Mass Function (HMF)}
-
-  \subsection{Cosmic Variance}
-
-\section{Linking Galaxy Luminosity Function (GLF) and
-  Dark Matter Halo (DMH) mass}
-
-\subsection{Magnitude to Luminosity}
-
-L
-Luminosity of any object can be compared with Sun Luminosity $(L_{\lambda
-\odot})$ at any wavelengt. With the Sun Magnitude as reference
-$(M_{\lambda \odot})$, the absolute magnitud of the objet  at an specific
-wavelengt is given by: 
- \[ M_{\lambda} = M_{\lambda \odot} - 2.5 \log_{10}\left( 
-\frac{L_\lambda}{L_{\lambda \odot}} \right) \]
-  The solar absolute magnitude in the U filter is $M_{U\odot} = 5.61$,
-and the solar luminosity in the same filter is $L_{U\odot} = 10^{18.48} 
-\textrm{ergs s}^{-1}\textrm{Hz}^{-1}$ or $ L_{U\odot} = 3.02 \times 10^{18} 
-\textrm{ergs s}^{-1}\textrm{Hz}^{-1}$. The solar luminosity can be used as
-refference unit, in this fashion, the typical luminosity of a galaxy can be expresed in
-terms of $10^{8}-10^{11}$ times the sun luminosity.
-
-  The absolute magnitude of a galaxy equation in the U filter:
-  %\[ M_{U} = 5.61 - 2.5 \log_{10}(L_{U}) + 2.5\times18.48\]
-  %gives the magnitude in the U filter of an astrophysical source:
-  \[ M_{U} = 51.82 - 2.5 \log_{10}(L_{U}) \]
-
- %\subsection{Best Fitting Parameters}
 

### 2015-04-24 paper/ms.tex
removing generic text on the star formation rate

@@
 formation rate and dark matter halo mass at redshift $z\sim 6$.
-The observational basis for our work is the luminosity function data
-obtained with from CFHTLS, HST Legacy Survey and UKIDSS.
+The observational basis for our work is the restframe UV luminosity
+function data obtained with CFHTLS, HST Legacy Survey and UKIDSS.
 The constrains are based on an abundance matching methodology using data
@@
 We compare our results against the results of abundance matching
-methods, a semi-analytic model of galaxy formation (GALFORM) and a
-hydrodynamical simulation (Illustris).
+methods (to the stellar mass), a semi-analytic model of galaxy
+formation (GALFORM) and a hydrodynamical simulation (Illustris).
 \end{abstract}
@@
 
-\section{Observational Background}
+\section{Observational Constraints}
 \label{sec:theo}
-
-\subsection{Star Formation Rate}
-
-The age of a star can be estimated by analyzing its spectrum. But when far
-galaxies are studied, individual stars can not be resolved. Is not 
-possible to make a detailed census of the galaxy popullation. Only is possible 
-to get information from the whole stellar population, an integrated spectrum.
-
-There is a  method\citep{madau98} in wich a linear relation between SFR
-and luminosity in specific wavelength ranges can be assumed. This model allows
-to estimate the young stars fraction and the mean SFR over periods of $10^8 -
-10^9 \textrm{yr}$\citep{kennicutt98}. The luminosity in the model, comes from
-the UV and the FIR broadband, also from speciffic recombination lines.
-
-In a typical galaxy spectrum the visible wavelengths are dominated by the main 
-sequence stars (A to early F) and G-K giants. In few wavelength ranges we have 
-a significative contribution from the young stars rather than the old stars. 
-The infrared and far infrared wavelengths emission is dominated by dust, this 
-dust is  heated by the whole stellar popullation, in particular by young, 
-UV-bright stars \citep{law11}.
-
-On active galaxies the UV broadband emission is dominated by late-O
-and early-B type stars, with temperature near to 40.000K. These hot and massive
-stars has a lifetime below $10^7\textrm{Gyr}$, they spend their nuclear fuel
-faster than smaller and cooler sunlike stars.
-
-The relation between UV luminosity and Star Formation Rate
-\citep{madau98,kennicutt98} 
-is given by:
-\begin{equation}
- \textrm{SFR}\left(M_\odot \textrm{yr}^{-1}\right) 
-      = 1.4 \times 10^{-28} L_{\nu} \left( \textrm{erg s}^{-1}\textrm{Hz}^{-1} 
-	\right)
-\end{equation}
-
-  With Initial Mass Function (IMF) between $0.1 M_\odot$ 
- and $100 M_\odot$, in the range of $1250-2500 \mathring{\textrm{A}} $
-
-The star forming rate will be:
-  \begin{equation}
-  SFR = k \times L_{0} M \left[ \left( \frac{M}{M_0}\right)^{-\beta} 
-		   + \left( \frac{M}{M_0}\right)^{\gamma} 
-               \right]^{-1}
-  \end{equation}
 
@@
 \label{sec:methodology}
+
+The relation between UV luminosity and Star Formation Rate
+\citep{madau98,kennicutt98} 
+is given by:
+\begin{equation}
+ \textrm{SFR}\left(M_\odot \textrm{yr}^{-1}\right) 
+      = 1.4 \times 10^{-28} L_{\nu} \left( \textrm{erg s}^{-1}\textrm{Hz}^{-1} 
+	\right)
+\end{equation}
+
+  With Initial Mass Function (IMF) between $0.1 M_\odot$ 
+ and $100 M_\odot$, in the range of $1250-2500 \mathring{\textrm{A}} $
+
+The star forming rate will be:
+  \begin{equation}
+  SFR = k \times L_{0} M \left[ \left( \frac{M}{M_0}\right)^{-\beta} 
+		   + \left( \frac{M}{M_0}\right)^{\gamma} 
+               \right]^{-1}
+  \end{equation}
 

### 2015-04-24 paper/ms.tex
minor edits

@@
 function data obtained with CFHTLS, HST Legacy Survey and UKIDSS.
-The constrains are based on an abundance matching methodology using data
-from cosmological N-body simulations in order to take into account the impact
-of cosmic variance in our estimates.
-We also measure the influence on the results of the dust extinction
+The constraints are based on an abundance matching methodology to the
+observational data using cosmological N-body simulations.
+We also take into account the influence on the results of the dust extinction
 scaling derived from observations by Bouwens.
@@
 
-\section{Observational Constraints}
+All magnitudes are in AB system.
+\section{Observational Datasets}
 \label{sec:theo}
 
-\subsection{Dust Absorption}
+We use information from seven observational data sets.
+Four obtained with the Hubble Space Telescope (HST) and three from
+ground-based telescopes.
+All of them select galaxy candidates at $z\sim 6$ using the drop-out
+technique \citep{Steidel96}.
 
-This paper is based on four main observational data sets from the Hubble Space Telescope 
-and three ground-based telescopes. All $z\sim 6$ LBG candidates where discovered using using 
-the drop-out technique\citep{steidel03}. All magnitudes are in AB system.
+The data from the Hubble Space Telescope Legacy (HSTL)
+\citep{bouwens14} is a compilation   of observations since the
+installation of the Advanced Camera for Surveys (ACS) in 2002,
+through the near-infrared Wide Field Camera 3 (WFC3/IR) installed in
+2009, up to 2012.
 
-The data from the Hubble Space Telescope Legacy (HSTL) \citep{bouwens14} is a compilation 
-of observations since the installation of the Advanced Camera for Surveys (ACS) in 2002, 
-through the near-infrared Wide Field Camera 3 (WFC3/IR) installed in 2009, up to 2012. 
 The HST fields of view are: XDF, HUDF09-1, HUDF09-2, CANDELS-S/Deep, 

### 2015-04-28 paper/ms.tex
Willott results

@@
 
+\subsection{Willott}
+
+We performed MCMC runnings with 100.000 steps over the 64 small 
+cubic boxes (of $250$ \hMpc side length) fitting the LF to the 
+Willott observational data, comparing the two cases; with and 
+without dust attenuation. (figures \ref{fig:OD1_MCMC_best_steps_w} and 
+\ref{fig:OD1_MCMC_best_steps_wo}). 
+We used the Likelihood Ratio criterion ($\mathcal{LR}= 0.5$) to
+define the $1\sigma$ confidence interval for our parameters.
+
+$M_0$ is quite similar in booth cases (they are compatible within 
+the error bars), the turnover point corresponds to the same mass.
+$\gamma$ and $L_0$ shown a significative difference in booth cases.
+$\beta$ is hard to constraint in booth cases. 
+The parameer was limited to vary in the range form 0.0 to 1.6. 
+$1\sigma$ region covers the whole range.
+
+The UV luminosity model (eqn. \ref{eqn:luminosity}) that we have 
+chosen can be divided in two regimes; high mass regime 
+(with $M > M_0$) and low mass regime (with $M < M_0$).
+
+The observational dataset from Willott are in the high mass regime 
+with one point in the low mass regime. It makes makes hard to impose
+restrictions over $\beta$, but the other three parameters can be
+well defined.
+
+We also compare the likelihood of the two cases on each individual 
+small box. The Dust Attenuation model is more acurrate than the
+No-Dust Attenuation model in most of the cases as is shown in the figure 
+\ref{fig:OD1_chi2_comparison}.
+
+To study cosmic variance effects, we compared the best fit parameters
+of each box and its likelihood value. We found that cosmic variance
+effects are less significative in best fit parameters than MCMC parameter
+estimation itself.
+
 \begin{table}
@@
 $1\sigma$ is defined by the likelihood ratio between 0.0 (red) and 0.5 (green)}
-\label{}
+\label{fig:OD1_MCMC_best_steps_w}
 \end{figure*}
@@
 $1\sigma$ is defined by the likelihood ratio between 0.0 (red) and 0.5 (green)}
-\label{}
+\label{fig:OD1_MCMC_best_steps_wo}
 \end{figure*}

### 2015-04-29 paper/ms.tex
Some references in references.bib

@@
 The data from the Hubble Space Telescope Legacy (HSTL)
-\citep{bouwens14} is a compilation   of observations since the
+\citep{Bouwens15} is a compilation   of observations since the
 installation of the Advanced Camera for Surveys (ACS) in 2002,
@@
 end of the LF, magnitudes in the rest frame are in the range $-22.52\leq M_{1600} \leq -16.77$
-\citet{bouwens14} calculated LF using a stepwise maximum-likelihood (SWML) based on \citet{efstathiou88}. 
+\citet{Bouwens15} calculated LF using a stepwise maximum-likelihood (SWML) based on \citet{Efstathiou88}. 
 The Schechter parameters derived are: 
@@
 $M^*_{1600} = -21.16\pm 0.20$ and $\alpha = -1.91 \pm 0.09$. 
-\citet{bouwens14} reported that using just few fields of view, UVLF has a slightly non-Schechter-like form.
+\citet{Bouwens15} reported that using just few fields of view, UVLF has a slightly non-Schechter-like form.
 
-\citet{finkelstein14} worked also with HST, using the HUDF, CANDELS and GOODS fields, 
+\citet{Finkelstein14} worked also with HST, using the HUDF, CANDELS and GOODS fields, 
 along with two of the Hubble Frontier Fields (HFF): deep parallel observations (unlensed 
@@
 
-\citet{willott13} presented the sixth release of the Canada-France-Hawaii 
+\citet{Willott13} presented the sixth release of the Canada-France-Hawaii 
 Telescope Legacy Survey CFHTLS. The observations where performed over four 
@@
 was focussed on the highly luminous LBGs. LF is calculated using the stepwise 
-maximum likelihood method of \citet{efstathiou88}, within 
+maximum likelihood method of \citet{Efstathiou88}, within 
 magnitudes 
@@
 
-\citet{mclure09} build the luminosity function for $z=5$ and $z=6$ using data from two ground-based
+\citet{McLure09} build the luminosity function for $z=5$ and $z=6$ using data from two ground-based
  telescopes: the United Kingdom Infrared Telescope in the near-IR imaging and Subaru 
@@
 $z'=26$. The UV rest frame magnitude range is $-22.4\leq M_{1500} \leq-20.6$. The LF 
-was calculated using the maximum likelihood estimator of \citet{schmidt68}. 
+was calculated using the maximum likelihood estimator of \citet{Schmidt68}. 
 Their analysis gave a total number of 104 LBG candidates in the redshift range 
@@
 
-The dataset was retrieved from \cite{mclure09} graph using
+The dataset was retrieved from \cite{McLure09} graph using
 GAVO-DEXTER\footnote{\url{http://dc.zah.uni-heidelberg.de/dexter/ui/ui/custom}}.
@@
 \plotone{fig/observational_data.pdf}
-\caption{Observational data from \cite{bouwens14,mclure09}and \cite{willott13}.}
+\caption{Observational data from \cite{Bouwens15,McLure09}and \cite{Willott13}.}
 \label{graph_observational_data}
@@
 We use the dark matter halo catalog from the Big MultiDark Plank 1 (MDPL) Simulation 
-\citep{klypin14} with 2013 Planck cosmology \citep{planck1}. MDPL is quite similar to the 
-Big Bolshoi ($1 \textrm{Gpc h}^{-1}$) \citep{prada12} and 
+\citep{Klypin14} with 2013 Planck cosmology \citep{Planck1}. MDPL is quite similar to the 
+Big Bolshoi ($1 \textrm{Gpc h}^{-1}$) \citep{Prada12} and 
 its predecesor Bolshoi \citep{klypin11} ($250 \textrm{Mpc h}^{-1}$), booth of them with 

### 2015-04-29 paper/ms.tex
references

@@
 The relation between UV luminosity and Star Formation Rate
-\citep{madau98,kennicutt98} 
+\citep{Madau98,Kennicutt98} 
 is given by:
@@
 Big Bolshoi ($1 \textrm{Gpc h}^{-1}$) \citep{Prada12} and 
-its predecesor Bolshoi \citep{klypin11} ($250 \textrm{Mpc h}^{-1}$), booth of them with 
+its predecesor Bolshoi \citep{Klypin11} ($250 \textrm{Mpc h}^{-1}$), booth of them with 
 WMAP5 cosmology, but MDPL has bigger mass resolution.  Those halo catalogs are 
 available at the MultiDark Database\footnote{\url{http://www.multidark.org}} 
-\citep{riebe13}.
+\citep{Riebe13}.
 
@@
 
-The halo abundance matching technique has been widely used \citep{colin99, kravtsov04}
-resulting in good reproduction of the observed galaxy clustering. \citep{conroy06, lee09}. 
+The halo abundance matching technique has been widely used \citep{Colin99, Kravtsov04}
+resulting in good reproduction of the observed galaxy clustering. \citep{Conroy06, Lee09}. 
 Here we use the simplest case with few premises: 
@@
 $\beta$ and $\gamma$ are the slopes. This equation has a similar fashion to the
-mass to light relation \citep{vandenbosch03} and the mean relation between
-stellar mas of a galaxy and the mass of its halo used by \citet{moster10}.
+mass to light relation \citep{vandenBosch03} and the mean relation between
+stellar mas of a galaxy and the mass of its halo used by \citet{Moster10}.
 
@@
 
-The UV Spectral Slope $\beta$ was introduced by \citet{meurer99} as a UV color to 
+The UV Spectral Slope $\beta$ was introduced by \citet{Meurer99} as a UV color to 
 study dust attenuation in local starburst galaxies and extrapolating to high redshift galaxies. 
@@
 
-\citet{bouwens12b} uses the fluxes on different bands to estimate $\beta$ on each LBG 
+\citet{Bouwens12} uses the fluxes on different bands to estimate $\beta$ on each LBG 
 candidate found with $z \sim 4-7$. After in redshift groups they found a linear relation 
@@
 
-\citet{smit12} used the aforementioned relations to infer the corrected luminosity functions,
+\citet{Smit12} used the aforementioned relations to infer the corrected luminosity functions,
 i.e. dust-free luminosity functions, and the corrected SFR at $z=4$.
@@
 Finally, the UV luminosity for each galaxy can be directly related with SFR according 
-to \citet{madau98}.
-This model is accurate within the range of $10^8 - 10^9 \textrm{yr}$\citep{kennicutt98}.
-The relation between UV luminosity and Star Formation Rate \citep{madau98,kennicutt98} 
+to \citet{Madau98}.
+This model is accurate within the range of $10^8 - 10^9 \textrm{yr}$\citep{Kennicutt98}.
+The relation between UV luminosity and Star Formation Rate \citep{Madau98} and \cite{Kennicutt98} 
 is given by:
@@
 $\beta$ and $\gamma$ are the slopes. This equation has a similar fashion to the
-mass to light relation \citep{vandenbosch03} and the mean relation between
-stellar mas of a galaxy and the mas of its halo used by \cite{moster10}.
+mass to light relation \citep{vandenBosch03} and the mean relation between
+stellar mas of a galaxy and the mass of its halo used by \cite{Moster10}.
 
-There are more complex models\citep{lee09} that includes a random behavior:
+There are more complex models\citep{Lee09} that includes a random behavior:
 galaxies has not synchronization on the beginning of star forming stage, also
@@
 The $x$ axis corresponds to the box number.}
-\label{}
+\label{fig:OD1_individual_box_results_w}
 \end{figure}
@@
 The $x$ axis corresponds to the box number.}
-\label{}
+\label{fig:OD1_individual_box_results_wo}
 \end{figure}
@@
  attenuation model.}
-\label{}
+\label{fig:OD1_CosmicVar2_w_dust}
 \end{figure}
@@
  attenuation model.}
-\label{}
+\label{fig:OD1_CosmicVar2_wo_dust}
 \end{figure}
@@
 Solid lines represents the mean SFR value over the small boxes within $50\%$  shaded region. 
-Comparison with the GALFORM semi-analitical model \citep{gonzalez14} and a implementation
+Comparison with the GALFORM semi-analitical model \citep{Gonzalez14} and a implementation
 of abundance matching model \citep{Behroozi13}. }
@@
 Solid lines represents the mean SFR value over the small boxes within $50\%$  shaded region.
-Comparison with the GALFORM semi-analitical model \citep{gonzalez14} and a implementation
+Comparison with the GALFORM semi-analitical model \citep{Gonzalez14} and a implementation
 of abundance matching model \citep{Behroozi13}. }

### 2015-04-29 paper/ms.tex
Abstract. (+Word Wrap)

@@
 scaling derived from observations by Bouwens.
+We show dependence of our parameter uncertainties related to the
+comoving volume and magnitude range in observed surveys, taking advantage of the 
+wide mass resolution range of latest available dark matter halo catalogs.
 We compare our results against the results of abundance matching
@@
 Two cameras performed the observations: ACS and WFC3/IR, using 
-$B_{435}$, $V_{606}$, $ i_{814}$, $ z_{850}$, $ I_{814}$, $Y_{098}$, $Y_{105}$, $J{125}$, 
-$JH_{140}$ and $H_{160}$ filters.
-The limit magnitude is between $\sim27.5$mag in CANDELS-EGS and$\sim30 $mag in the 
-deepest field (XDF). Total number of z=6 LBG candidates is 940, most of them in the faint 
-end of the LF, magnitudes in the rest frame are in the range $-22.52\leq M_{1600} \leq -16.77$
-\citet{Bouwens15} calculated LF using a stepwise maximum-likelihood (SWML) based on \citet{Efstathiou88}. 
+$B_{435}$, $V_{606}$, $ i_{814}$, $ z_{850}$, $ I_{814}$, $Y_{098}$, $Y_{105}$, 
+$J{125}$,  $JH_{140}$ and $H_{160}$ filters.
+The limit magnitude is between $\sim27.5$mag in CANDELS-EGS and$\sim30 $mag in 
+the  deepest field (XDF). Total number of z=6 LBG candidates is 940, most of 
+them in the faint end of the LF, magnitudes in the rest frame are in the range 
+$-22.52\leq M_{1600} \leq -16.77$ \citet{Bouwens15} calculated LF using a 
+stepwise maximum-likelihood (SWML) based on \citet{Efstathiou88}. 
 The Schechter parameters derived are: 
@@
 $M^*_{1600} = -21.16\pm 0.20$ and $\alpha = -1.91 \pm 0.09$. 
-\citet{Bouwens15} reported that using just few fields of view, UVLF has a slightly non-Schechter-like form.
+\citet{Bouwens15} reported that using just few fields of view, UVLF has a 
+slightly non-Schechter-like form.
 
-\citet{Finkelstein14} worked also with HST, using the HUDF, CANDELS and GOODS fields, 
-along with two of the Hubble Frontier Fields (HFF): deep parallel observations (unlensed 
-fields) near the Abell 2744 and MACS J0416.1-2403 clusters. The HFF uses the ACS and 
-the WFC3/IR with the same filters aforementioned but $z_{850}$. Total survey area is around 
-$\sim300\textrm{arcmin}^2$, with 706 photometric candidates at redshift 6 defined as the interval $5.5<z<6.5$. 
-Total volume of this study is around $ 8 \times 10^5 \textrm{Mpc}^3$. The Schechter function parameters they found are $\phi^* =(1.86_{-0.80}^{+0.94}) \times 10 ^{-4}  \textrm{Mpc}^{-3} $, 
+\citet{Finkelstein14} worked also with HST, using the HUDF, CANDELS and GOODS 
+fields, along with two of the Hubble Frontier Fields (HFF): deep parallel 
+observations (unlensed fields) near the Abell 2744 and MACS J0416.1-2403 
+clusters. The HFF uses the ACS and the WFC3/IR with the same filters 
+aforementioned but $z_{850}$. Total survey area is around 
+$\sim300\textrm{arcmin}^2$, with 706 photometric candidates at redshift 6 
+defined as the interval $5.5<z<6.5$. Total volume of this study is around 
+$ 8 \times 10^5 \textrm{Mpc}^3$. The Schechter function parameters they found 
+are $\phi^* =(1.86_{-0.80}^{+0.94}) \times 10 ^{-4}  \textrm{Mpc}^{-3} $, 
 $M^*_{1600} = -21.1_{-0.31}^{+0.25}$ and $\alpha = -2.02_{-0.10}^{+0.10}$.
@@
 Telescope Legacy Survey CFHTLS. The observations where performed over four 
-separated fields covering a total area $\sim 4 \deg^2$ (a large area), it gives this 
-survey great robustness. Optical observations used MegaCam  %%%%%%[CITE REQUIRED] 
+separated fields covering a total area $\sim 4 \deg^2$ (a large area), it gives 
+this survey great robustness. Optical observations used MegaCam  %%%%%%[CITE REQUIRED] 
 with $u^* g' r' i' z'$ filters. The main selection criteria: all the 
@@
 for 7 candidates using GMOS spectrograph on the Gemini Telescopes, which 
-has a $\ll 5.5$-square arcmin field of view, giving a volume $\sim 1.09 \times 10^7 \textrm{Mpc}^3$. 
+has a $\ll 5.5$-square arcmin field of view, giving a volume 
+$\sim 1.09 \times 10^7 \textrm{Mpc}^3$. 
 They show incompleteness in the sample due to 
@@
 have every object brighter than the limit magnitude on the faint limit. The full 
-galaxy LF at $z=6$ cannot be obtained as in other studies. Nevertheless, this survey 
-was focussed on the highly luminous LBGs. LF is calculated using the stepwise 
-maximum likelihood method of \citet{Efstathiou88}, within 
-magnitudes 
+galaxy LF at $z=6$ cannot be obtained as in other studies. Nevertheless, this 
+survey was focussed on the highly luminous LBGs. LF is calculated using the 
+stepwise maximum likelihood method of \citet{Efstathiou88}, within magnitudes 
 from $M_{1350} = -22.5$ up to $-20.5$. The luminosity function of $z=5.9$ shows 
-an exponential decline at the bright end, where feedback processes and inefficient 
-last cooling limites star forming in bright galaxies hosted in the most massive halos.
+an exponential decline at the bright end, where feedback processes and 
+inefficient last cooling limites star forming in bright galaxies hosted in the 
+most massive halos.
 
-\citet{McLure09} build the luminosity function for $z=5$ and $z=6$ using data from two ground-based
- telescopes: the United Kingdom Infrared Telescope in the near-IR imaging and Subaru 
- Telescope for the optical imaging. They use the first data release of the UKIRT Infrared 
- DeepSky Survey Ultra Deep Survey (UDS), together with the Subaru XMM-Newton 
- Survey (SXDS). Total observed area is $0.63 \deg^2$ uniformly covered by booth catalogues.
+\citet{McLure09} build the luminosity function for $z=5$ and $z=6$ using data 
+from two ground-based telescopes: the United Kingdom Infrared Telescope in the 
+near-IR imaging and Subaru Telescope for the optical imaging. They use the first 
+data release of the UKIRT Infrared  DeepSky Survey Ultra Deep Survey (UDS), 
+together with the Subaru XMM-Newton  Survey (SXDS). Total observed area is 
+$0.63 \deg^2$ uniformly covered by booth catalogues.
 The volume in this survey is $\sim 3 \times 10^6 \textrm{Mpc}^3$.
-The UKIRT was equipped with the WFCAM using $J K$ filters. The Subaru was equipped 
-with the Suprime-Cam with the $B V R i' z'$ filters. All candidates where brighter than 
-$z'=26$. The UV rest frame magnitude range is $-22.4\leq M_{1500} \leq-20.6$. The LF 
-was calculated using the maximum likelihood estimator of \citet{Schmidt68}. 
-Their analysis gave a total number of 104 LBG candidates in the redshift range 
-$5.7\leq z \leq 6.3$. LF was parameterized according to the Schechter function with 
-$\phi^*  =(1.8 \pm 0.5) \times 10 ^{-3}  \textrm{Mpc}^{-3}$, $M^*_{1500} = -20.04\pm 0.12$ 
-and $\alpha = -1.71 \pm 0.11$.
+The UKIRT was equipped with the WFCAM using $J K$ filters. The Subaru was 
+equipped with the Suprime-Cam with the $B V R i' z'$ filters. All candidates 
+where brighter than $z'=26$. The UV rest frame magnitude range is 
+$-22.4\leq M_{1500} \leq-20.6$. The LF was calculated using the maximum 
+likelihood estimator of \citet{Schmidt68}. Their analysis gave a total number of 
+104 LBG candidates in the redshift range $5.7\leq z \leq 6.3$. LF was 
+parameterized according to the Schechter function with 
+$\phi^* =(1.8\pm 0.5)\times 10 ^{-3} \textrm{Mpc}^{-3}$, 
+$M^*_{1500} = -20.04\pm 0.12$ and $\alpha = -1.71 \pm 0.11$.
 
@@
 
-The key element to connect SFR with halo mass from simulations is the observed UVLF. 
-If there exist a function whom gives to each halo a UV luminosity then is posible to 
-reproduce UVLF from DMH catalogs. The fitting parameters can be explored using a 
-Markov Chain Monte-Carlo (MCMC) implementation. Once the parameters are found, 
-the SFR-Halo Mass relation have been found.
+The key element to connect SFR with halo mass from simulations is the observed 
+UVLF. If there exist a function whom gives to each halo a UV luminosity then is 
+posible to reproduce UVLF from DMH catalogs. The fitting parameters can be 
+explored using a Markov Chain Monte-Carlo (MCMC) implementation. Once the 
+parameters are found, the SFR-Halo Mass relation have been found.
 
-We use the dark matter halo catalog from the Big MultiDark Plank 1 (MDPL) Simulation 
-\citep{Klypin14} with 2013 Planck cosmology \citep{Planck1}. MDPL is quite similar to the 
-Big Bolshoi ($1 \textrm{Gpc h}^{-1}$) \citep{Prada12} and 
-its predecesor Bolshoi \citep{Klypin11} ($250 \textrm{Mpc h}^{-1}$), booth of them with 
-WMAP5 cosmology, but MDPL has bigger mass resolution.  Those halo catalogs are 
-available at the MultiDark Database\footnote{\url{http://www.multidark.org}} 
-\citep{Riebe13}.
+We use the dark matter halo catalog from the Big MultiDark Plank 1 (MDPL) 
+Simulation \citep{Klypin14} with 2013 Planck cosmology \citep{Planck1}. MDPL is 
+quite similar to the Big Bolshoi ($1 \textrm{Gpc h}^{-1}$) \citep{Prada12} and 
+its predecesor Bolshoi \citep{Klypin11} ($250 \textrm{Mpc h}^{-1}$), booth of 
+them with WMAP5 cosmology, but MDPL has bigger mass resolution.  Those halo 
+catalogs are available at the MultiDark 
+Database\footnote{\url{http://www.multidark.org}} \citep{Riebe13}.
 
 The MDPL run is a N-body dark matter only simulation based on the L-Gadget2 
-code. The simulated volume is a cubic box of $1 \textrm{Gpc h}^{-1}$ side length. 
-It has $3840^3$ dark matter particles of  $1.51\times 9
+code. The simulated volume is a cubic box of $1 \textrm{Gpc h}^{-1}$ side 
+length. It has $3840^3$ dark matter particles of  $1.51\times 9
 \textrm{M}_{\odot} \textrm{h}^{-1}$ mass each one. The 2013 Planck
@@
 
-The halo abundance matching technique has been widely used \citep{Colin99, Kravtsov04}
-resulting in good reproduction of the observed galaxy clustering. \citep{Conroy06, Lee09}. 
-Here we use the simplest case with few premises: 
+The halo abundance matching technique has been widely used \citep{Colin99, 
+Kravtsov04} resulting in good reproduction of the observed galaxy clustering. 
+\citep{Conroy06, Lee09}. Here we use the simplest case with few premises: 
 \begin{enumerate}
@@
 We used a Markov Chain Monte Carlo method to find the best parameters and its 
-uncertainties over each one of the boxes and each observational dataset. The code was written
-on Python using the Scipy, Numpy and Matplotlib libraries.
+uncertainties over each one of the boxes and each observational dataset. The 
+code was written on Python using the SciPy Library \citep{SciPy}
+the IPython environment \citep{IPython}.
 
-First of all, one of the four observational data sets (Bouwens, Finkelstein, Willott and McLure) 
-is selected to be the model to fit.
+First of all, one of the four observational data sets (Bouwens, Finkelstein, 
+Willott and McLure) is selected to be the model to fit.
 From the whole simulated halo catalog, a subsample with cubic box shape of 
@@
 
-With an initial set of parameters $(\alpha, \gamma, M_0,$ and $ L_0)$ the UV luminosity
-for the halo is calculated as function of his mass according to equation
+With an initial set of parameters $(\alpha, \gamma, M_0,$ and $ L_0)$ the UV 
+luminosity for the halo is calculated as function of his mass according to 
+equation
  \ref{eqn:luminosity}. Then Luminosity is converted to magnitude units using:
   \[ M_{UV} = 51.82 - 2.5 \log_{10}(L_{UV}). \]
-If we consider the dust attenuation im the equation \ref{eqn. dust attenuation} we have
-a dust-corrected UV Luminosity Function.
+If we consider the dust attenuation im the equation \ref{eqn. dust attenuation} 
+we have a dust-corrected UV Luminosity Function.
 
-The luminosity function is constructed as an histogram of the magnitudes normalized by 
-the volume of the catalog. Each observed luminosity function has a different bin range.
+The luminosity function is constructed as an histogram of the magnitudes 
+normalized by the volume of the catalog. Each observed luminosity function has a 
+different bin range.
 
-Once having the LF, we compare our LF against observed LF. The error function we consider
-is the sum of the square difference over each bin, divided by the observational data uncertain.
+Once having the LF, we compare our LF against observed LF. The error function we 
+consider is the sum of the square difference over each bin, divided by the 
+observational data uncertain.
 \[ \chi^2  = \sum_{i=o}^{n} \frac {\left( x_{i,obs} - x_{i,fit} \right)^2 }{2\sigma_i^2}\]
@@
 The likelihood will have this property:
-\[ \mathcal{L} \propto \exp \left(  -\frac{\chi ^2}{n} \right) \], where $n$ is the number of degrees
-of freedom. We have the maximum likelihood when the error is the minimum.
+\[ \mathcal{L} \propto \exp \left(  -\frac{\chi ^2}{n} \right) \], where $n$ is 
+the number of degrees of freedom. We have the maximum likelihood when the error 
+is the minimum.
 
-Each MCMC step will have have a small variation of the parameters, the UV luminosity and magnitude are 
-calculated again for each halo, we have a new error $\chi_{new}^2$ and a new likelihood 
-$ \mathcal{L}_{new} $.
+Each MCMC step will have have a small variation of the parameters, the UV 
+luminosity and magnitude are calculated again for each halo, we have a new error 
+$\chi_{new}^2$ and a new likelihood $ \mathcal{L}_{new} $.
 
@@
 
-If $  R \geq 1$, then we immediate accept the new set of parameters and start the next MCMC step.
+If $  R \geq 1$, then we immediate accept the new set of parameters and start 
+the next MCMC step.
 
-Else, we have a chance to keep the new set. When $ R < 1$, we compare with a uniformly 
-random number $p$ in the range $[0,1]$. if $ R>p$ we accept the new set of parameters and start
-the next MCMC step. 
-Else we reject the new set and start again with the old set.
+Else, we have a chance to keep the new set. When $ R < 1$, we compare with a 
+uniformly random number $p$ in the range $[0,1]$. if $ R>p$ we accept the new 
+set of parameters and start the next MCMC step.  Else we reject the new set and 
+start again with the old set.
 
-We performed 10.000 effective MCMC steps, plus 1.000 thermalization steps over each box.
-We repeated for the same box without consider dust attenuation.
+We performed 100.000 effective MCMC steps, plus 10.000 thermalization steps over 
+each box. We repeated for the same box without consider dust attenuation.
 
@@
 to \citet{Madau98}.
-This model is accurate within the range of $10^8 - 10^9 \textrm{yr}$\citep{Kennicutt98}.
-The relation between UV luminosity and Star Formation Rate \citep{Madau98} and \cite{Kennicutt98} 
+This model is accurate within the range of $10^8 - 10^9 \textrm{yr}$
+\citep{Kennicutt98}. The relation between UV luminosity and Star Formation Rate 
 is given by:
@@
 \end{enumerate}
-
-The simplest relation we can have is a powerlaw:
- \begin{equation}
-  L = L_0 M^\alpha
- \end{equation}
-but has not well agreement with observed luminosity functions.
-
-A better model is a four parameter function. Each galaxy has a luminosity given
+Our model is a four parameter function. Each galaxy has a luminosity given
 by:
@@
 
-There are more complex models\citep{Lee09} that includes a random behavior:
-galaxies has not synchronization on the beginning of star forming stage, also
-this stage may be time limited. This is called duty cycle. It is probable to
-have in the observations some invisible galaxies in the UV continuum due their
+There exists more sophisticated models as \cite{Lee09} shown, with scattering in 
+the DM Mass-Stellar Mass, but also including some 
+randomization in star forming histories, starburst episodes (duty cycle); 
+galaxies have not synchronization on the beginning of star forming stage, also
+this stage may be time limited. It results in the existence of massive galaxies
+in the studied volume, but with no emmission in the UV continuum due their
 duty cycle may has not started as well it may ended. Also may be present a
@@
 \begin{center}
-\begin{tabular}{ccccc}\hline\hline
-Parameter  & Mean value & Cosmic Variance & MCMC error\\\hline
-$\log_{10}(L_0)$   & 18.067   & 0.029   & 0.116 \\
-$\log_{10}(M_0)$  & 11.190   & 0.072   & 0.729 \\
-$\beta$                  & 1.4801  & 0.175   & 1.299 \\
-$\gamma$             & 0.40284 & 0.058  & 0.3147\\
+\begin{tabular}{cccccc}\hline\hline
+ & \multicolumn{2}{c}{Dust Att.} & \multicolumn{2}{c}{No-Dust Att.}\\
+Parameter                  & MCMC                  & C.Var. & MCMC                    & C.Var. \\\hline
+$\log_{10}(L_0/L_{\odot})$ & $18.07_{-0.06}^{+0.10}$ & 0.03 & $17.81_{-0.08}^{+0.12}$ & 0.02  \\
+$\log_{10}(M_0/M_{\odot})$ & $11.19_{-0.03}^{+0.67}$ & 0.07 & $11.12_{-0.24}^{+0.58}$ & 0.06  \\
+$\beta$                    & $1.480_{-1.28}^{+0.11}$ & 0.18 & $ 1.44_{-1.35}^{+0.16}$ & 0.18  \\
+$\gamma\times0.1$          & $4.028_{-0.82}^{+3.01}$ & 0.58 & $ 5.18_{-0.59}^{+2.36}$ & 0.46  \\
 \hline\hline
 \end{tabular}
-\caption{  Average Best fit parameters to the Willott data in the Dust Attenuation Model.} 
-\label{table:Willott_best_fit_parameters}
-\end{center}
-\end{table}
-
-\begin{table}
-\begin{center}
-\begin{tabular}{ccccc}\hline\hline
-Parameter  & Mean value & Cosmic Variance & MCMC error\\\hline
-$\log_{10}(L_0)$   & 17.807   & 0.020   & 0.150 \\
-$\log_{10}(M_0)$  & 11.119    & 0.060   & 0.642 \\
-$\beta$                  &  1.437    & 0.178   & 1.374 \\
-$\gamma$             &   0.518   & 0.046  & 0.246\\
-\hline\hline
-\end{tabular}
-\caption{  Average Best fit parameters to the Willott data in the No-Dust Attenuation Model.} 
+\caption{ Best fit parameters to the Willott data with and without 
+dust attenuation over 64 small boxes. Mean best value estimated 
+with MCMC, mean $1\sigma$ confidence interval and Cosmic Variance
+(C.Var.)
+} 
 \label{table:Willott_best_fit_parameters_no_dust}
@@
 
-\begin{figure*}
+\begin{figure}
 \epsscale{1.00}
@@
 \label{fig:OD1_MCMC_best_steps_w}
-\end{figure*}
+\end{figure}
 
-\begin{figure*}
+\begin{figure}
 \epsscale{1.00}
@@
 \label{fig:OD1_MCMC_best_steps_wo}
-\end{figure*}
+\end{figure}
 
@@
 of abundance matching model \citep{Behroozi13}. }
-\label{graph_SFR_DMHM_wo}
+\label{fig:SFR_DMHM_wo}
 \end{figure}
@@
 of abundance matching model \citep{Behroozi13}. }
-\label{graph_SFR_DMHM_w}
+\label{fig:_SFR_DMHM_w}
 \end{figure}
@@
 \end{document}
+
+\begin{table*}
+\begin{center}
+\begin{tabular}{cccccc}\hline\hline
+ & \multicolumn{2}{c}{Dust Attenuation} & \multicolumn{2}{c}{No-Dust Attenuation}\\
+Parameter  & MCMC & Cosmic Variance & MCMC & Cosmic Variance \\\hline
+$\log_{10}(L_0)$   & $18.067_{-0.059}^{+0.096}$   & 0.029 & $17.807_{-0.083}^{+0.115}$   & 0.020  \\
+$\log_{10}(M_0)$   & $11.190_{-0.026}^{+0.674}$   & 0.072 & $11.119_{-0.237}^{+0.582}$   & 0.060  \\
+$\beta$            & $1.4801_{-1.276}^{+0.114}$   & 0.175 & $ 1.437_{-1.348}^{+0.157}$   & 0.178  \\
+$\gamma\times0.1$  & $4.0284_{-0.822}^{+3.010}$   & 0.576 & $ 5.182_{-0.588}^{+2.366}$  & 0.461  \\
+\hline\hline
+\end{tabular}
+\caption{  Average Best fit parameters to the Willott data with and without dust attenuation.} 
+\label{table:Willott_best_fit_parameters_no_dust}
+\end{center}
+\end{table*}

### 2015-04-29 paper/ms.tex
editando intro observacional

@@
 The data from the Hubble Space Telescope Legacy (HSTL)
-\citep{Bouwens15} is a compilation   of observations since the
-installation of the Advanced Camera for Surveys (ACS) in 2002,
-through the near-infrared Wide Field Camera 3 (WFC3/IR) installed in
-2009, up to 2012.
+\citep{Bouwens15} is a compilation  of observations taken with the
+Advanced Camera for Surveys (ACS) and near-infrared Wide Field Camera
+3 (WFC3/IR) since 2002 through 2012.
 
-The HST fields of view are: XDF, HUDF09-1, HUDF09-2, CANDELS-S/Deep, 
-CANDELS-S/Wide, ERS, CANDELS-N/Deep, CANDELS-N/Wide, CANDELS-UDS, 
-CANDELS-COSMOS and CANDELS-EGS, with areas of 4.7, 4.7, 4.7, 64.5, 34.2, 
-40.5, 62.9, 60.9, 151.2, 151.9 and 150.7 arcmin$^2$ respectively. The total area 
-at redshift 6 corresponds 
-to 740.8 arcmin$^2$ over five different lines of sight, wit a total volume of 
-$1.8 \times 10^6 \textrm{Mpc}^3$.
-Two cameras performed the observations: ACS and WFC3/IR, using 
-$B_{435}$, $V_{606}$, $ i_{814}$, $ z_{850}$, $ I_{814}$, $Y_{098}$, $Y_{105}$, 
-$J{125}$,  $JH_{140}$ and $H_{160}$ filters.
-The limit magnitude is between $\sim27.5$mag in CANDELS-EGS and$\sim30 $mag in 
-the  deepest field (XDF). Total number of z=6 LBG candidates is 940, most of 
-them in the faint end of the LF, magnitudes in the rest frame are in the range 
-$-22.52\leq M_{1600} \leq -16.77$ \citet{Bouwens15} calculated LF using a 
+The information in that study comes from the ACS and WFC3/IR using the
+filter $B_{435}$, $V_{606}$, $ i_{814}$, $ z_{850}$, $ I_{814}$, $Y_{098}$, $Y_{105}$,
+$J{125}$,  $JH_{140}$ and $H_{160}$.
+The study inclues the following fields of view. XDF,
+HUDF09-1, HUDF09-2, CANDELS-S/Deep,  CANDELS-S/Wide, ERS,
+CANDELS-N/Deep, CANDELS-N/Wide, CANDELS-UDS,  CANDELS-COSMOS and
+CANDELS-EGS, with areas of 4.7, 4.7, 4.7, 64.5, 34.2,  40.5, 62.9,
+60.9, 151.2, 151.9 and 150.7 arcmin$^2$ respectively.  
+The total area  at redshift 6 corresponds to 740.8 arcmin$^2$ over
+five different lines of sight, with a total estimated volume of  $1.8 \times
+10^6 \textrm{Mpc}^3$ comoving.
+
+The limit magnitude ranges between $\sim27.5$mag in CANDELS-EGS and
+$\sim30 $mag in  the  deepest field (XDF). 
+The total number of $z=6$ LBG candidates is $940$, most of 
+them in the faint end of the LF given the relativeley small survey volume.
+The restframe UV magnitudes for these candidates are in the range.
+$-22.52\leq M_{1600} \leq -16.77$.
+\citet{Bouwens15} estimated the Luminosity Function (LF) using a 
 stepwise maximum-likelihood (SWML) based on \citet{Efstathiou88}. 
-The Schechter parameters derived are: 
+They obtained the following Schechter parameters:
 $\phi^* =(0.33_{-0.10}^{+0.15}) \times 10 ^{-3}  \textrm{Mpc}^{-3} $, 
 $M^*_{1600} = -21.16\pm 0.20$ and $\alpha = -1.91 \pm 0.09$. 
-\citet{Bouwens15} reported that using just few fields of view, UVLF has a 
-slightly non-Schechter-like form.
+\citet{Bouwens15} notes that only using few fields of view can yield a
+LF with a deviations from the Schechter shape.
 
 \citet{Finkelstein14} worked also with HST, using the HUDF, CANDELS and GOODS 
-fields, along with two of the Hubble Frontier Fields (HFF): deep parallel 
+fields, along with two of the Hubble Frontier Fields (HFF) of deep parallel 
 observations (unlensed fields) near the Abell 2744 and MACS J0416.1-2403 
-clusters. The HFF uses the ACS and the WFC3/IR with the same filters 
+clusters. 
+The HFF uses the ACS and the WFC3/IR with the same filters
 aforementioned but $z_{850}$. Total survey area is around  

### 2015-04-29 paper/ms.tex
editada parte de finkelstein

@@
 60.9, 151.2, 151.9 and 150.7 arcmin$^2$ respectively.
-The total area  at redshift 6 corresponds to 740.8 arcmin$^2$ over
-five different lines of sight, with a total estimated volume of  $1.8 \times
-10^6 \textrm{Mpc}^3$ comoving.
 
-The limit magnitude ranges between $\sim27.5$mag in CANDELS-EGS and
+The total survey area is $740.8$ arcmin$^2$ over five different lines
+of sight, with a total estimated volume of  $1.8 \times 10^6
+\textrm{Mpc}^3$ comoving. 
+The limiting magnitude ranges between $\sim27.5$mag in CANDELS-EGS and
 $\sim30 $mag in  the  deepest field (XDF). 
@@
 The HFF uses the ACS and the WFC3/IR with the same filters
-aforementioned but $z_{850}$. Total survey area is around  
-$\sim300\textrm{arcmin}^2$, with 706 photometric candidates at redshift 6 
-defined as the interval $5.5<z<6.5$. Total volume of this study is around 
-$ 8 \times 10^5 \textrm{Mpc}^3$. The Schechter function parameters they found 
+aforementioned except $z_{850}$.
+
+The total survey area is around   $\sim300\textrm{arcmin}^2$ with a
+total estimated volume of $8\times 10^5$ Mpc$^{-3}$.
+There are 706 photometric candidates at redshift 6  defined as the
+interval $5.5<z<6.5$. 
+The Schechter function parameters estimated for this data set 
 are $\phi^* =(1.86_{-0.80}^{+0.94}) \times 10 ^{-4}  \textrm{Mpc}^{-3} $, 

### 2015-04-29 paper/ms.tex
first pass en la parte observacional

@@
 
-We use information from seven observational data sets.
-Four obtained with the Hubble Space Telescope (HST) and three from
-ground-based telescopes.
+We use information compiled in four different publications. 
 All of them select galaxy candidates at $z\sim 6$ using the drop-out
 technique \citep{Steidel96}.  
+In what follows we describe the relevant details of each reference.
 
-The data from the Hubble Space Telescope Legacy (HSTL)
-\citep{Bouwens15} is a compilation  of observations taken with the
-Advanced Camera for Surveys (ACS) and near-infrared Wide Field Camera
-3 (WFC3/IR) since 2002 through 2012.
-
-The information in that study comes from the ACS and WFC3/IR using the
-filter $B_{435}$, $V_{606}$, $ i_{814}$, $ z_{850}$, $ I_{814}$, $Y_{098}$, $Y_{105}$,
-$J{125}$,  $JH_{140}$ and $H_{160}$.
+\subsection{Bouwens et al. 2015}
+\citet{Bouwens15} presented results from a compilation of
+observations taken with the Advanced Camera for Surveys (ACS) and
+near-infrared Wide Field Camera 3 (WFC3/IR) since 2002 through 2012. 
 The study inclues the following fields of view. XDF,
@@
 CANDELS-N/Deep, CANDELS-N/Wide, CANDELS-UDS,  CANDELS-COSMOS and
-CANDELS-EGS, with areas of 4.7, 4.7, 4.7, 64.5, 34.2,  40.5, 62.9,
-60.9, 151.2, 151.9 and 150.7 arcmin$^2$ respectively.
+CANDELS-EGS.
+%The information in that study comes from the ACS and WFC3/IR using the
+%filter $B_{435}$, $V_{606}$, $ i_{814}$, $ z_{850}$, $ I_{814}$, $Y_{098}$, $Y_{105}$,
+%$J{125}$,  $JH_{140}$ and $H_{160}$.
 
+%with areas of 4.7, 4.7, 4.7, 64.5, 34.2,  40.5, 62.9,
+%60.9, 151.2, 151.9 and 150.7 arcmin$^2$ respectively.  
 The total survey area is $740.8$ arcmin$^2$ over five different lines
@@
 $-22.52\leq M_{1600} \leq -16.77$.
-\citet{Bouwens15} estimated the Luminosity Function (LF) using a 
-stepwise maximum-likelihood (SWML) based on \citet{Efstathiou88}. 
-They obtained the following Schechter parameters:
+The estimated Schechter parameters:
 $\phi^* =(0.33_{-0.10}^{+0.15}) \times 10 ^{-3}  \textrm{Mpc}^{-3} $, 
 $M^*_{1600} = -21.16\pm 0.20$ and $\alpha = -1.91 \pm 0.09$. 
-\citet{Bouwens15} notes that only using few fields of view can yield a
-LF with a deviations from the Schechter shape.
+%\citet{Bouwens15} notes that only using few fields of view can yield a
+%LF with a deviations from the Schechter shape.
 
-\citet{Finkelstein14} worked also with HST, using the HUDF, CANDELS and GOODS 
-fields, along with two of the Hubble Frontier Fields (HFF) of deep parallel 
-observations (unlensed fields) near the Abell 2744 and MACS J0416.1-2403 
-clusters. 
+\subsection{Finkelstein et al. 2014}
+\citet{Finkelstein14} worked also with HST data.
+They used results from the HUDF, CANDELS and GOODS  fields, along with
+two of the Hubble Frontier Fields (HFF) of deep parallel  observations
+(unlensed fields) near the Abell 2744 and MACS J0416.1-2403  clusters. 
 The HFF uses the ACS and the WFC3/IR with the same filters
 aforementioned except $z_{850}$. 
-
 The total survey area is around   $\sim300\textrm{arcmin}^2$ with a
@@
 
-\citet{Willott13} presented the sixth release of the Canada-France-Hawaii 
-Telescope Legacy Survey CFHTLS. The observations where performed over four 
-separated fields covering a total area $\sim 4 \deg^2$ (a large area), it gives 
-this survey great robustness. Optical observations used MegaCam  %%%%%%[CITE REQUIRED] 
-with $u^* g' r' i' z'$ filters. The main selection criteria: all the 
-objects must be brighter than magnitude $z' = 25.3$. The final 
-number of LBGs founded was 40. Moreover, they get spectroscopic confirmation 
+\subsection{Willott et al. 2013}
+\citet{Willott13} presented results form the sixth release of the Canada-France-Hawaii 
+Telescope Legacy Survey (CFHTLS). 
+The observations where performed over four separated fields covering a
+total area $\sim 4 \deg^2$ giving a survey volume of $\sim 1 \times
+10^7 \textrm{Mpc}^3$, which is over one order of magnitude larger than
+the compilations by \citet{Bouwens15} and \citet{Finkelstein14}
+
+They performed otical observations with MegaCam.
+Their main selection criteria was that all objects must be brighter
+than magnitude $z' = 25.3$. 
+The final  number of LBGs founded was 40. 
+Moreover, they get spectroscopic confirmation 
 for 7 candidates using GMOS spectrograph on the Gemini Telescopes, which 
-has a $\ll 5.5$-square arcmin field of view, giving a volume 
-$\sim 1.09 \times 10^7 \textrm{Mpc}^3$. 
-They show incompleteness in the sample due to 
-foreground contamination and the detection algorithm; there is no warranty to 
-have every object brighter than the limit magnitude on the faint limit. The full 
-galaxy LF at $z=6$ cannot be obtained as in other studies. Nevertheless, this 
-survey was focussed on the highly luminous LBGs. LF is calculated using the 
-stepwise maximum likelihood method of \citet{Efstathiou88}, within magnitudes 
-from $M_{1350} = -22.5$ up to $-20.5$. The luminosity function of $z=5.9$ shows 
-an exponential decline at the bright end, where feedback processes and 
-inefficient last cooling limites star forming in bright galaxies hosted in the 
-most massive halos.
+has a $\ll 5.5$-square arcmin field of view,
 
-\citet{McLure09} build the luminosity function for $z=5$ and $z=6$ using data 
-from two ground-based telescopes: the United Kingdom Infrared Telescope in the 
-near-IR imaging and Subaru Telescope for the optical imaging. They use the first 
-data release of the UKIRT Infrared  DeepSky Survey Ultra Deep Survey (UDS), 
-together with the Subaru XMM-Newton  Survey (SXDS). Total observed area is 
-$0.63 \deg^2$ uniformly covered by booth catalogues.
-The volume in this survey is $\sim 3 \times 10^6 \textrm{Mpc}^3$.
-The UKIRT was equipped with the WFCAM using $J K$ filters. The Subaru was 
-equipped with the Suprime-Cam with the $B V R i' z'$ filters. All candidates 
-where brighter than $z'=26$. The UV rest frame magnitude range is 
-$-22.4\leq M_{1500} \leq-20.6$. The LF was calculated using the maximum 
-likelihood estimator of \citet{Schmidt68}. Their analysis gave a total number of 
-104 LBG candidates in the redshift range $5.7\leq z \leq 6.3$. LF was 
-parameterized according to the Schechter function with 
+%They show incompleteness in the sample due to 
+%foreground contamination and the detection algorithm; there is no warranty to 
+%have every object brighter than the limit magnitude on the faint
+%limit. 
+The survey was focused on the most luminous LBGs. 
+The full LF at $z=6$ cannot be obtained as in other studies, however
+its large volume allows constraints on the bright end.
+The LF Schechter parameters are calculated in the magnitud range 
+$-20.5 > M_{1350} > -22.5$.
+
+\subsection{McLure et al. 2009}
+
+\citet{McLure09} used data obtained with the 
+the United Kingdom Infrared Telescope (UKIRT) in the near-IR imaging
+and Subaru Telescope for the optical imaging. 
+They covered $2268$ arcmin$^{2}$  for a volume $\sim 3 \times 10^6 \textrm{Mpc}^3$.
+The UKIRT was equipped with the WFCAM using $J K$ filters, while Subaru was 
+equipped with the Suprime-Cam with the $B V R i' z'$ filters. 
+All candidates  where brighter than $z'=26$. 
+The UV rest frame magnitude range is 
+$-22.4\leq M_{1500} \leq-20.6$. 
+The LF was calculated using the maximum 
+likelihood estimator of \citet{Schmidt68}. 
+Their analysis gave a total number of 
+$104$ LBG candidates in the redshift range $5.7\leq z \leq 6.3$. 
+They reported the following values for the Schechter function
 $\phi^* =(1.8\pm 0.5)\times 10 ^{-3} \textrm{Mpc}^{-3}$, 
 $M^*_{1500} = -20.04\pm 0.12$ and $\alpha = -1.71 \pm 0.11$.
-
-The dataset was retrieved from \cite{McLure09} graph using
-GAVO-DEXTER\footnote{\url{http://dc.zah.uni-heidelberg.de/dexter/ui/ui/custom}}.
 
@@
 
+The observational datasets were retrieved using
+GAVO-DEXTER\footnote{\url{http://dc.zah.uni-heidelberg.de/dexter/ui/ui/custom}}.
+
 \bibliography{references}

### 2015-04-29 paper/ms.tex
new subsection on abundance matching

@@
 
-\section{Abundance Matching Methodology}
+\section{Theoretical and Numerical Framework}
 \label{sec:methodology}
+
+\subsection{The Abundance Matching Methodology}
+We use an abundance matching approach to find the relationship between
+dark matter halo mass and star formation rate. 
+This approach has been used to link stellar and dark matter masses. 
+Here we extend it to constraint star formation rate properties at high
+redshift.
+
+The starting point for this medho is a population of dark matter halos.
+To each halo we assign a UV luminosity according to the following
+parameterization.
+  \begin{equation}\label{eqn:luminosity}
+  L_{\textrm{\small{UV}}} (M) = L_{0} M \left[ \left( \frac{M}{M_0}\right)^{-\beta} 
+		   + \left( \frac{M}{M_0}\right)^{\gamma} 
+               \right]^{-1},
+  \end{equation}
+where $M$ is the DM mass, $L_{0}$ is a normalization constant, $M_0$
+is the critical mass where the luminosity function has a slope change, 
+$\beta$ and $\gamma$ are two slopes corresponding to the faint and
+bright end, respectively. 
+This equation has the same functional dependence as stellar to dark
+mass ratio used by \citet{Moster10}.
 
@@
 \subsection{Fitting Model}
-
-The observed UV Luminosity Function has two slopes. To reproduce it we decide to use the
- four parameter model:
-  \begin{equation}\label{eqn:luminosity}
-  L_{\textrm{\small{UV}}} (M) = L_{0} M \left[ \left( \frac{M}{M_0}\right)^{-\beta} 
-		   + \left( \frac{M}{M_0}\right)^{\gamma} 
-               \right]^{-1}
-  \end{equation}
-where $M$ is the hosting DMH mass, $L_{0}$ is a normalization constant, $M_0$
-is the critical mass where the luminosity function has a slope change, 
-$\beta$ and $\gamma$ are the slopes. This equation has a similar fashion to the
-mass to light relation \citep{vandenBosch03} and the mean relation between
-stellar mas of a galaxy and the mass of its halo used by \citet{Moster10}.
 

### 2015-04-29 paper/ms.tex
moved dust extinction subsection into obs part

@@
 All magnitudes are in AB system.
-\section{Observational Datasets}
+\section{Observational Constraints}
 \label{sec:theo}
@@
 
-\section{Theoretical and Numerical Framework}
-\label{sec:methodology}
-
-\subsection{The Abundance Matching Methodology}
-We use an abundance matching approach to find the relationship between
-dark matter halo mass and star formation rate. 
-This approach has been used to link stellar and dark matter masses. 
-Here we extend it to constraint star formation rate properties at high
-redshift.
-
-The starting point for this medho is a population of dark matter halos.
-To each halo we assign a UV luminosity according to the following
-parameterization.
-  \begin{equation}\label{eqn:luminosity}
-  L_{\textrm{\small{UV}}} (M) = L_{0} M \left[ \left( \frac{M}{M_0}\right)^{-\beta} 
-		   + \left( \frac{M}{M_0}\right)^{\gamma} 
-               \right]^{-1},
-  \end{equation}
-where $M$ is the DM mass, $L_{0}$ is a normalization constant, $M_0$
-is the critical mass where the luminosity function has a slope change, 
-$\beta$ and $\gamma$ are two slopes corresponding to the faint and
-bright end, respectively. 
-This equation has the same functional dependence as stellar to dark
-mass ratio used by \citet{Moster10}.
-
-The relation between UV luminosity and Star Formation Rate
-\citep{Madau98,Kennicutt98} 
-is given by:
-\begin{equation}
- \textrm{SFR}\left(M_\odot \textrm{yr}^{-1}\right) 
-      = 1.4 \times 10^{-28} L_{\nu} \left( \textrm{erg s}^{-1}\textrm{Hz}^{-1} 
-	\right)
-\end{equation}
-
-  With Initial Mass Function (IMF) between $0.1 M_\odot$ 
- and $100 M_\odot$, in the range of $1250-2500 \mathring{\textrm{A}} $
-
-The star forming rate will be:
-  \begin{equation}
-  SFR = k \times L_{0} M \left[ \left( \frac{M}{M_0}\right)^{-\beta} 
-		   + \left( \frac{M}{M_0}\right)^{\gamma} 
-               \right]^{-1}
-  \end{equation}
-
-The key element to connect SFR with halo mass from simulations is the observed 
-UVLF. If there exist a function whom gives to each halo a UV luminosity then is 
-posible to reproduce UVLF from DMH catalogs. The fitting parameters can be 
-explored using a Markov Chain Monte-Carlo (MCMC) implementation. Once the 
-parameters are found, the SFR-Halo Mass relation have been found.
-
-We use the dark matter halo catalog from the Big MultiDark Plank 1 (MDPL) 
-Simulation \citep{Klypin14} with 2013 Planck cosmology \citep{Planck1}. MDPL is 
-quite similar to the Big Bolshoi ($1 \textrm{Gpc h}^{-1}$) \citep{Prada12} and 
-its predecesor Bolshoi \citep{Klypin11} ($250 \textrm{Mpc h}^{-1}$), booth of 
-them with WMAP5 cosmology, but MDPL has bigger mass resolution.  Those halo 
-catalogs are available at the MultiDark 
-Database\footnote{\url{http://www.multidark.org}} \citep{Riebe13}.
-
-The MDPL run is a N-body dark matter only simulation based on the L-Gadget2 
-code. The simulated volume is a cubic box of $1 \textrm{Gpc h}^{-1}$ side 
-length. It has $3840^3$ dark matter particles of  $1.51\times 9
-\textrm{M}_{\odot} \textrm{h}^{-1}$ mass each one. The 2013 Planck
-cosmology is defined by the following parameters: $\Omega_M = 0.307$,
-$\Omega_B = 0.048$, $\Omega_\Lambda = 0.730$, $\sigma_8 = 0.829$, $n_s
-= 0.96$ and  $H_0 = 67.8$. The DMH Catalog at $z=6$ contains $\sim
-10.9 \times 10^7$   halos, to avoid incompleteness in the low mass
-end, halos with mass below   $10^{10.3} \textrm{M}_{\odot}
-\textrm{h}^{-1}$ are rejected. In order to study how  
-cosmic variance can affect measurements, the original catalog is
-divided into 64 small   cubic boxes, with a similar volume to the
-observations.
-
-The following treatment is applied to every one small box.
-
-The halo abundance matching technique has been widely used \citep{Colin99, 
-Kravtsov04} resulting in good reproduction of the observed galaxy clustering. 
-\citep{Conroy06, Lee09}. Here we use the simplest case with few premises: 
-\begin{enumerate}
- \item Each halo in the catalog hosts one galaxy. There are not empty
-halos, also none of halos has two or more galaxies.
- \item The UV luminosity of each galaxy is function of one variable; the mass of
-the DMH in which is located. This function must be monotone, this guarantees that most 
-massive halos will host the most luminous galaxies in the same volume.
-\end{enumerate}
-
-\subsection{Fitting Model}
-
 \subsection{Dust Attenuation}
 
-Dust in star forming galaxies absorbs part of the UV radiation and reemits on IR. The more 
-massive is the galaxy then more dust contains and dust attenuation will be greater. The 
-relation between dust attenuation and magnitude have been already studied, with this relation 
-we can infer the dust-free UV luminosity of a galaxy from observations, resulting in  a more 
-accurate inferred SFR.
+Dust present in these high redshift star forming galaxies can
+attenuate the UV intrinsic luminosity.
+Although relatively uncertain compared to studies in the local
+universe, there are constraints on the extinction level in LBGs at
+$z=6$.
 
@@
 \end{equation}
+
+\section{Theoretical and Numerical Framework}
+\label{sec:methodology}
+
+\subsection{The Abundance Matching Methodology}
+We use an abundance matching approach to find the relationship between
+dark matter halo mass and star formation rate. 
+This approach has been used to link stellar and dark matter masses. 
+Here we extend it to constraint star formation rate properties at high
+redshift.
+
+The starting point for this method is a population of dark matter halos.
+To each halo we assign a UV luminosity according to the following
+parameterization.
+  \begin{equation}\label{eqn:luminosity}
+  L_{\textrm{\small{UV}}} (M) = L_{0} M \left[ \left( \frac{M}{M_0}\right)^{-\beta} 
+		   + \left( \frac{M}{M_0}\right)^{\gamma} 
+               \right]^{-1},
+  \end{equation}
+where $M$ is the DM mass, $L_{0}$ is a normalization constant, $M_0$
+is the critical mass where the luminosity function has a slope change, 
+$\beta$ and $\gamma$ are two slopes corresponding to the faint and
+bright end, respectively. 
+We now that this equation has the same functional dependence suggested
+ by \citet{Moster10} to link stellar and dark matter masses.
+
+Once each halo has a UV luminosity we also have the option to include
+an extinction correction in order to modify this intrinsic luminosity
+vale. 
+From these UV values we build the LF.
+The free parameters in Eq. (\ref{eqn:luminosity}) are determined by
+requiring that the abudance matching LF follows the observational
+constraints. 
+Then we use the following relationship between UV luminosity and Star Formation Rate
+\citep{Madau98,Kennicutt98} 
+\begin{equation}
+ \textrm{SFR}\left(M_\odot \textrm{yr}^{-1}\right) 
+      = 1.4 \times 10^{-28} L_{\nu} \left( \textrm{erg s}^{-1}\textrm{Hz}^{-1} 
+	\right), 
+\end{equation}
+to finally link SFR with DM halo mass.
+
+\subsection{N-body Simulations and Halo Catalogs}
+
+Cosmological N-body simulations are the source of the dark matter halo
+populations.
+We use two different simulations to cover the wide dynamical range
+explored by the observations: Big MultiDark Planck (MDPL) and Planck
+Bolshoi (P-Bolshoi). 
+Both simulations use 2013 Planck cosmology  defined by the following
+parameters: $\Omega_M = 0.307$, $\Omega_B = 0.048$, $\Omega_\Lambda =
+0.730$, $\sigma_8 = 0.829$, $n_s = 0.96$ and  $H_0 = 67.8$.
+
+The MDPL run is a N-body dark matter only simulation based on the L-Gadget2 
+code. 
+The simulated volume is a cubic box of $1 \textrm{Gpc h}^{-1}$ on a side.
+It has $3840^3$ dark matter particles mass of $1.51\times 9
+\textrm{M}_{\odot} \textrm{h}^{-1}$.
+The DMH Catalog at $z=6$ contains $\sim 10.9 \times 10^7$   halos, to
+avoid incompleteness in the low mass end, halos with mass below
+$10^{10.3} \textrm{M}_{\odot} \textrm{h}^{-1}$ are rejected. 
+We split this large volume into 64 smaller cubic boxes of $250$\hMpc
+on a side (similar volume to the observations by \citet{Willott13}) to
+study the influence of cosmic variance.
+
+The P-Bolshoi simulation...
+
+We obtained the data from the public
+database\footnote{\url{http://www.multidark.org}} \citep{Riebe13}.
+
+\subsection{Fitting Model}
+
+The key element to connect SFR with halo mass from simulations is the observed 
+UVLF. If there exist a function whom gives to each halo a UV luminosity then is 
+posible to reproduce UVLF from DMH catalogs. The fitting parameters can be 
+explored using a Markov Chain Monte-Carlo (MCMC) implementation. Once the 
+parameters are found, the SFR-Halo Mass relation have been found.
 

### 2015-04-29 paper/ms.tex
mcmc description

@@
 \subsection{Dust Attenuation}
-
-Dust present in these high redshift star forming galaxies can
-attenuate the UV intrinsic luminosity.
+\label{subsec:dust}
+Dust in star forming galaxies can attenuate the UV intrinsic luminosity.
 Although relatively uncertain compared to studies in the local
@@
 
-The UV Spectral Slope $\beta$ was introduced by \citet{Meurer99} as a UV color to 
-study dust attenuation in local starburst galaxies and extrapolating to high redshift galaxies. 
-This index appears when a power law fitting is performed over the spectral flux $f$ 
-as function of the wavelength $\lambda$;
-\[ f \propto \lambda^\beta.\]
-The relation for ultra-violet attenuation at $1600 \textrm{\AA}$ they found is:
-\begin{equation}
-A_{1600} = 4.43 + 1.99 \beta,
-\end{equation}
-with $A_{1600}$ in magnitude units.
-
-Due LBGs have more similar spectra properties to local starburst galaxies rather than AGNs 
-for example, we can assume that local calibration of $\beta-A_{1600}$ can be applied also 
-for LBGs,
-%%% From Meurer99
-``The main requirement is that the data include fluxes in two broad bands or coarse spectra 
-covering the rest-frame UV.''
+These studies are based on the UV Spectral slope $\beta$ correlation
+with extinction. 
+This index can be defined approximating by a power-law
+the shape  the spectral flux $f$ as function of the wavelength
+$\lambda f \propto \lambda^\beta$.  
+The relation for attenuation at $1600 \textrm{\AA}$ is $A_{1600} =
+4.43 + 1.99 \beta$, with $A_{1600}$ in magnitude units
+\citet{Meurer99}.
 
 \citet{Bouwens12} uses the fluxes on different bands to estimate $\beta$ on each LBG 
-candidate found with $z \sim 4-7$. After in redshift groups they found a linear relation 
-between $\beta$ and the UV magnitude:
+candidate found with $z \sim 4-7$. 
+At $z=6$ they found a linear relation beteen between $\beta$ and
+$M_{\rm UV}$:
+
 \begin{equation}
 \langle \beta \rangle = \frac{d \beta}{d M_{UV}} \left( M_{UV,AB}+19.5 \right) 
-                                   + \beta_{M_{UV}=-19.5}
+                                   + \beta_{M_{UV}=-19.5},
 \end{equation}
-with $ \beta_{M_{UV}=-19.5} = -2.20$ and $d \beta/d M_{UV} = -0.21$ at $z=5.9$.
+with $ \beta_{M_{UV}=-19.5} = -2.20$ and $d \beta/d M_{UV} = -0.21$ at
+$z=5.9$. 
+We use these relationships to modify the instrinsic UV luminosity
+values.
 
-\citet{Smit12} used the aforementioned relations to infer the corrected luminosity functions,
-i.e. dust-free luminosity functions, and the corrected SFR at $z=4$.
+%Here we use the inverse relation, starting from the intrinsic or dust-free galaxy magnitude, 
+%obtaining the observed magnitude:
+%\begin{equation}
+%  M_{obs} = \begin{cases} 
+%                         \frac{M_{int}-4.616}{1.259}, &\mbox{if } A>0 \\
+%                         M_{int}, &\mbox{else}
+%                   \end{cases}.
+%label{eqn. dust attenuation}
+%end{equation}
 
-Here we use the inverse relation, starting from the intrinsic or dust-free galaxy magnitude, 
-obtaining the observed magnitude:
-\begin{equation}
-  M_{obs} = \begin{cases} 
-                         \frac{M_{int}-4.616}{1.259}, &\mbox{if } A>0 \\
-                         M_{int}, &\mbox{else}
-                   \end{cases}.
-\label{eqn. dust attenuation}
-\end{equation}
-
-\section{Theoretical and Numerical Framework}
+\section{Theoretical, Numerical and Statistical Framework}
 \label{sec:methodology}
@@
 Once each halo has a UV luminosity we also have the option to include
-an extinction correction in order to modify this intrinsic luminosity
-vale. 
+an extinction correction (as described in \SS \ref{subsec:dust})in
+order to modify this intrinsic luminosity value. 
 From these UV values we build the LF.
@@
 
-\subsection{Fitting Model}
+\subsection{Constraining the Free Parameters}
 
-The key element to connect SFR with halo mass from simulations is the observed 
-UVLF. If there exist a function whom gives to each halo a UV luminosity then is 
-posible to reproduce UVLF from DMH catalogs. The fitting parameters can be 
-explored using a Markov Chain Monte-Carlo (MCMC) implementation. Once the 
-parameters are found, the SFR-Halo Mass relation have been found.
+We use a Markov Chain Monte Carlo (MCMC) methodology to constraint the 
+the free parameters in Eq. (\ref{eqn:luminosity}). 
+We use a Metropolis-Hastings algorithm to build the MC chains on the
+four parameters. 
+We performed $10^5$ MCMC steps with $10^4$ additional initial burn-out
+iterations.
 
-\subsection{MCMC}
-We used a Markov Chain Monte Carlo method to find the best parameters and its 
-uncertainties over each one of the boxes and each observational dataset. The 
-code was written on Python using the SciPy Library \citep{SciPy}
-the IPython environment \citep{IPython}.
+To explore the likelihood ${\mathcal L}\propto \exp{(-\chi^2)}$we
+consider the following $\chi^2$. 
+\begin{equation} 
+\chi^2  = \sum_{i=o}^{n} \frac {\left( \log\Phi_{i,obs} - \log\Phi_{i,th} \right)^2
+}{2\sigma_i^2}, 
+\end{equation}
+defined over each LF magnitude bin.
 
-First of all, one of the four observational data sets (Bouwens, Finkelstein, 
-Willott and McLure) is selected to be the model to fit.
-From the whole simulated halo catalog, a subsample with cubic box shape of 
- $250\textrm{Mpc h}^{-1}$ length is selected.
-
-With an initial set of parameters $(\alpha, \gamma, M_0,$ and $ L_0)$ the UV 
-luminosity for the halo is calculated as function of his mass according to 
-equation
- \ref{eqn:luminosity}. Then Luminosity is converted to magnitude units using:
-  \[ M_{UV} = 51.82 - 2.5 \log_{10}(L_{UV}). \]
-If we consider the dust attenuation im the equation \ref{eqn. dust attenuation} 
-we have a dust-corrected UV Luminosity Function.
-
-The luminosity function is constructed as an histogram of the magnitudes 
-normalized by the volume of the catalog. Each observed luminosity function has a 
-different bin range.
-
-Once having the LF, we compare our LF against observed LF. The error function we 
-consider is the sum of the square difference over each bin, divided by the 
-observational data uncertain.
-\[ \chi^2  = \sum_{i=o}^{n} \frac {\left( x_{i,obs} - x_{i,fit} \right)^2 }{2\sigma_i^2}\]
-We worked on the logarithmic space of luminosities to have a good fitting on
-six decades.
-
-The likelihood will have this property:
-\[ \mathcal{L} \propto \exp \left(  -\frac{\chi ^2}{n} \right) \], where $n$ is 
-the number of degrees of freedom. We have the maximum likelihood when the error 
-is the minimum.
-
-Each MCMC step will have have a small variation of the parameters, the UV 
-luminosity and magnitude are calculated again for each halo, we have a new error 
-$\chi_{new}^2$ and a new likelihood $ \mathcal{L}_{new} $.
-
-Following the Metropolis method, we compare the new and the old likelihood:
-\[ R =\frac{ \mathcal{L}_{new}  }{ \mathcal{L}_{old} }  = 
-exp( \chi_{new}^2 - \chi_{old}^2 )
-\]
-
-If $  R \geq 1$, then we immediate accept the new set of parameters and start 
-the next MCMC step.
-
-Else, we have a chance to keep the new set. When $ R < 1$, we compare with a 
-uniformly random number $p$ in the range $[0,1]$. if $ R>p$ we accept the new 
-set of parameters and start the next MCMC step.  Else we reject the new set and 
-start again with the old set.
-
-We performed 100.000 effective MCMC steps, plus 10.000 thermalization steps over 
-each box. We repeated for the same box without consider dust attenuation.
-
-Then we perform the same method over the 64 boxes and the resting three data sets.
-
-The restrictions imposed over the parameters where $0 \leq \alpha \leq 2.0 $  and 
-$\gamma \geq 0$.
-
-Finally, the UV luminosity for each galaxy can be directly related with SFR according 
-to \citet{Madau98}.
-This model is accurate within the range of $10^8 - 10^9 \textrm{yr}$
-\citep{Kennicutt98}. The relation between UV luminosity and Star Formation Rate 
-is given by:
-\begin{equation}
- \textrm{SFR}\left(M_\odot \textrm{yr}^{-1}\right) 
-      = 1.4 \times 10^{-28} L_{\nu} \left( \textrm{erg s}^{-1}\textrm{Hz}^{-1} 
-	\right)
-\end{equation}
-
-\subsection{The Luminosity Model}
-
-In this model we have made two assumptions:
-\begin{enumerate}
- \item Each halo in the catalog hosts one galaxy. There are not empty
-halos, also none of halos has two or more galaxies.
- \item The UV luminosity of each galaxy is function of one variable: the mass of
-the DMH in wich is located.
-\end{enumerate}
-Our model is a four parameter function. Each galaxy has a luminosity given
-by:
-  \begin{equation}
-  L = L_{0} M \left[ \left( \frac{M}{M_0}\right)^{-\beta} 
-		   + \left( \frac{M}{M_0}\right)^{\gamma} 
-               \right]^{-1}
-  \end{equation}
-where $M$ is the hosting DMH mass, $L_{0}$ is a normalization constant, $M_0$
-is the critical mass where the luminosity function has a slope change, 
-$\beta$ and $\gamma$ are the slopes. This equation has a similar fashion to the
-mass to light relation \citep{vandenBosch03} and the mean relation between
-stellar mas of a galaxy and the mass of its halo used by \cite{Moster10}.
-
-There exists more sophisticated models as \cite{Lee09} shown, with scattering in 
-the DM Mass-Stellar Mass, but also including some 
-randomization in star forming histories, starburst episodes (duty cycle); 
-galaxies have not synchronization on the beginning of star forming stage, also
-this stage may be time limited. It results in the existence of massive galaxies
-in the studied volume, but with no emmission in the UV continuum due their
-duty cycle may has not started as well it may ended. Also may be present a
-normal distribution of the luminosity around the expected values.
+We treat each dataset (Bouwens, Finkelstein, Willott and McLure)
+separately to join at the end the posteriors. 
+The size and halo resolution of the computational boxes is coarse for
+the case of Willott and fine for the other datasets.
+We perform two kinds of MCMC explorations with and without considering
+dust extinctions.
+We impose the following priors over the parameters $0 \leq \alpha \leq
+2.0 $  and  $\gamma \geq 0$.
 

### 2015-04-29 paper/ms.tex
new pass on the abstract. first pass on results

@@
 The observational basis for our work is the restframe UV luminosity
-function data obtained with CFHTLS, HST Legacy Survey and UKIDSS.
+function data obtained with HST, CFHTLS, Subary and UKIRT.
 The constraints are based on an abundance matching methodology to the
 observational data using cosmological N-body simulations.
+The relationship between halo mass and star formation rate follows a
+double power law.
 We also take into account the influence on the results of the dust extinction
-scaling derived from observations by Bouwens.
-We show dependence of our parameter uncertainties related to the
-comoving volume and magnitude range in observed surveys, taking advantage of the 
-wide mass resolution range of latest available dark matter halo catalogs.
-We compare our results against the results of abundance matching
+scaling derived from observations by Bouwens et al. (2012).
+Taking advantage of a wide dynamical range in observations and
+simulations we manage to constrain the free parameters of our model
+for halos in the mass range $10^{10}\Msun < M_{h}<10^{13}\Msun$. 
+We find that including dust extinction improves the the match with
+observations.
+Finally, we compare these results against the prediction of abundance matching
 methods (to the stellar mass), a semi-analytic model of galaxy
@@
 
-We performed MCMC runnings with 100.000 steps over the 64 small 
-cubic boxes (of $250$ \hMpc side length) fitting the LF to the 
-Willott observational data, comparing the two cases; with and 
-without dust attenuation. (figures \ref{fig:OD1_MCMC_best_steps_w} and 
-\ref{fig:OD1_MCMC_best_steps_wo}). 
-We used the Likelihood Ratio criterion ($\mathcal{LR}= 0.5$) to
+We use 64 cubic boxes of $250$\hMpc on a side to fit the
+LF data from \citet{Willott13}.
+We use the Likelihood Ratio criterion ($\mathcal{LR}= 0.5$) to
 define the $1\sigma$ confidence interval for our parameters.
 
-$M_0$ is quite similar in booth cases (they are compatible within 
+$M_0$ does not change with and without extinction.
+cases (they are compatible within 
 the error bars), the turnover point corresponds to the same mass.

### 2015-05-01 paper/ms.tex
figs. 9 and 10: fontsize changed. Gonzales-Perez error bars are pending.

@@
 \epsscale{1.00}
-\plotone{fig/SFR_DMHM_wo.pdf}
+\plotone{fig/OD1_SFR_DMHM_wo.pdf}
 \caption{Star formation rate as function of the dark matter halo mass without dust attenuation. 
 Solid lines represents the mean SFR value over the small boxes within $50\%$  shaded region. 
-Comparison with the GALFORM semi-analitical model \citep{Gonzalez14} and a implementation
+Comparison with %the GALFORM semi-analitical model \citep{Gonzalez14} and a
+an implementation
 of abundance matching model \citep{Behroozi13}. }
@@
 \epsscale{1.00}
-\plotone{fig/SFR_DMHM_w.pdf}
+\plotone{fig/OD1_SFR_DMHM_w.pdf}
 \caption{Star formation rate as function of the dark matter halo mass with dust attenuation. 
 Solid lines represents the mean SFR value over the small boxes within $50\%$  shaded region.
-Comparison with the GALFORM semi-analitical model \citep{Gonzalez14} and a implementation
+Comparison with %the GALFORM semi-analitical model \citep{Gonzalez14} and a
+an implementation
 of abundance matching model \citep{Behroozi13}. }

### 2015-08-13 paper/ms.tex
6 cosmic variance graphs

@@
 near-infrared Wide Field Camera 3 (WFC3/IR) since 2002 through 2012. 
-The study inclues the following fields of view. XDF,
+The survey inclues the following fields of view. XDF,
 HUDF09-1, HUDF09-2, CANDELS-S/Deep,  CANDELS-S/Wide, ERS,
@@
 
-They performed otical observations with MegaCam.
+They performed optical observations with MegaCam.
 Their main selection criteria was that all objects must be brighter
@@
 \plotone{fig/observational_data.pdf}
-\caption{Observational data from \cite{Bouwens15,McLure09}and \cite{Willott13}.}
+\caption{Observational data from \cite{Bouwens15,Finkelstein14,McLure09}and \cite{Willott13}.}
 \label{graph_observational_data}
@@
 \epsscale{1.00}
+\plotone{fig/OD2_CosmicVar1_w_dust.pdf}
+\caption{Best fit parameter distribution due cosmic variance with Bouwens data in the dust
+ attenuation model.}
+\label{fig:OD2_CosmicVar1_w_dust}
+\end{figure}
+
+\begin{figure}
+\epsscale{1.00}
+\plotone{fig/OD3_CosmicVar1_w_dust.pdf}
+\caption{Best fit parameter distribution due cosmic variance with McLure data in the dust
+ attenuation model.}
+\label{fig:OD3_CosmicVar1_w_dust}
+\end{figure}
+
+\begin{figure}
+\epsscale{1.00}
+\plotone{fig/OD4_CosmicVar1_w_dust.pdf}
+\caption{Best fit parameter distribution due cosmic variance with Finkelstein data in the dust
+ attenuation model.}
+\label{fig:OD4_CosmicVar1_w_dust}
+\end{figure}
+
+\begin{figure}
+\epsscale{1.00}
 \plotone{fig/OD1_CosmicVar2_wo_dust.pdf}

### 2015-08-13 paper/ms.tex
6 cosmic variance graphs

@@
 \epsscale{1.00}
+\plotone{fig/OD2_CosmicVar1_wo_dust.pdf}
+\caption{Best fit parameter distribution due cosmic variance with Bouwens data in the no-dust
+ attenuation model.}
+\label{fig:OD2_CosmicVar1_wo_dust}
+\end{figure}
+
+\begin{figure}
+\epsscale{1.00}
 \plotone{fig/OD3_CosmicVar1_w_dust.pdf}
@@
 \epsscale{1.00}
+\plotone{fig/OD3_CosmicVar1_wo_dust.pdf}
+\caption{Best fit parameter distribution due cosmic variance with McLure data in the no-dust
+ attenuation model.}
+\label{fig:OD3_CosmicVar1_wo_dust}
+\end{figure}
+
+\begin{figure}
+\epsscale{1.00}
 \plotone{fig/OD4_CosmicVar1_w_dust.pdf}
@@
 \label{fig:OD4_CosmicVar1_w_dust}
+\end{figure}
+
+\begin{figure}
+\epsscale{1.00}
+\plotone{fig/OD4_CosmicVar1_wo_dust.pdf}
+\caption{Best fit parameter distribution due cosmic variance with Finkelstein data in the no-dust
+ attenuation model.}
+\label{fig:OD4_CosmicVar1_wo_dust}
 \end{figure}

### 2015-08-17 paper/ms.tex
adding some text and making minor corrections

@@
 \title{The connection between star formation rate and dark matter halo
-  mass in the epoch of reionization}  
+  mass during reionization}
 \shorttitle{SFR and DM halo mass during reionization}
@@
 The constraints are based on an abundance matching methodology to the
-observational data using cosmological N-body simulations.
-The relationship between halo mass and star formation rate follows a
-double power law.
-We also take into account the influence on the results of the dust extinction
+observational data using cosmological N-body simulations assuming a
+doible power law relationship between halo mass and star formation
+rate follows
+We take into account the influence on the results of the dust extinction
 scaling derived from observations by Bouwens et al. (2012).
@@
 for halos in the mass range $10^{10}\Msun < M_{h}<10^{13}\Msun$. 
-We find that including dust extinction improves the the match with
-observations.
-Finally, we compare these results against the prediction of abundance matching
+We compare our results against the constraints of abundance matching
 methods (to the stellar mass), a semi-analytic model of galaxy
@@
 
-We use information compiled in four different publications. 
-All of them select galaxy candidates at $z\sim 6$ using the drop-out
-technique \citep{Steidel96}.  
+We use information compiled in four different publications that select
+galaxy candidates at $z\sim 6$ using the drop-out  technique
+\citep{Steidel96}.   
 In what follows we describe the relevant details of each reference.
@@
 CANDELS-EGS.
-%The information in that study comes from the ACS and WFC3/IR using the
-%filter $B_{435}$, $V_{606}$, $ i_{814}$, $ z_{850}$, $ I_{814}$, $Y_{098}$, $Y_{105}$,
-%$J{125}$,  $JH_{140}$ and $H_{160}$.
 
@@
 $M^*_{1600} = -21.16\pm 0.20$ and $\alpha = -1.91 \pm 0.09$.
-%\citet{Bouwens15} notes that only using few fields of view can yield a
-%LF with a deviations from the Schechter shape.
 
@@
 bright end, respectively. 
-We now that this equation has the same functional dependence suggested
+We note that this equation has the same functional dependence suggested
  by \citet{Moster10} to link stellar and dark matter masses.
+
+We also include a fixed intrinsic scatter in the mass to SFR
+relationship... %http://arxiv.org/pdf/1507.00999.pdf
 
@@
 We use two different simulations to cover the wide dynamical range
-explored by the observations: Big MultiDark Planck (MDPL) and Planck
-Bolshoi (P-Bolshoi). 
-Both simulations use 2013 Planck cosmology  defined by the following
-parameters: $\Omega_M = 0.307$, $\Omega_B = 0.048$, $\Omega_\Lambda =
+explored by the observations: the Big MultiDark Planck (MDPL) and
+Planck-Bolshoi (P-Bolshoi).  
+Both simulations use cosmological parameters consistent with 2013
+Planck results: $\Omega_M = 0.307$, $\Omega_B = 0.048$, $\Omega_\Lambda =
 0.730$, $\sigma_8 = 0.829$, $n_s = 0.96$ and  $H_0 = 67.8$.
 
-The MDPL run is a N-body dark matter only simulation based on the L-Gadget2 
-code. 
-The simulated volume is a cubic box of $1 \textrm{Gpc h}^{-1}$ on a side.
-It has $3840^3$ dark matter particles mass of $1.51\times 9
-\textrm{M}_{\odot} \textrm{h}^{-1}$.
-The DMH Catalog at $z=6$ contains $\sim 10.9 \times 10^7$   halos, to
-avoid incompleteness in the low mass end, halos with mass below
-$10^{10.3} \textrm{M}_{\odot} \textrm{h}^{-1}$ are rejected. 
-We split this large volume into 64 smaller cubic boxes of $250$\hMpc
-on a side (similar volume to the observations by \citet{Willott13}) to
-study the influence of cosmic variance.
+The MDPL is a N-body dark matter only simulation ran unsing the
+L-Gadget2 code.
+The simulated volume is a cubic box of $1000$ \hMpc on a side.
+It has $3840^3$ dark matter particles mass of $1.51\times 10^{9}$ \hMsun.
+The halo catalog at $z=6$ is built using the Bound Density Maxima algorithm.
+We split the simulation volume into 64 smaller cubic boxes of
+$250$\hMpc to study the influence of cosmic variance in matching the
+observations  by \citet{Willott13}
 
-The P-Bolshoi simulation...
+The P-Bolshoi simulation follows the non-linear evolution of $2048^3$
+particles in a cubic box of $250$ \hMpc on a side.
+This translates into a mass resolution of $1.35\times 10^{8}$ \hMsun
+per particle. We split this simulation into $8$ smaller cubic boxes of
+$125$ \hMpc on a side to study cosmic variance in matching the
+observations by \citet{McLure09, Finkelstein14, Bouwens15}
 
-We obtained the data from the public
-database\footnote{\url{http://www.multidark.org}} \citep{Riebe13}.
+To avoid incompleteness in the low mass end we exclude halos with
+masses lower than $10^{10.3}$\hMsun.
+
+We obtain the halo catalogs from the public \texttt{cosmosim}
+database \footnote{\url{http://www.cosmosim.org}} \citep{Riebe13}.
 

### 2015-08-29 analysis_whole/constants.py
whole SFR-DMHM graphs

@@ -1,0 +1,32 @@
+import numpy as np
+import pylab as P
+from observational_data import *
+
+hpl = 0.6777
+Mag0 = -4.61455/0.2587
+
+# Dust Attenuation/Extinction
+# only if Dust_Ext == 1
+Dust_Ext = 1
+
+# Set of parameters to fit
+Obs_Data = [OD1]
+
+# Initial Conditions
+L_0in   = 10.0**(18.0)
+M_0in   = 10.0**(11.25)
+betain  =  0.75
+gammain =  0.4
+MULT    =  1
+
+# Number of Monte-Carlo Steps
+MS = 100000-1
+
+# Monte-Carlo tuning
+chi_sqr_treshold = 30
+DeltaChi = 0.0001      #
+k0       = 0.02        # L_0
+k1       = 0.015        # M_0
+k2       = 0.02         # beta
+k3       = 0.02         # gamma
+BlowUp  = 1.0e3       # In case that first or first and second bin is equal to zero

### 2015-08-29 analysis_whole/observational_data.py

@@ -1,0 +1,138 @@
+# Last modification: 2015-mar-17 - West Lafayette
+# commented lines added with "OD# Name"
+
+# OD1 Willott
+# OD2 Bouwens
+# OD3 McLure
+# OD4 Finkelstein
+
+
+from numpy import *
+
+HIST1_bins=[-22.75,-22.25,-21.75,-21.25,-20.75,-20.25]
+Willott = array(
+[# Mag,LumFunct, low_err, upp_err #
+[-22.5, 2.66E-8, 9.08E-9, 7.78E-8],
+[-22.0, 2.18E-6, 8.70E-7, 9.70E-6],
+[-21.5, 1.45E-5, 2.88E-6, 2.92E-5],
+[-21.0, 1.29E-4, 7.06E-5, 2.19E-4],
+[-20.5, 2.30E-4, 9.34E-5, 5.77E-4]
+])
+Obs_data1 = zeros([5,4])
+Obs_data1_log10 = zeros([5,4])
+Obs_data1yerror = [array(Willott[:,1]-Willott[:,2]),array(Willott[:,3]-Willott[:,1])]
+for i in range(5):
+    Obs_data1[i,0]=Willott[i,0]
+    Obs_data1[i,1]=Willott[i,1]
+    Obs_data1[i,2]=0
+    Obs_data1[i,3]=0.25
+    Obs_data1_log10[i,0]=Willott[i,0]
+    Obs_data1_log10[i,1]=log10(Willott[i,1])
+    Obs_data1_log10[i,2]=0
+    Obs_data1_log10[i,3]=0.25
+Obs_data1_log10yerror = [array(log10(Willott[:,1]/Willott[:,2])),array(log10(Willott[:,3]/Willott[:,1]))]
+sigma1 = (Obs_data1_log10yerror[:][0] +  Obs_data1_log10yerror[:][0])/2
+
+OD1 = [Obs_data1.transpose(), HIST1_bins, sigma1,"Willott"]
+
+###########################################################################
+
+HIST2_bins=[-22.70,-22.27,-21.77,-21.27,-20.77,-20.27,-19.77,-19.27]
+Bouwens = array(
+[# Mag,LumFunct, +/err #
+[-22.52,0.000002,0.000002],
+[-22.02,0.000011,0.000004],
+[-21.52,0.000029,0.000008],
+[-21.02,0.000060,0.000012],
+[-20.52,0.000146,0.000023],
[…]

### 2015-09-01 paper/ms.tex
SFR-DMHM graphs. (comparisson with Gonzalez-Perez et. al. and Behroozi et. al.)

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\epsscale{1.00}
+\plotone{fig/smallcells/OD2_w_dust_box_1.png} % pdf available
+\caption{Parameter dispersion fitting the Bouwens with the Dust Attenuation model. 
+$1\sigma$ is defined by the likelihood ratio between 0.0 (red) and 0.5 (green)}
+\label{fig:OD2_MCMC_best_steps_w}
+\end{figure}
+
+\begin{figure}
+\epsscale{1.00}
+\plotone{fig/smallcells/OD2_wo_dust_box_1.png} % pdf available
+\caption{Parameter dispersion fitting the Bouwens with the No-Dust Attenuation model. 
+$1\sigma$ is defined by the likelihood ratio between 0.0 (red) and 0.5 (green)}
+\label{fig:OD2_MCMC_best_steps_wo}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\epsscale{1.00}
+\plotone{fig/smallcells/OD3_w_dust_box_1.png} % pdf available
+\caption{Parameter dispersion fitting the McLure with the Dust Attenuation model. 
+$1\sigma$ is defined by the likelihood ratio between 0.0 (red) and 0.5 (green)}
+\label{fig:OD3_MCMC_best_steps_w}
+\end{figure}
+
+\begin{figure}
+\epsscale{1.00}
+\plotone{fig/smallcells/OD3_wo_dust_box_1.png} % pdf available
+\caption{Parameter dispersion fitting the McLure with the No-Dust Attenuation model. 
+$1\sigma$ is defined by the likelihood ratio between 0.0 (red) and 0.5 (green)}
+\label{fig:OD3_MCMC_best_steps_wo}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\epsscale{1.00}
+\plotone{fig/smallcells/OD4_w_dust_box_1.png} % pdf available
+\caption{Parameter dispersion fitting the Finkelstein with the Dust Attenuation model. 
+$1\sigma$ is defined by the likelihood ratio between 0.0 (red) and 0.5 (green)}
+\label{fig:OD4_MCMC_best_steps_w}
+\end{figure}
+
+\begin{figure}
+\epsscale{1.00}
+\plotone{fig/smallcells/OD4_wo_dust_box_1.png} % pdf available
+\caption{Parameter dispersion fitting the Finkelstein with the No-Dust Attenuation model. 
+$1\sigma$ is defined by the likelihood ratio between 0.0 (red) and 0.5 (green)}
+\label{fig:OD4_MCMC_best_steps_wo}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{figure}
@@
 
-\begin{figure}
-\epsscale{1.00}
-\plotone{fig/OD1_CosmicVar2_w_dust.pdf}
-\caption{Best fit parameter distribution due cosmic variance with Willott data in the dust
- attenuation model.}
-\label{fig:OD1_CosmicVar2_w_dust}
-\end{figure}
+%\begin{figure}
+%\epsscale{1.00}
+%\plotone{fig/OD1_CosmicVar2_w_dust.pdf}
+%\caption{Best fit parameter distribution due cosmic variance with Willott data in the dust
+% attenuation model.}
+%\label{fig:OD1_CosmicVar2_w_dust}
+%\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \epsscale{1.00}
-\plotone{fig/OD2_CosmicVar1_wo_dust.pdf}
+\plotone{fig/smallcells/OD2_plotcosmicvariance_wo_dust.pdf}
 \caption{Best fit parameter distribution due cosmic variance with Bouwens data in the no-dust
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{figure}
 \epsscale{1.00}
-\plotone{fig/OD3_CosmicVar1_w_dust.pdf}
+\plotone{fig/smallcells/OD3_plotcosmicvariance_w_dust.pdf}
 \caption{Best fit parameter distribution due cosmic variance with McLure data in the dust
@@
 \epsscale{1.00}
-\plotone{fig/OD3_CosmicVar1_wo_dust.pdf}
+\plotone{fig/smallcells/OD3_plotcosmicvariance_wo_dust.pdf}
 \caption{Best fit parameter distribution due cosmic variance with McLure data in the no-dust
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{figure}
 \epsscale{1.00}
-\plotone{fig/OD4_CosmicVar1_w_dust.pdf}
+\plotone{fig/smallcells/OD4_plotcosmicvariance_w_dust.pdf}
 \caption{Best fit parameter distribution due cosmic variance with Finkelstein data in the dust
@@
 \epsscale{1.00}
-\plotone{fig/OD4_CosmicVar1_wo_dust.pdf}
-\caption{Best fit parameter distribution due cosmic variance with Finkelstein data in the no-dust
+\plotone{fig/smallcells/OD4_plotcosmicvariance_wo_dust.pdf}
+\caption{Best fit parameter distribution due cosmic variance with McLure data in the no-dust
  attenuation model.}
-\label{fig:OD4_CosmicVar1_wo_dust}
+\label{fig:OD3_CosmicVar1_wo_dust}
 \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \epsscale{1.00}
-\plotone{fig/OD1_CosmicVar2_wo_dust.pdf}
-\caption{Best fit parameter distribution due cosmic variance with Willott data in the no-dust
- attenuation model.}
-\label{fig:OD1_CosmicVar2_wo_dust}
-\end{figure}
-
-\begin{figure}
-\epsscale{1.00}
-\plotone{fig/OD1_SFR_DMHM_wo.pdf}
+\plotone{fig/SFR_DMHM_wo.pdf}
 \caption{Star formation rate as function of the dark matter halo mass without dust attenuation. 
-Solid lines represents the mean SFR value over the small boxes within $50\%$  shaded region. 
-Comparison with %the GALFORM semi-analitical model \citep{Gonzalez14} and a
-an implementation
-of abundance matching model \citep{Behroozi13}. }
+Solid lines represents our model's mean SFR value within $50\%$  shaded region. 
+Comparison with the GALFORM semi-analitical model \citep{Gonzalez14} (dashed line within the 
+$50\%$ shaded region) and a an implementation of abundance matching model \citep{Behroozi13}
+(black circles). }
 \label{fig:SFR_DMHM_wo}
@@
 \epsscale{1.00}
-\plotone{fig/OD1_SFR_DMHM_w.pdf}
+\plotone{fig/SFR_DMHM_w.pdf}
 \caption{Star formation rate as function of the dark matter halo mass with dust attenuation. 
-Solid lines represents the mean SFR value over the small boxes within $50\%$  shaded region.
-Comparison with %the GALFORM semi-analitical model \citep{Gonzalez14} and a
-an implementation
-of abundance matching model \citep{Behroozi13}. }
+Solid lines represents our model's mean SFR value within $50\%$  shaded region. 
+Comparison with the GALFORM semi-analitical model \citep{Gonzalez14} (dashed line within the 
+$50\%$ shaded region) and a an implementation of abundance matching model \citep{Behroozi13}
+(black circles). }
 \label{fig:_SFR_DMHM_w}

### 2015-09-03 paper/ms.tex
Chi2 plots
Bouwens

@@
 $\beta$                    & $1.480_{-1.28}^{+0.11}$ & 0.18 & $ 1.44_{-1.35}^{+0.16}$ & 0.18  \\
-$\gamma\times0.1$          & $4.028_{-0.82}^{+3.01}$ & 0.58 & $ 5.18_{-0.59}^{+2.36}$ & 0.46  \\
+$\gamma\times0.1$          & $4.028_{-0.82}^{+3.01}$ & 0.58 & $ 5.18_{-0.59}^{+2.36}$ & 0.58  \\
 \hline\hline
@@
 
+\begin{table}
+\begin{center}
+\begin{tabular}{cccccc}\hline\hline
+ & \multicolumn{2}{c}{Dust Att.} & \multicolumn{2}{c}{No-Dust Att.}\\
+Parameter                  & MCMC                  & C.Var. & MCMC                    & C.Var. \\\hline
+$\log_{10}(L_0/L_{\odot})$ & $18.27_{-0.22}^{+0.33}$ & 0.03 & $17.81_{-0.16}^{+0.22}$ & 0.06  \\
+$\log_{10}(M_0/M_{\odot})$ & $11.43_{-0.49}^{+0.57}$ & 0.07 & $11.82_{-0.32}^{+1.02}$ & 0.13  \\
+$\beta$                    & $ 0.88_{-0.27}^{+0.39}$ & 0.18 & $ 0.91_{-0.48}^{+0.63}$ & 0.04  \\
+$\gamma\times0.1$          & $ 1.41_{-1.41}^{+7.58}$ & 0.58 & $ 1.34_{-1.34}^{+6.77}$ & 0.13  \\
+\hline\hline
+\end{tabular}
+\caption{ Best fit parameters to the Bouwens data with and without 
+dust attenuation over 8 tiny boxes. Mean best value estimated 
+with MCMC, mean $1\sigma$ confidence interval and Cosmic Variance
+(C.Var.)
+} 
+\label{table:Bouwens_best_fit_parameters_no_dust}
+\end{center}
+\end{table}
+
 \begin{figure}
 \epsscale{1.00}
-\plotone{fig/OD1_chi2_comparison.pdf}
+\plotone{fig/chi2_OD1.pdf}
 \caption{Best fit to Willott comparison between the two models. Each point represent $\chi^2$ 
@@
 \label{fig:OD1_chi2_comparison}
+\end{figure}
+
+\begin{figure}
+\epsscale{1.00}
+\plotone{fig/chi2_OD2.pdf}
+\caption{Best fit to Bouwens between the two models. Each point represent $\chi^2$ 
+calculated over each small-box. The solid line represents the ratio 1:1 }
+\label{fig:OD2_chi2_comparison}
+\end{figure}
+
+\begin{figure}
+\epsscale{1.00}
+\plotone{fig/chi2_OD3.pdf}
+\caption{Best fit to McLure comparison between the two models. Each point represent $\chi^2$ 
+calculated over each small-box. The solid line represents the ratio 1:1 }
+\label{fig:OD3_chi2_comparison}
+\end{figure}
+
+\begin{figure}
+\epsscale{1.00}
+\plotone{fig/chi2_OD4.pdf}
+\caption{Best fit to Finkelstein comparison between the two models. Each point represent $\chi^2$ 
+calculated over each small-box. The solid line represents the ratio 1:1 }
+\label{fig:OD4_chi2_comparison}
 \end{figure}

### 2015-09-04 paper/ms.tex
loren ipsum

@@
 
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Nulla accumsan elementum leo at ornare.
+Curabitur at ligula ac purus ultrices suscipit in non leo.
+Aliquam erat volutpat.
+Curabitur sit amet lectus ligula.
+Sed tincidunt urna ac felis sodales, non accumsan lorem porta.
+Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos himenaeos.
+Curabitur risus dolor, sollicitudin sit amet fringilla volutpat, convallis eu nibh.
+Interdum et malesuada fames ac ante ipsum primis in faucibus.
+Sed vulputate elit sit amet risus interdum, nec efficitur velit aliquam.
+Mauris nec scelerisque nisi, sed accumsan nunc.
+Pellentesque elementum pulvinar magna.
+Donec eleifend luctus libero vitae fermentum.
+Proin eu viverra est.
+Duis eget congue libero, nec iaculis libero.
+
 \begin{table}

### 2015-09-04 paper/ms.tex
Tables.

--- 2015-09-03 paper/ms.tex
@@
 $\beta$                    & $1.480_{-1.28}^{+0.11}$ & 0.18 & $ 1.44_{-1.35}^{+0.16}$ & 0.18  \\
-$\gamma\times0.1$          & $4.028_{-0.82}^{+3.01}$ & 0.58 & $ 5.18_{-0.59}^{+2.36}$ & 0.58  \\
+$\gamma\times10$           & $4.028_{-0.82}^{+3.01}$ & 0.58 & $ 5.18_{-0.59}^{+2.36}$ & 0.58  \\
 \hline\hline
@@
 Parameter                  & MCMC                  & C.Var. & MCMC                    & C.Var. \\\hline
-$\log_{10}(L_0/L_{\odot})$ & $18.27_{-0.22}^{+0.33}$ & 0.03 & $17.81_{-0.16}^{+0.22}$ & 0.06  \\
-$\log_{10}(M_0/M_{\odot})$ & $11.43_{-0.49}^{+0.57}$ & 0.07 & $11.82_{-0.32}^{+1.02}$ & 0.13  \\
-$\beta$                    & $ 0.88_{-0.27}^{+0.39}$ & 0.18 & $ 0.91_{-0.48}^{+0.63}$ & 0.04  \\
-$\gamma\times0.1$          & $ 1.41_{-1.41}^{+7.58}$ & 0.58 & $ 1.34_{-1.34}^{+6.77}$ & 0.13  \\
+$\log_{10}(L_0/L_{\odot})$ & $18.27_{-0.22}^{+0.33}$ & 0.06 & $17.81_{-0.16}^{+0.22}$ & 0.07  \\
+$\log_{10}(M_0/M_{\odot})$ & $11.43_{-0.49}^{+0.57}$ & 0.13 & $11.82_{-0.32}^{+1.02}$ & 0.18  \\
+$\beta$                    & $ 0.88_{-0.27}^{+0.39}$ & 0.04 & $ 0.91_{-0.48}^{+0.63}$ & 0.11  \\
+$\gamma\times10$           & $ 1.41_{-1.41}^{+7.58}$ & 1.34 & $ 1.34_{-1.34}^{+6.77}$ & 1.03  \\
 \hline\hline
@@
 \label{table:Bouwens_best_fit_parameters_no_dust}
+\end{center}
+\end{table}
+
+\begin{table}
+\begin{center}
+\begin{tabular}{cccccc}\hline\hline
+ & \multicolumn{2}{c}{Dust Att.} & \multicolumn{2}{c}{No-Dust Att.}\\
+Parameter                  & MCMC                  & C.Var. & MCMC                    & C.Var. \\\hline
+$\log_{10}(L_0/L_{\odot})$ & $18.03_{-0.20}^{+0.08}$ & 0.05 & $17.78_{-0.12}^{+0.15}$ & 0.07  \\
+$\log_{10}(M_0/M_{\odot})$ & $11.41_{-0.83}^{+0.57}$ & 0.27 & $11.01_{-0.43}^{+0.83}$ & 0.40  \\
+$\beta$                    & $ 0.49_{-0.44}^{+1.07}$ & 0.60 & $ 0.67_{-0.65}^{+0.90}$ & 0.64  \\
+$\gamma\times10$           & $ 1.95_{-1.39}^{+2.93}$ & 2.43 & $ 3.36_{-1.06}^{+2.91}$ & 0.78  \\
+\hline\hline
+\end{tabular}
+\caption{ Best fit parameters to the McLure data with and without 
+dust attenuation over 8 tiny boxes. Mean best value estimated 
+with MCMC, mean $1\sigma$ confidence interval and Cosmic Variance
+(C.Var.)
+} 
+\label{table:McLure_best_fit_parameters_no_dust}
+\end{center}
+\end{table}
+
+\begin{table}
+\begin{center}
+\begin{tabular}{cccccc}\hline\hline
+ & \multicolumn{2}{c}{Dust Att.} & \multicolumn{2}{c}{No-Dust Att.}\\
+Parameter                  & MCMC                  & C.Var. & MCMC                    & C.Var. \\\hline
+$\log_{10}(L_0/L_{\odot})$ & $17.98_{-0.07}^{+0.23}$ & 0.04 & $17.63_{-0.06}^{+0.17}$ & 0.01  \\
+$\log_{10}(M_0/M_{\odot})$ & $11.17_{-0.10}^{+0.51}$ & 0.05 & $10.88_{-0.11}^{+0.44}$ & 0.05  \\
+$\beta$                    & $ 1.36_{-0.48}^{+0.22}$ & 0.08 & $ 1.56_{-0.75}^{+0.03}$ & 0.04  \\
+$\gamma\times10$           & $ 0.24_{-0.23}^{+5.03}$ & 0.20 & $ 0.93_{-0.83}^{+3.03}$ & 0.42  \\
+\hline\hline
+\end{tabular}
+\caption{ Best fit parameters to the Finkelstein data with and without 
+dust attenuation over 8 tiny boxes. Mean best value estimated 
+with MCMC, mean $1\sigma$ confidence interval and Cosmic Variance
+(C.Var.)
+} 
+\label{table:Finkelstein_best_fit_parameters_no_dust}
 \end{center}

### 2015-09-12 paper/ms.tex

@@
 methods (to the stellar mass), a semi-analytic model of galaxy
-formation (GALFORM) and a hydrodynamical simulation (Illustris).
+formation and a hydrodynamical simulation.
 \end{abstract}

### 2015-09-12 mcmc_hammer/constants.py
Some hard modifications in the test.

@@ -1,0 +1,32 @@
+import numpy as np
+import pylab as P
+from observational_data import *
+
+hpl = 0.6777
+Mag0 = -4.61455/0.2587
+
+# Dust Attenuation/Extinction
+# only if Dust_Ext == 1
+Dust_Ext = 0
+
+# Set of parameters to fit
+Obs_Data = [OD2]
+
+# Initial Conditions
+L_0in   = 10.0**(18.666666)
+M_0in   = 10.0**(11.25)
+betain  =  1.2 
+gammain =  0.2
+MULT    =  1
+
+# Number of Monte-Carlo Steps
+MS = 100000
+
+# Monte-Carlo tuning
+chi_sqr_treshold = 30
+DeltaChi = 0.0001      #
+k0       = 0.02        # L_0
+k1       = 0.015        # M_0
+k2       = 0.02         # beta
+k3       = 0.02         # gamma
+BlowUp  = 1.0e3       # In case that first or first and second bin is equal to zero

### 2015-09-12 mcmc_hammer/functions.py

@@ -1,0 +1,325 @@
+import numpy as np
+import pylab as P
+import time
+from random             import *
+from constants          import *
+from observational_data import *
+
+# 2015-mar-22: Chi2 modification in MCMC
+
+def Luminosity(M,L_0,M_0,beta,gamma):
+    """Returns the luminosity of the halo with mass M.
+
+    Instead of use a two parametric function (a power law), we use a
+    four-parameter function to reproduce the two slopes in the LF.
+
+    Input parameters:
+    M     (double)
+    L_0   (double) ~10**17   (Lsun)
+    M_0   (double) ~10**11.4 (Msun)
+    beta  (double) >0
+    gamma (double) > 0"""
+    return L_0 * M / ( (M/M_0)**(-beta) + (M/M_0)**gamma )
+
+def StarFormationRate(M,L_0,M_0,beta,gamma):
+    """Returns SFR (in Msun yr-1) of a DM halo of mass M
+
+    Input parameters:
+    M     (double)
+    L_0   (double) ~10**17   (Lsun)
+    M_0   (double) ~10**11.4 (Msun)
+    beta  (double) >0
+    gamma (double) > 0"""
+
+    return Luminosity(M,L_0,M_0,beta,gamma) * 1.4e-28
+
+def Dust_Extinction():
+    "Control. Prints if Dust Extinction in constants.py is ON/OFF"
+    if ( Dust_Ext == 1):
+        print "Dust Extinction ON"
+    else:
+        print "Dust Extinction OFF"
+    #return 0
+
+def MCMC( BoxLength, MonteCarloSteps, M, L_0, M_0, beta, gamma,MCMC_reg, *DataSets):
+    """
+Markov Chain  Monte Carlo function.
+
+This function writes MonteCarloSteps lines in the input file MCMC_reg.
+The jump-size on the parameters space is controlled by the "constants.py" file
+
+Arguments:
+        Box size (double)
+        Monte-Carlo Steps (int)
+        Mass (array)
+        4 parameters(double)
+        Output filename (string)
+        DataSets (list) This list contains the names of the observational data
+                 to be fitted.
+     """
+    seed(None)
+    L   = np.zeros(M.size)
+    L_R = np.zeros(M.size)
+    L[:] = Luminosity( M[:], L_0, M_0, beta, gamma)
[…]

### 2015-09-12 mcmc_hammer/observational_data.py

@@ -1,0 +1,202 @@
+# Last modification: 2015-mar-17 - West Lafayette
+# commented lines added with "OD# Name"
+
+# OD1 Willott
+# OD2 Bouwens
+# OD3 McLure
+# OD4 Finkelstein
+
+
+from numpy import *
+
+# ODn = list[ array[magnitude,                               # Abs. Mag. units
+#                   luminosity function,                     # Mpc^-3 h^+3
+#                   zeros?, 
+#                   magnitude_bin_width],                    # Abs. Mag. units
+#             list[ magnitude_bins ],
+#             list[ log10(upper_error)+log10(lower_error) ],
+#             string( name_of_dataset )
+#             float( Boxlength ) ]                          # in Mpc h-1
+
+OD1 = [
+ array([[ -2.25000000e+01,  -2.20000000e+01,  -2.15000000e+01,
+          -2.10000000e+01,  -2.05000000e+01    ],
+        [  2.66000000e-08,   2.18000000e-06,   1.45000000e-05,
+           1.29000000e-04,   2.30000000e-04    ]]),
+ [-22.75, -22.25, -21.75, -21.25, -20.75, -20.25],
+ array([ 0.46679579,  0.39893724,  0.70197551,  0.26178501,  0.39138096]),
+ 'Willott',
+ 250.0 ]
+
+OD2 = [
+ array([
+        [ -2.25200000e+01,  -2.20200000e+01,  -2.15200000e+01, 
+          -2.10200000e+01,  -2.05200000e+01,  -2.00200000e+01,
+           1.95200000e+01,  -1.87700000e+01,  -1.77700000e+01,
+          -1.67700000e+01],
+        [  4.00000000e-06,   2.20000000e-05,   5.80000000e-05,
+           1.20000000e-04,   2.93000000e-04,   5.93000000e-04,
+           1.22200000e-03,   1.72000000e-03,   5.84000000e-03,
+           9.42000000e-03]]),
[…]

### 2015-09-12 mcmc_hammer/triangle.py

@@ -1,0 +1,522 @@
+# -*- coding: utf-8 -*-
+
+from __future__ import print_function, absolute_import, unicode_literals
+
+__all__ = ["corner", "hist2d"]
+__version__ = "0.2.0"
+__author__ = "Dan Foreman-Mackey (danfm@nyu.edu)"
+__copyright__ = "Copyright 2013 Daniel Foreman-Mackey"
+__contributors__ = [
+    # Alphabetical by first name.
+    "Adrian Price-Whelan @adrn",
+    "Brendon Brewer @eggplantbren",
+    "Ekta Patel @ekta1224",
+    "Emily Rice @emilurice",
+    "Geoff Ryan @geoffryan",
+    "Guillaume @ceyzeriat",
+    "Gregory Ashton @ga7g08",
+    "Kelle Cruz @kelle",
+    "Kyle Barbary @kbarbary",
+    "Marco Tazzari @mtazzari",
+    "Matt Pitkin @mattpitkin",
+    "Phil Marshall @drphilmarshall",
+    "Pierre Gratier @pirg",
+    "Stephan Hoyer @shoyer",
+    "Will Vousden @willvousden",
+    "Wolfgang Kerzendorf @wkerzendorf",
+]
+
+import logging
+import numpy as np
+import matplotlib.pyplot as pl
+from matplotlib.ticker import MaxNLocator
+from matplotlib.colors import LinearSegmentedColormap, colorConverter
+from matplotlib.ticker import ScalarFormatter
+
+try:
+    from scipy.ndimage import gaussian_filter
+except ImportError:
+    gaussian_filter = None
+
+
+def corner(xs, bins=20, range=None, weights=None, color="k",
+           smooth=None, smooth1d=None,
+           labels=None, label_kwargs=None,
+           show_titles=False, title_fmt=".2f", title_kwargs=None,
+           truths=None, truth_color="#4682b4",
+           scale_hist=False, quantiles=None, verbose=False, fig=None,
+           max_n_ticks=5, top_ticks=False, use_math_text=False,
+           hist_kwargs=None, **hist2d_kwargs):
+    """
+    Make a *sick* corner plot showing the projections of a data set in a
+    multi-dimensional space. kwargs are passed to hist2d() or used for
+    `matplotlib` styling.
+
+    Parameters
+    ----------
+    xs : array_like (nsamples, ndim)
+        The samples. This should be a 1- or 2-dimensional array. For a 1-D
+        array this results in a simple histogram. For a 2-D array, the zeroth
[…]
